### 2015-06-05 manuscript/maintext.tex
ALL the files

Coevolutionary dynamics act on both species and their interactions in
ways that shape ecological communities. It remains unclear, however, how
the structure of communities at larger spatial scales either influences
or is influenced by local coevolutionary processes, and how mechanisms
acting at these different scales feedback onto one another. Here we show
that, although species interactions vary substantially over a
continental gradient, the coevolutionary significance of individual
interactions is maintained across different scales. Notably, this occurs
despite the fact that observed community variation at the local scale
frequently tends to weaken or remove community-wide coevolutionary
signal. When considered in terms of the interplay between community
ecology and coevolutionary theory, our results demonstrate that
individual interactions are capable and likely to show a consistent
signature of past coevolution even when woven into communities that do
not.

Ecological interactions often exert important selective pressures on the
species involved. For example, the phenologies of lodgepole pines and
red crossbills respond spatially to the presence of squirrels
\citep{benk03a} and palm species undergo changes in seed morphology in
response to the extinction of bird dispersing their seeds
\citep{gale13}. Given that interactions are distributed in similar ways
across communities, at both the large or small scale \citep{jord03}, it
can be argued that much ecological structure is the end result of
evolutionary or coevolutionary dynamics between species
\citep{eklo11, stou12}. Unfortunately, while the coevolutionary dynamic
of pairs of interacting species has been well described at macro
\citep{van73} and micro \citep{gand08} evolutionary timescales, most
attempts to understand how they cascade up to the levels of diversity of
both species and interactions found within empirical communities have
been inconclusive \citep{hemb14}. Moreover, because coevolutionary
dynamics are often presented as a key driving force behind ecological
structure across both time and space \citep{thom05}, it is crucial to
determine the scale at which they are both relevant and quantifiable.

Historically, the evidence for coevolution in taxonomically diverse
communities is quantified as the degree of matching between the
phylogenies of two sets of interacting organisms \citep{lege02}. This
notion builds on the century-old idea that extant species interact in a
way similar to the way their ancestors did \citep{fahr13}, but it is
considerably more restrictive than just phylogenetic conservation of
species' interactions \citep{reze07, eklo11} because it additional
higher-order constraints. More explicitly, communities that have
assembled by successive divergence events due to coevolution should
display phylogenetic congruence, that is (i) have similar phylogenetic
trees and (ii) have species at matching positions in the trees that tend
to interact \citep{page03}. On the other hand, many ecological and
evolutionary processes that occur locally are expected to blur
community-wide coevolutionary signal \citep{pois15}. One possible
explanation is that interactions can display substantial turnover at
ecologically relevant temporal and spatial scales \citep{pois12c}: the
same two species can interact in different ways under the effect of
local environmental contingencies, spatial mismatch in species
phenologies, variations in population abundances, and chance events
\citep{pois14}. It is unclear, however, whether these mechanisms
influence how the coevolutionary signal within individual interactions
should vary across spatial scales.

To answer these questions, we study a dataset of interactions between
rodents and their ectoparasites from 51 sites across Western to Eastern
Europe \citep{kras12b} (Methods Summary). This dataset is uniquely
suited for this task as it represents a paradigmatic system in which
species-species interactions are thought to be driven by macro-evolution
and co-speciation events \citep{vern09}, and coevolutionary signal is
indeed significant at the continental level \citep{kras12a}
(\(p \leq 10^{-4}\); Methods). Importantly, it also provides spatial
replication and variability at a scale large enough to capture
macro-ecological processes.

As host-macroparasite interactions are hypothesized to be both
ecologically constrained and evolutionary conserved \citep{comb01}, the
congruence observed at the continental level sets the baseline for what
would be expected in local communities. Of course, if ecological
mechanisms reduce coevolutionary signal, we should detect coevolution at
the continental scale but not locally. Noting that variation of
interactions can decrease congruence, we analyse the data at two
different levels to test these hypotheses: first, we use \emph{regional}
interaction data---which accounts for different species composition
across sites--and second, we use the \emph{local} interaction
data---which also accounts for variation in the interactions between
observed these species (Methods Summary). Out of 51 sites, 35 show no
signal of coevolution, 11 show significant coevolutionary signal when
using the regional interactions, and 12 show significant coevolutionary
signal using the local interactions (see \emph{Supp. Mat. 1} for
network-level significance values).

These results would appear to support the idea that macro-evolutionary
processes such as co-diversification can have consequences at the
macro-ecological level but may not in fact be detectable at finer
spatial scales. On the other hand, system-level differences say little
about the behaviour of individual interactions, despite the fact most
coevolutionary mechanisms act at the interaction level \citep{thom99}.
As might be expected, we observe here that networks with interactions
that are important for coevolution at the continental scale indeed have
more coevolutionary signal at the local and regional scales alike (Fig.
2A). Intriguingly, we also find that the distribution of individual
interactions' contributions to coevolution is strongly conserved,
regardless of the scale at which the interactions are quantified (Fig.
2B). Because interactions differ in their total contribution to
coevolution, this implies that their distribution across networks is
what actually drives differences in overall coevolutionary signal.
Network-level coevolutionary signal emerges directly from the properties
of interactions and is not a property of the network itself.

Beyond their contribution to coevolution, interactions also ultimately
differ in how frequently they vary when the species involved co-occur
\citep{olit14}. Once more, the literature on host-parasite interactions
usually assumes that the reason why some interactions are more frequent
is because they reflect a significant past history of coevolution
\citep{mora10}. If this were true, we should observe a significant,
positive correlation between the probability of observing an interaction
and the importance of that interaction for coevolution at the
continental scale (Methods Summary). Surprisingly, we find that neither
is true here since interactions that are important for coevolution are
not more conserved (Fig. 3).

Ultimately, coevolutionary signal varies across scale because of the
simultaneous variation of species' interactions \emph{and} communities'
phylogenetic tree structure. In a system characterised by substantial
turnover, we would expect the contribution of each separate interaction
to differ across scales as well. Instead, we observe here that
interactions that contribute strongly to coevolutionary signal at the
continental scale \emph{also} show a significant tendency to contribute
strongly at the local (\(p<0.05\) for positive correlations in 48 out of
51 networks) and regional (in 47 out of 51 networks), and this
observation is independent of network-wide coevolutionary signal (Fig.
4). Remarkably, this result implies that the remnants of coevolution are
still locally detectable in \emph{individual interactions} even though
coevolution regularly fails to leave its imprint on most local networks.

Overall, the results of our analyses demonstrate that there is a
sizeable gap between our current understanding of coevolution as the
basis of multi-species interactions and its applicability to ecological
questions. Local networks show little to no signal of coevolution and
the strength of coevolution between two species is a surprisingly poor
predictor of how frequently they interact. In contrast to the frequent
assumption that phylogenetic structure is a key driver of community
structure \citep{cave09}, these data reveal that this impact is actually
minimal at ecologically relevant spatial scales. Despite all the above,
individual interactions are able to maintain their coevolutionary signal
even when the community they are woven into does not. Thinking more
broadly, these discrepancies provide a clear roadmap for bridging the
aforementioned gap between our appreciation of the role of coevolution
and its empirically measurable outcomes. Network structure is the most
parsimonious \emph{mechanism} by which coevolution proceeds, not the
imprint coevolution leaves on ecological communities.

\section{Methods}\label{methods}

We use data on observations of interactions between 121 species of
rodents and 205 species of parasitic fleas in 51 locations across Europe
\citep{kras12b} to build 51 species-species interaction networks.
Interactions were measured by combing rodents for fleas, a method that
gives high quality data as it has a high power of detection. To account
for differential sampling effort and across site variations in
abundance, we only study the networks' incidence matrices (presence and
absence of interactions).

In our study, we define threes scales for the network data and
analysis---continental, regional, and local. The continental scale is
the aggregated ``metanetwork'' which includes all potential interactions
between co-occurring species \citep{pois12c} (\emph{i.e.}, all species
and all their interactions across the 51 networks). Within each site,
the regional scale is given by the list of observed species and all
their possible interactions. Hence the regional networks are always a
perfect subset of the continental network. The local scale includes only
the interactions that were actually observed in the field at a given
site. Therefore, the local and regional networks always include the same
species, but the local network has only a subset (or, at most, an exact
match) of the interactions in the regional network. The spatial
consistency of every individual interaction is measured as the number of
sites in which the two species involved co-occur.

We quantified the coevolutionary signal in terms of the degree of
matching between host and parasite phylogenies given knowledge of
species interactions using the \emph{PACO} method \citep{balb13}, which
is robust to variations in number of species. \emph{PACO} provides
measures of both the network-level congruence (\emph{i.e.}, is the
network coevolved?) and the interaction-level signal (\emph{i.e.}, what
is the contribution of each interaction to the overall coevolutionary
signal?). We measured the phylogenetic dissimilarity between two sites
for hosts and parasites using PCD \citep{ives10}, a measure that
accounts for the dissimilarity of species, corrected for the
phylogenetic distance between all species in the dataset. Since it is a
requirement of the methods we use here, the phylogenetic trees for hosts
and parasites were rendered ultrametric (i.e., all species are at the
same distance from the root).

\textbf{Acknowledgements.} We thank Juan Antonio Balbuena for
discussions about the \emph{PACo} method, and members of the Stouffer
and Tylianakis groups for comments on an early draft of this manuscript.
We are indebted to Matt Hutchinson and Fernando Cagua for contributions
to the code of the \texttt{paco} R package. Funding to TP and DBS was
provided by a Marsden Fund Fast-Start grant (UOC-1101) and to DBS by a
Rutherford Discovery Fellowship, both administered by the Royal Society
of New Zealand.

\clearpage

\section{Figures}\label{figures}

\begin{figure}[htbp]
\centering
\includegraphics{../figures/figure1.pdf}
\caption{Spatial distribution of coevolutionary signal across the 51
sites. For each location, we indicate whether or not the structure of
regional and local interaction networks is consistent with phylogenetic
congruence. The colour of the circle corresponds to regionally
significant or non-significant (black and grey, respectively) while the
colour of the symbol within corresponds to locally significant or
non-significant (black and grey, respectively).}
\end{figure}

\clearpage

\begin{figure}[htbp]
\centering
\includegraphics{../figures/figure4.pdf}
\caption{Distribution of coevolutionary signal at the network and
interaction levels. \textbf{a}, Networks that have lower coevolutionary
signal at the local or regional level are composed of interactions that
on average contribute little to coevolution at the continental scale.
Dashed lines are the cubic smoothing spline; the two levels of the same
networks are linked by solid grey lines. \textbf{b}, Overall,
interactions observed at the local, regional, and continental scale have
equal contributions to coevolutionary signal. Probability density was
smoothed using a Gaussian kernel density estimator. Raw probability
densities are shown as semi-transparent bars.}
\end{figure}

\clearpage

\begin{figure}[htbp]
\centering
\includegraphics{../figures/figure3.pdf}
\caption{Spatial consistency of an interaction and its contribution to
coevolutionary signal. Spatial consistency is defined as the probability
of observing an interaction between two species given that they were
observed to co-occur. Although statistically significant, there was no
biologically meaningful relationship between spatial consistency and an
interaction's importance for coevolution in the continental network
(\(R^2 \approx 0.01\), \(\rho = -0.1\), \(p \leq 10^{-5}\)).}
\end{figure}

\clearpage

\begin{figure}[htbp]
\centering
\includegraphics{../figures/figure2.pdf}
\caption{The contribution to coevolutionary signal of the interaction
between two species is maintained across scales. For every site, we show
the Pearson's correlation between interaction-level coevolutionary
signal in the continental network and the same in the local network. The
size of each point is proportional to the size of the network, and all
correlations are significant at \(\alpha = 0.05\) except in the grey
shaded area.}
\end{figure}

\clearpage

### 2015-06-05 manuscript/nature-template.tex
ALL the files

--- 2015-06-05 manuscript/maintext.tex
@@
-Coevolutionary dynamics act on both species and their interactions in
-ways that shape ecological communities. It remains unclear, however, how
-the structure of communities at larger spatial scales either influences
-or is influenced by local coevolutionary processes, and how mechanisms
-acting at these different scales feedback onto one another. Here we show
-that, although species interactions vary substantially over a
-continental gradient, the coevolutionary significance of individual
-interactions is maintained across different scales. Notably, this occurs
-despite the fact that observed community variation at the local scale
-frequently tends to weaken or remove community-wide coevolutionary
-signal. When considered in terms of the interplay between community
-ecology and coevolutionary theory, our results demonstrate that
-individual interactions are capable and likely to show a consistent
-signature of past coevolution even when woven into communities that do
-not.
+%% Template for a preprint Letter or Article for submission
+%% to the journal Nature.
+%% Written by Peter Czoschke, 26 February 2004
+%%
+
+\documentclass{nature}
+
+%% make sure you have the nature.cls and naturemag.bst files where
+%% LaTeX can find them
+
+\bibliographystyle{naturemag}
+
+\title{Coevolution leaves a stronger imprint on interactions than on community structure.}
+
+%% Notice placement of commas and superscripts and use of &
+%% in the author list
+
+\author{Timoth\'ee Poisot$^{1}$ \& Daniel B. Stouffer$^1$}
+
+\begin{document}
+
+\maketitle
+
+\begin{affiliations}
+ \item School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand
+\end{affiliations}
+
+\textbf{Coevolutionary dynamics act on both species and their interactions
+in ways that shape ecological communities \textsuperscript{1--4}. It
+remains unclear, however, how the structure of communities at larger
+spatial scales either influences or is influenced by local coevolutionary
+processes \textsuperscript{5,6}, and how mechanisms acting at these different
+scales feedback onto one another \textsuperscript{7--9}. Here we show that,
+although species interactions vary substantially over a continental gradient,
+the coevolutionary significance of individual interactions is maintained
+across different scales. Notably, this occurs despite the fact that observed
+community variation at the local scale frequently tends to weaken or remove
+community-wide coevolutionary signal. When considered in terms of the interplay
+between community ecology and coevolutionary theory, our results demonstrate
+that individual interactions are capable and likely to show a consistent
+signature of past coevolution even when woven into communities that do not.}
 
 Ecological interactions often exert important selective pressures on the
-species involved. For example, the phenologies of lodgepole pines and
-red crossbills respond spatially to the presence of squirrels
-\citep{benk03a} and palm species undergo changes in seed morphology in
-response to the extinction of bird dispersing their seeds
-\citep{gale13}. Given that interactions are distributed in similar ways
-across communities, at both the large or small scale \citep{jord03}, it
-can be argued that much ecological structure is the end result of
-evolutionary or coevolutionary dynamics between species
-\citep{eklo11, stou12}. Unfortunately, while the coevolutionary dynamic
-of pairs of interacting species has been well described at macro
-\citep{van73} and micro \citep{gand08} evolutionary timescales, most
-attempts to understand how they cascade up to the levels of diversity of
-both species and interactions found within empirical communities have
-been inconclusive \citep{hemb14}. Moreover, because coevolutionary
-dynamics are often presented as a key driving force behind ecological
-structure across both time and space \citep{thom05}, it is crucial to
-determine the scale at which they are both relevant and quantifiable.
+species involved. For example, the phenologies of lodgepole pines and red
+crossbills respond spatially to the presence of squirrels \textsuperscript{1}
+and palm species undergo changes in seed morphology in response to the
+extinction of bird dispersing their seeds \textsuperscript{3}. Given that
+interactions are distributed in similar ways across communities, at both
+the large or small scale \textsuperscript{10}, it can be argued that much
+ecological structure is the end result of evolutionary or coevolutionary
+dynamics between species \textsuperscript{11,12}. Unfortunately, while
+the coevolutionary dynamic of pairs of interacting species has been well
+described at macro \textsuperscript{13} and micro \textsuperscript{14}
+evolutionary timescales, most attempts to understand how they cascade up
+to the levels of diversity of both species and interactions found within
+empirical communities have been inconclusive \textsuperscript{15}.  Moreover,
+because coevolutionary dynamics are often presented as a key driving force
+behind ecological structure across both time and space \textsuperscript{6},
+it is crucial to determine the scale at which they are both relevant and
+quantifiable.
 
-Historically, the evidence for coevolution in taxonomically diverse
-communities is quantified as the degree of matching between the
-phylogenies of two sets of interacting organisms \citep{lege02}. This
-notion builds on the century-old idea that extant species interact in a
-way similar to the way their ancestors did \citep{fahr13}, but it is
-considerably more restrictive than just phylogenetic conservation of
-species' interactions \citep{reze07, eklo11} because it additional
-higher-order constraints. More explicitly, communities that have
-assembled by successive divergence events due to coevolution should
-display phylogenetic congruence, that is (i) have similar phylogenetic
-trees and (ii) have species at matching positions in the trees that tend
-to interact \citep{page03}. On the other hand, many ecological and
-evolutionary processes that occur locally are expected to blur
-community-wide coevolutionary signal \citep{pois15}. One possible
-explanation is that interactions can display substantial turnover at
-ecologically relevant temporal and spatial scales \citep{pois12c}: the
-same two species can interact in different ways under the effect of
-local environmental contingencies, spatial mismatch in species
-phenologies, variations in population abundances, and chance events
-\citep{pois14}. It is unclear, however, whether these mechanisms
-influence how the coevolutionary signal within individual interactions
-should vary across spatial scales.
+Historically, the evidence for coevolution in taxonomically diverse communities
+is quantified as the degree of matching between the phylogenies of two
+sets of interacting organisms \textsuperscript{16}.  This notion builds on
+the century-old idea that extant species interact in a way similar to the
+way their ancestors did \textsuperscript{17}, but it is considerably more
+restrictive than just phylogenetic conservation of species' interactions
+\textsuperscript{11,18} because it additional higher-order constraints. More
+explicitly, communities that have assembled by successive divergence events
+due to coevolution should display phylogenetic congruence, that is (i)
+have similar phylogenetic trees and (ii) have species at matching positions
+in the trees that tend to interact \textsuperscript{7}. On the other hand,
+many ecological and evolutionary processes that occur locally are expected
+to blur community-wide coevolutionary signal \textsuperscript{9}. One
+possible explanation is that interactions can display substantial turnover
+at ecologically relevant temporal and spatial scales \textsuperscript{19}:
+the same two species can interact in different ways under the effect of
+local environmental contingencies, spatial mismatch in species phenologies,
+variations in population abundances, and chance events \textsuperscript{20}. It
+is unclear, however, whether these mechanisms influence how the coevolutionary
+signal within individual interactions should vary across spatial scales.
 
-To answer these questions, we study a dataset of interactions between
-rodents and their ectoparasites from 51 sites across Western to Eastern
-Europe \citep{kras12b} (Methods Summary). This dataset is uniquely
-suited for this task as it represents a paradigmatic system in which
-species-species interactions are thought to be driven by macro-evolution
-and co-speciation events \citep{vern09}, and coevolutionary signal is
-indeed significant at the continental level \citep{kras12a}
-(\(p \leq 10^{-4}\); Methods). Importantly, it also provides spatial
-replication and variability at a scale large enough to capture
-macro-ecological processes.
+To answer these questions, we study a dataset of interactions between rodents
+and their ectoparasites from 51 sites across Western to Eastern Europe
+\textsuperscript{21} (Methods Summary). This dataset is uniquely suited for
+this task as it represents a paradigmatic system in which species-species
+interactions are thought to be driven by macro-evolution and co-speciation
+events \textsuperscript{22}, and coevolutionary signal is indeed significant
+at the continental level \textsuperscript{23} ($p \leq 10^{-4}$; Methods
+Summary). Importantly, it also provides spatial replication and variability
+at a scale large enough to capture macro-ecological processes.
 
-As host-macroparasite interactions are hypothesized to be both
-ecologically constrained and evolutionary conserved \citep{comb01}, the
-congruence observed at the continental level sets the baseline for what
-would be expected in local communities. Of course, if ecological
-mechanisms reduce coevolutionary signal, we should detect coevolution at
-the continental scale but not locally. Noting that variation of
-interactions can decrease congruence, we analyse the data at two
-different levels to test these hypotheses: first, we use \emph{regional}
-interaction data---which accounts for different species composition
-across sites--and second, we use the \emph{local} interaction
-data---which also accounts for variation in the interactions between
-observed these species (Methods Summary). Out of 51 sites, 35 show no
-signal of coevolution, 11 show significant coevolutionary signal when
-using the regional interactions, and 12 show significant coevolutionary
-signal using the local interactions (see \emph{Supp. Mat. 1} for
-network-level significance values).
+As host-macroparasite interactions are hypothesized to be both ecologically
+constrained and evolutionary conserved \textsuperscript{24}, the congruence
+observed at the continental level sets the baseline for what would be
+expected in local communities. Of course, if ecological mechanisms reduce
+coevolutionary signal, we should detect coevolution at the continental scale
+but not locally. Noting that variation of interactions can decrease congruence,
+we analyse the data at two different levels to test these hypotheses: first,
+we use \emph{regional} interaction data---which accounts for different
+species composition across sites--and second, we use the \emph{local}
+interaction data---which also accounts for variation in the interactions
+between observed these species (Methods Summary). Out of 51 sites, 35 show no
+signal of coevolution, 11 show significant coevolutionary signal when using
+the regional interactions, and 12 show significant coevolutionary signal
+using the local interactions (see \emph{Supp. Mat.} for network-level
+significance values).
 
@@
 processes such as co-diversification can have consequences at the
-macro-ecological level but may not in fact be detectable at finer
-spatial scales. On the other hand, system-level differences say little
-about the behaviour of individual interactions, despite the fact most
-coevolutionary mechanisms act at the interaction level \citep{thom99}.
-As might be expected, we observe here that networks with interactions
-that are important for coevolution at the continental scale indeed have
-more coevolutionary signal at the local and regional scales alike (Fig.
-2A). Intriguingly, we also find that the distribution of individual
-interactions' contributions to coevolution is strongly conserved,
-regardless of the scale at which the interactions are quantified (Fig.
-2B). Because interactions differ in their total contribution to
-coevolution, this implies that their distribution across networks is
-what actually drives differences in overall coevolutionary signal.
-Network-level coevolutionary signal emerges directly from the properties
-of interactions and is not a property of the network itself.
+macro-ecological level but may not in fact be detectable at finer spatial
+scales. On the other hand, system-level differences say little about the
+behaviour of individual interactions, despite the fact most coevolutionary
+mechanisms act at the interaction level \textsuperscript{25}. As might be
+expected, we observe here that networks with interactions that are important
+for coevolution at the continental scale indeed have more coevolutionary signal
+at the local and regional scales alike (Fig. 2A). Intriguingly, we also find
+that the distribution of individual interactions' contributions to coevolution
+is strongly conserved, regardless of the scale at which the interactions are
+quantified (Fig. 2B). Because interactions differ in their total contribution
+to coevolution, this implies that their distribution across networks is what
+actually drives differences in overall coevolutionary signal. Network-level
+coevolutionary signal emerges directly from the properties of interactions
+and is not a property of the network itself.
 
@@
 differ in how frequently they vary when the species involved co-occur
-\citep{olit14}. Once more, the literature on host-parasite interactions
-usually assumes that the reason why some interactions are more frequent
-is because they reflect a significant past history of coevolution
-\citep{mora10}. If this were true, we should observe a significant,
-positive correlation between the probability of observing an interaction
-and the importance of that interaction for coevolution at the
-continental scale (Methods Summary). Surprisingly, we find that neither
-is true here since interactions that are important for coevolution are
-not more conserved (Fig. 3).
+\textsuperscript{26}. Once more, the literature on host-parasite
+interactions usually assumes that the reason why some interactions are more
+frequent is because they reflect a significant past history of coevolution
+\textsuperscript{27}. If this were true, we should observe a significant,
+positive correlation between the probability of observing an interaction and
+the importance of that interaction for coevolution at the continental scale
+(Methods Summary). Surprisingly, we find that neither is true here since
+interactions that are important for coevolution are not more conserved
+(Fig. 3).
 
@@
 simultaneous variation of species' interactions \emph{and} communities'
-phylogenetic tree structure. In a system characterised by substantial
-turnover, we would expect the contribution of each separate interaction
-to differ across scales as well. Instead, we observe here that
-interactions that contribute strongly to coevolutionary signal at the
-continental scale \emph{also} show a significant tendency to contribute
-strongly at the local (\(p<0.05\) for positive correlations in 48 out of
-51 networks) and regional (in 47 out of 51 networks), and this
-observation is independent of network-wide coevolutionary signal (Fig.
-4). Remarkably, this result implies that the remnants of coevolution are
-still locally detectable in \emph{individual interactions} even though
+phylogenetic tree structure. In a system characterised by substantial turnover,
+we would expect the contribution of each separate interaction to differ across
+scales as well. Instead, we observe here that interactions that contribute
+strongly to coevolutionary signal at the continental scale \emph{also} show a
+significant tendency to contribute strongly at the local ($p<0.05$ for positive
+correlations in 48 out of 51 networks) and regional (in 47 out of 51 networks),
+and this observation is independent of network-wide coevolutionary signal
+(Fig.  4). Remarkably, this result implies that the remnants of coevolution
+are still locally detectable in \emph{individual interactions} even though
 coevolution regularly fails to leave its imprint on most local networks.
 
-Overall, the results of our analyses demonstrate that there is a
-sizeable gap between our current understanding of coevolution as the
-basis of multi-species interactions and its applicability to ecological
-questions. Local networks show little to no signal of coevolution and
-the strength of coevolution between two species is a surprisingly poor
-predictor of how frequently they interact. In contrast to the frequent
-assumption that phylogenetic structure is a key driver of community
-structure \citep{cave09}, these data reveal that this impact is actually
-minimal at ecologically relevant spatial scales. Despite all the above,
-individual interactions are able to maintain their coevolutionary signal
-even when the community they are woven into does not. Thinking more
-broadly, these discrepancies provide a clear roadmap for bridging the
-aforementioned gap between our appreciation of the role of coevolution
-and its empirically measurable outcomes. Network structure is the most
-parsimonious \emph{mechanism} by which coevolution proceeds, not the
-imprint coevolution leaves on ecological communities.
+Overall, the results of our analyses demonstrate that there is a sizeable gap
+between our current understanding of coevolution as the basis of multi-species
+interactions and its applicability to ecological questions. Local networks
+show little to no signal of coevolution and the strength of coevolution
+between two species is a surprisingly poor predictor of how frequently they
+interact. In contrast to the frequent assumption that phylogenetic structure
+is a key driver of community structure \textsuperscript{28}, these data
+reveal that this impact is actually minimal at ecologically relevant spatial
+scales. Despite all the above, individual interactions are able to maintain
+their coevolutionary signal even when the community they are woven into does
+not. Thinking more broadly, these discrepancies provide a clear roadmap
+for bridging the aforementioned gap between our appreciation of the role
+of coevolution and its empirically measurable outcomes. Network structure
+is the most parsimonious \emph{mechanism} by which coevolution proceeds,
+not the imprint coevolution leaves on ecological communities.
 
-\section{Methods}\label{methods}
-
-We use data on observations of interactions between 121 species of
-rodents and 205 species of parasitic fleas in 51 locations across Europe
-\citep{kras12b} to build 51 species-species interaction networks.
-Interactions were measured by combing rodents for fleas, a method that
-gives high quality data as it has a high power of detection. To account
-for differential sampling effort and across site variations in
-abundance, we only study the networks' incidence matrices (presence and
-absence of interactions).
-
-In our study, we define threes scales for the network data and
-analysis---continental, regional, and local. The continental scale is
-the aggregated ``metanetwork'' which includes all potential interactions
-between co-occurring species \citep{pois12c} (\emph{i.e.}, all species
-and all their interactions across the 51 networks). Within each site,
-the regional scale is given by the list of observed species and all
-their possible interactions. Hence the regional networks are always a
-perfect subset of the continental network. The local scale includes only
-the interactions that were actually observed in the field at a given
-site. Therefore, the local and regional networks always include the same
-species, but the local network has only a subset (or, at most, an exact
-match) of the interactions in the regional network. The spatial
-consistency of every individual interaction is measured as the number of
-sites in which the two species involved co-occur.
-
-We quantified the coevolutionary signal in terms of the degree of
-matching between host and parasite phylogenies given knowledge of
-species interactions using the \emph{PACO} method \citep{balb13}, which
-is robust to variations in number of species. \emph{PACO} provides
-measures of both the network-level congruence (\emph{i.e.}, is the
-network coevolved?) and the interaction-level signal (\emph{i.e.}, what
-is the contribution of each interaction to the overall coevolutionary
-signal?). We measured the phylogenetic dissimilarity between two sites
-for hosts and parasites using PCD \citep{ives10}, a measure that
-accounts for the dissimilarity of species, corrected for the
-phylogenetic distance between all species in the dataset. Since it is a
-requirement of the methods we use here, the phylogenetic trees for hosts
-and parasites were rendered ultrametric (i.e., all species are at the
-same distance from the root).
-
-\textbf{Acknowledgements.} We thank Juan Antonio Balbuena for
-discussions about the \emph{PACo} method, and members of the Stouffer
-and Tylianakis groups for comments on an early draft of this manuscript.
-We are indebted to Matt Hutchinson and Fernando Cagua for contributions
-to the code of the \texttt{paco} R package. Funding to TP and DBS was
-provided by a Marsden Fund Fast-Start grant (UOC-1101) and to DBS by a
-Rutherford Discovery Fellowship, both administered by the Royal Society
-of New Zealand.
-
-\clearpage
-
-\section{Figures}\label{figures}
-
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 
-\clearpage
-
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 interaction's importance for coevolution in the continental network
-(\(R^2 \approx 0.01\), \(\rho = -0.1\), \(p \leq 10^{-5}\)).}
+($R^2 \approx 0.01$, $\rho = -0.1$, $p \leq 10^{-5}$).}
 \end{figure}
 
-\clearpage
-
-\begin{figure}[htbp]
+\begin{figure}
 \centering
@@
 size of each point is proportional to the size of the network, and all
-correlations are significant at \(\alpha = 0.05\) except in the grey
+correlations are significant at $\alpha = 0.05$ except in the grey
 shaded area.}
@@
 
-\clearpage
+\begin{methods}
+
+We use data on observations of interactions between 121 species of
+rodents and 205 species of parasitic fleas in 51 locations across Europe
+\textsuperscript{21} to build 51 species-species interaction networks.
+Interactions were measured by combing rodents for fleas, a method that
+gives high quality data as it has a high power of detection. To account
+for differential sampling effort and across site variations in
+abundance, we only study the networks' incidence matrices (presence and
+absence of interactions).
+
+In our study, we define threes scales for the network data and
+analysis---continental, regional, and local. The continental scale is
+the aggregated ``metanetwork'' which includes all potential interactions
+between co-occurring species \textsuperscript{19} (\emph{i.e.}, all
+species and all their interactions across the 51 networks). Within each
+site, the regional scale is given by the list of observed species and
+all their possible interactions. Hence the regional networks are always
+a perfect subset of the continental network. The local scale includes
+only the interactions that were actually observed in the field at a
+given site. Therefore, the local and regional networks always include
+the same species, but the local network has only a subset (or, at most,
+an exact match) of the interactions in the regional network. The spatial
+consistency of every individual interaction is measured as the number of
+sites in which the two species involved co-occur.
+
+We quantified the coevolutionary signal in terms of the degree of
+matching between host and parasite phylogenies given knowledge of
+species interactions using the \emph{PACO} method \textsuperscript{29},
+which is robust to variations in number of species. \emph{PACO} provides
+measures of both the network-level congruence (\emph{i.e.}, is the
+network coevolved?) and the interaction-level signal (\emph{i.e.}, what
+is the contribution of each interaction to the overall coevolutionary
+signal?). We measured the phylogenetic dissimilarity between two sites
+for hosts and parasites using PCD \textsuperscript{30}, a measure that
+accounts for the dissimilarity of species, corrected for the
+phylogenetic distance between all species in the dataset. Since it is a
+requirement of the methods we use here, the phylogenetic trees for hosts
+and parasites were rendered ultrametric (i.e., all species are at the
+same distance from the root).
+
+\end{methods}
+
+%% Put the bibliography here, most people will use BiBTeX in
+%% which case the environment below should be replaced with
+%% the \bibliography{} command.
+
+% \begin{thebibliography}{1}
+% \bibitem{dummy} Articles are restricted to 50 references, Letters
+% to 30.
+% \bibitem{dummyb} No compound references -- only one source per
+% reference.
+% \end{thebibliography}
+
+\section*{References}
+
+\begin{enumerate}
+
+\item Benkman, C. W., Parchman, T. L., Favis, A. \& Siepielski, A.
+M. Reciprocal selection causes a coevolutionary arms race
+between crossbills and lodgepole pine. \emph{Am. Nat.} \textbf{162,}
+182--194 (2003).
+
+\item Thompson, J. N. The coevolving web of life. \emph{Am.
+Nat.} \textbf{173,} 125--140 (2009).
+
+\item Galetti, M. \emph{et al.} Functional Extinction of Birds Drives Rapid
+Evolutionary Changes in Seed Size. \emph{Science} \textbf{340,}
+1086--1090 (2013).
+
+\item Nuismer, S. L., Jordano, P. \& Bascompte, J. Coevolution
+and the Architecture of Mutualistic Networks. \emph{Evolution}
+\textbf{67,} 338--354 (2013).
+
+\item Nuismer, S. L., Thompson, J. N. \& Gomulkiewicz, R.
+Coevolution between hosts and parasites with partially overlapping
+geographic ranges. \emph{J. Evol. Biol.} \textbf{16,} 1337--1345 (2003).
+
+\item Thompson, J. N. \emph{The Geographic Mosaic of
+Coevolution}. (University Of Chicago Press, 2005).
+
+\item Page, R. D. M. \emph{Tangled trees: Phylogeny,
+cospeciation, and coevolution}. (University of Chicago Press, 2003).
+
+\item Urban, M. C. \emph{et al.} The evolutionary ecology of
+metacommunities. \emph{Trends Ecol. Evol.} \textbf{23,} 311--317 (2008).
+
+\item Poisot, T. in \emph{Evolutionary Ecology of
+Host-Parasite Systems} (eds. Morand, S., Littlewood, D. T. \& Poulin,
+R.) (Cambridge University Press, 2015).
+
+\item Jordano, P., Bascompte, J. \& Olesen, J. M. Invariant
+properties in coevolutionary networks of plant-animal interactions.
+\emph{Ecol. Lett.} \textbf{6,} 69--81 (2003).
+
+\item Eklof, A., Helmus, M. R., Moore, M. \& Allesina, S. Relevance of
+evolutionary history for food web structure. \emph{Proc. R. Soc. B Biol. Sci.}
+\textbf{279,} 1588--1596 (2011).
+
+\item Stouffer, D. B., Sales-Pardo, M., Sirer, M. I. \& Bascompte,
+J. Evolutionary Conservation of Species' Roles in Food
+Webs. \emph{Science} \textbf{335,} 1489--1492 (2012).
+
+\item Van Valen, L. A new evolutionary law. \emph{Evol.
+Theory} \textbf{1,} 1--30 (1973).
+
+\item Gandon, S., Buckling, A., Decaestecker, E. \& Day, T.
+Host-parasite coevolution and patterns of adaptation across time and
+space. \emph{J. Evol. Biol.} \textbf{21,} 1861--1866 (2008).
+
+\item Hembry, D. H., Yoder, J. B. \& Goodman, K. R.
+Coevolution and the Diversification of Life. \emph{The American
+Naturalist} \textbf{184,} 425--438 (2014).
+
+\item Legendre, P., Desdevises, Y. \& Bazin, E. A statistical
+test for host-parasite coevolution. \emph{Syst. Biol.} \textbf{51,}
+217--234 (2002).
+
+\item Fahrenholz, H. Ectoparasiten und abstammungslehre.
+\emph{Zool. Anz.} \textbf{41,} 371--374 (1913).
+
+\item Rezende, E. L., Lavabre, J. E., Guimarães, P. R., Jordano, P. \&
+Bascompte, J. Non-random coextinctions in phylogenetically
+structured mutualistic networks. \emph{Nature} \textbf{448,} 925--8
+(2007).
+
+\item Poisot, T., Canard, E., Mouillot, D., Mouquet, N. \& Gravel,
+D. The dissimilarity of species interaction networks.
+\emph{Ecol Lett} \textbf{15,} 1353--1361 (2012).
+
+\item Poisot, T., Stouffer, D. B. \& Gravel, D. Beyond
+species: why ecological interaction networks vary through space and
+time. \emph{Oikos} n/a--n/a (2014).
+
+\item Krasnov, B. \emph{et al.} Data from: Phylogenetic signal in module
+composition and species connectivity in compartmentalized host-parasite
+networks. \emph{Data Dryad} \texttt{10255/dryad.36193} (2012).
+
+\item Verneau, O., Du Preez, L. \& Badets, M. Lessons from
+parasitic flatworms about evolution and historical biogeography of their
+vertebrate hosts. \emph{C. R. Biol.} \textbf{332,} 149--158 (2009).
+
+\item Krasnov, B. R. \emph{et al.} Phylogenetic Signal in Module
+Composition and Species Connectivity in Compartmentalized Host-Parasite
+Networks. \emph{Am. Nat.} \textbf{179,} 501--511 (2012).
+
+\item Combes, C. \emph{Parasitism - The Ecology and Evolution
+of Intimate Interactions}. (University Of Chicago Press, 2001).
+
+\item Thompson, J. N. The raw material for coevolution.
+\emph{Oikos} \textbf{84,} 5--16 (1999).
+
+\item Olito, C. \& Fox, J. W. Species traits and abundances
+predict metrics of plant--pollinator network structure, but not pairwise
+interactions. \emph{Oikos} n/a--n/a (2014).
+
+\item Morand, S. \& Krasnov, B. \emph{Biogreography of host-parasite
+interactions}. (Oxford University Press, 2010).
+
+\item Cavender-Bares, J., Kozak, K. H., Fine, P. V. A. \& Kembel, S.
+W. The merging of community ecology and phylogenetic
+biology. \emph{Ecol. Lett.} \textbf{12,} 693--715 (2009).
+
+\item Balbuena, J. A., Míguez-Lozano, R. \& Blasco-Costa, I. \emph{et al.}
+PACo: A Novel Procrustes Application to Cophylogenetic Analysis.
+\emph{PLoS ONE} \textbf{8,} e61048 (2013).
+
+\item Ives, A. R. \& Helmus, M. R. Phylogenetic Metrics of
+Community Similarity. \emph{The American Naturalist} \textbf{176,}
+E128--E142 (2010).
+
+\end{enumerate}
+
+%% Here is the endmatter stuff: Supplementary Info, etc.
+%% Use \item's to separate, default label is "Acknowledgements"
+
+\begin{addendum}
+ \item We thank Juan Antonio Balbuena for
+discussions about the \emph{PACo} method, and members of the Stouffer
+and Tylianakis groups for comments on an early draft of this manuscript.
+Funding to TP and DBS was provided by a Marsden Fund Fast-Start grant
+(UOC-1101) and to DBS by a Rutherford Discovery Fellowship, both
+administered by the Royal Society of New Zealand.
+ \item[Competing Interests] The authors declare that they have no
+competing financial interests.
+ \item[Correspondence] Correspondence and requests for materials
+should be addressed to T.P.~(email: tim@poisotlab.io).
+\end{addendum}
+
+\end{document}

### 2015-06-05 manuscript/pnas.tex
ALL the files

%% PNAStwoS.tex
%% Sample file to use for PNAS articles prepared in LaTeX
%% For two column PNAS articles
%% Version1: Apr 15, 2008
%% Version2: Oct 04, 2013

%% BASIC CLASS FILE
\documentclass{pnastwo}

%% ADDITIONAL OPTIONAL STYLE FILES Font specification

%\usepackage{pnastwoF}

%% OPTIONAL MACRO DEFINITIONS
\def\s{\sigma}
%%%%%%%%%%%%
%% For PNAS Only:
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%\setcounter{page}{2687} %Set page number here if desired
%%%%%%%%%%%%

\begin{document}

\title{$title$}

\author{Roberta Graff\affil{1}{University of Cambridge, Cambridge,
United Kingdom},
Javier de Ruiz Garcia\affil{2}{Universidad de Murcia, Bioquimica y Biologia
Molecular, Murcia, Spain},
\and
Franklin Sonnery\affil{2}{}}

\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

%%%Newly updated.
%%% If significance statement need, then can use the below command otherwise just delete it.
\significancetext{RJSM and ACAC developed the concept of the study. RJSM conducted the analysis, data interpretation and drafted the manuscript. AGB contributed to the development of the statistical methods, data interpretation and drafting of the manuscript.}

\maketitle

\begin{article}
\begin{abstract}
   $abstract$
\end{abstract}

\keywords{monolayer | structure | x-ray reflectivity | molecular electronics}

\abbreviations{SAM, self-assembled monolayer; OTS, octadecyltrichlorosilane}

\end{article}

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figsamp.eps}}
\caption{LKB1 phosphorylates Thr-172 of AMPK$\alpha$ \textit{in vitro}
and activates its kinase activity.}\label{afoto}
\end{figure}

\begin{figure*}[ht]
\begin{center}
\centerline{\includegraphics[width=.7\textwidth]{figsamp.eps}}
\caption{LKB1 phosphorylates Thr-172 of AMPK$\alpha$ \textit{in vitro}
and activates its kinase activity.}\label{afoto2}
\end{center}
\end{figure*}

\begin{table}[h]
\caption{Repeat length of longer allele by age of onset class.
This is what happens when the text continues.}
\begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
&\multicolumn5c{Repeat length}\\
\noalign{\vskip-11pt}
Age of onset,\\
\cline{2-6}
\vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
\hline
Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
determined by mass spectrometric assay. The $m_t$ value indicates the
average number of wells positive for the over represented allele.}
\\
\hline
\end{tabular}
\end{table}

\begin{table*}[ht]
\caption{Summary of the experimental results}
\begin{tabular*}{\hsize}
{@{\extracolsep{\fill}}rrrrrrrrrrrrr}
\multicolumn{3}{l}{Parameters}&
\multicolumn{5}{c}{Averaged Results}&
\multicolumn{5}{c}{Comparisons}\cr
\hline
\multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
\multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
\multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
\multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
&\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
$r_1/r_2$&$m_1/m_2$&
$t_1/t_{lb}$\cr
\hline
10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
.990&.390&.182&---\ \ \cr
\hline
\end{tabular*}
\end{table*}

\end{document}

### 2015-06-05 manuscript/pnastempl.tex
ALL the files

--- 2015-06-05 manuscript/maintext.tex
@@
-Coevolutionary dynamics act on both species and their interactions in
+%% PNAStwoS.tex
+%% Sample file to use for PNAS articles prepared in LaTeX
+%% For two column PNAS articles
+%% Version1: Apr 15, 2008
+%% Version2: Oct 04, 2013
+
+%% BASIC CLASS FILE
+\documentclass{pnastwo}
+
+%% ADDITIONAL OPTIONAL STYLE FILES Font specification
+
+%\usepackage{pnastwoF}
+
+%% OPTIONAL MACRO DEFINITIONS
+\def\s{\sigma}
+%%%%%%%%%%%%
+%% For PNAS Only:
+\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
+\copyrightyear{2008}
+\issuedate{Issue Date}
+\volume{Volume}
+\issuenumber{Issue Number}
+%\setcounter{page}{2687} %Set page number here if desired
+%%%%%%%%%%%%
+
+\begin{document}
+
+\title{Coevolution leaves a stronger imprint on interactions than on community structure}
+
+\author{Timoth\'ee Poisot\affil{1}{School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
+\affil{2}{Département des Sciences Biologiques, Université de Montréal, Montréal, Canada}
+\affil{3}{Québec Centre for Biodiversity Sciences, Montréal, Canada}\and
+Daniel B. Stouffer\affil{1}{}}
+
+\contributor{Submitted to Proceedings of the National Academy of Sciences
+of the United States of America}
+
+%%%Newly updated.
+%%% If significance statement need, then can use the below command otherwise just delete it.
+\significancetext{Every ecological community is ultimately the outcome of evolutionary and coevolutionary processes in the past and ecological processes in the present.
+Previous studies have described the way that extant interactions can be captured by knowing species' evolutionary relationships while failing to quantify whether coevolution between these species underpins this observation.
+Here, we demonstrate how the fingerprint of coevolution is eroded away by distinct ecological processes, but also show that this signal is most manifest in interactions as opposed to whole networks.
+This implies that network structure is the most parsimonious mechanism by which coevolution proceeds and not the imprint it leaves on ecological communities.}
+
+\maketitle
+
+\begin{article}
+\begin{abstract}
+{Coevolutionary dynamics act on both species and their interactions in
 ways that shape ecological communities. It remains unclear, however, how
@@
 signature of past coevolution even when woven into communities that do
-not.
+not.}
+\end{abstract}
 
-Ecological interactions often exert important selective pressures on the
+\keywords{coevolution | host--parasite interactions | ecological networks | community ecology}
+
+\abbreviations{PACO, Procrustean Approach to Cophylogeny}
+
+\dropcap{E}cological interactions often exert important selective pressures on the
 species involved. For example, the phenologies of lodgepole pines and
 red crossbills respond spatially to the presence of squirrels
-\citep{benk03a} and palm species undergo changes in seed morphology in
+\cite{benk03a} and palm species undergo changes in seed morphology in
 response to the extinction of bird dispersing their seeds
-\citep{gale13}. Given that interactions are distributed in similar ways
-across communities, at both the large or small scale \citep{jord03}, it
+\cite{gale13}. Given that interactions are distributed in similar ways
+across communities, at both the large or small scale \cite{jord03}, it
 can be argued that much ecological structure is the end result of
 evolutionary or coevolutionary dynamics between species
-\citep{eklo11, stou12}. Unfortunately, while the coevolutionary dynamic
+\cite{eklo11, stou12}. Unfortunately, while the coevolutionary dynamic
 of pairs of interacting species has been well described at macro
-\citep{van73} and micro \citep{gand08} evolutionary timescales, most
+\cite{van73} and micro \cite{gand08} evolutionary timescales, most
 attempts to understand how they cascade up to the levels of diversity of
 both species and interactions found within empirical communities have
-been inconclusive \citep{hemb14}. Moreover, because coevolutionary
+been inconclusive \cite{hemb14}. Moreover, because coevolutionary
 dynamics are often presented as a key driving force behind ecological
-structure across both time and space \citep{thom05}, it is crucial to
+structure across both time and space \cite{thom05}, it is crucial to
 determine the scale at which they are both relevant and quantifiable.
@@
 communities is quantified as the degree of matching between the
-phylogenies of two sets of interacting organisms \citep{lege02}. This
+phylogenies of two sets of interacting organisms \cite{lege02}. This
 notion builds on the century-old idea that extant species interact in a
-way similar to the way their ancestors did \citep{fahr13}, but it is
+way similar to the way their ancestors did \cite{fahr13}, but it is
 considerably more restrictive than just phylogenetic conservation of
-species' interactions \citep{reze07, eklo11} because it additional
+species' interactions \cite{reze07, eklo11} because it additional
 higher-order constraints. More explicitly, communities that have
@@
 trees and (ii) have species at matching positions in the trees that tend
-to interact \citep{page03}. On the other hand, many ecological and
+to interact \cite{page03}. On the other hand, many ecological and
 evolutionary processes that occur locally are expected to blur
-community-wide coevolutionary signal \citep{pois15}. One possible
+community-wide coevolutionary signal \cite{pois15}. One possible
 explanation is that interactions can display substantial turnover at
-ecologically relevant temporal and spatial scales \citep{pois12c}: the
+ecologically relevant temporal and spatial scales \cite{pois12c}: the
 same two species can interact in different ways under the effect of
@@
 phenologies, variations in population abundances, and chance events
-\citep{pois14}. It is unclear, however, whether these mechanisms
+\cite{pois15a}. It is unclear, however, whether these mechanisms
 influence how the coevolutionary signal within individual interactions
@@
 rodents and their ectoparasites from 51 sites across Western to Eastern
-Europe \citep{kras12b} (Methods Summary). This dataset is uniquely
+Europe \cite{kras12b} (Methods). This dataset is uniquely
 suited for this task as it represents a paradigmatic system in which
 species-species interactions are thought to be driven by macro-evolution
-and co-speciation events \citep{vern09}, and coevolutionary signal is
-indeed significant at the continental level \citep{kras12a}
+and co-speciation events \cite{vern09}, and coevolutionary signal is
+indeed significant at the continental level \cite{kras12a}
 (\(p \leq 10^{-4}\); Methods). Importantly, it also provides spatial
@@
 As host-macroparasite interactions are hypothesized to be both
-ecologically constrained and evolutionary conserved \citep{comb01}, the
+ecologically constrained and evolutionary conserved \cite{comb01}, the
 congruence observed at the continental level sets the baseline for what
@@
 about the behaviour of individual interactions, despite the fact most
-coevolutionary mechanisms act at the interaction level \citep{thom99}.
+coevolutionary mechanisms act at the interaction level \cite{thom99}.
 As might be expected, we observe here that networks with interactions
@@
 differ in how frequently they vary when the species involved co-occur
-\citep{olit14}. Once more, the literature on host-parasite interactions
+\cite{olit14}. Once more, the literature on host-parasite interactions
 usually assumes that the reason why some interactions are more frequent
 is because they reflect a significant past history of coevolution
-\citep{mora10}. If this were true, we should observe a significant,
+\cite{mora10}. If this were true, we should observe a significant,
 positive correlation between the probability of observing an interaction
@@
 assumption that phylogenetic structure is a key driver of community
-structure \citep{cave09}, these data reveal that this impact is actually
+structure \cite{cave09}, these data reveal that this impact is actually
 minimal at ecologically relevant spatial scales. Despite all the above,
@@
 
-\section{Methods}\label{methods}
-
-We use data on observations of interactions between 121 species of
+\begin{materials}
+\section{Data provenance} We use data on observations of interactions between 121 species of
 rodents and 205 species of parasitic fleas in 51 locations across Europe
-\citep{kras12b} to build 51 species-species interaction networks.
+\cite{kras12b} to build 51 species-species interaction networks.
 Interactions were measured by combing rodents for fleas, a method that
@@
 
-In our study, we define threes scales for the network data and
+\section{Spatial scales} In our study, we define threes scales for the network data and
 analysis---continental, regional, and local. The continental scale is
 the aggregated ``metanetwork'' which includes all potential interactions
-between co-occurring species \citep{pois12c} (\emph{i.e.}, all species
+between co-occurring species \cite{pois12c} (\emph{i.e.}, all species
 and all their interactions across the 51 networks). Within each site,
@@
 
-We quantified the coevolutionary signal in terms of the degree of
+\section{Quantifcation of coevolutionary signal} We quantified the coevolutionary signal in terms of the degree of
 matching between host and parasite phylogenies given knowledge of
-species interactions using the \emph{PACO} method \citep{balb13}, which
+species interactions using the \emph{PACO} method \cite{balb13}, which
 is robust to variations in number of species. \emph{PACO} provides
@@
 signal?). We measured the phylogenetic dissimilarity between two sites
-for hosts and parasites using PCD \citep{ives10}, a measure that
+for hosts and parasites using PCD \cite{ives10}, a measure that
 accounts for the dissimilarity of species, corrected for the
@@
 same distance from the root).
+\end{materials}
 
-\textbf{Acknowledgements.} We thank Juan Antonio Balbuena for
+\begin{acknowledgments}
+We thank Juan Antonio Balbuena for
 discussions about the \emph{PACo} method, and members of the Stouffer
@@
 Rutherford Discovery Fellowship, both administered by the Royal Society
-of New Zealand.
+of New Zealand. TP received additional support through a Starting grant from the 
+Universit\'e de Montr\'eal, and through a NSERC Discovery grant.
+\end{acknowledgments}
 
-\clearpage
+\begin{thebibliography}{10}
 
-\section{Figures}\label{figures}
+\bibitem{benk03a}
+Benkman CW, Parchman TL, Favis A, Siepielski AM (2003) Reciprocal selection
+  causes a coevolutionary arms race between crossbills and lodgepole pine.
+\newblock {\em Am. Nat.} 162(2):182--194.
 
-\begin{figure}[htbp]
+\bibitem{gale13}
+Galetti M et~al. (2013) Functional extinction of birds drives rapid
+  evolutionary changes in seed size.
+\newblock {\em Science} 340(6136):1086--1090.
+
+\bibitem{jord03}
+Jordano P, Bascompte J, Olesen JM (2003) Invariant properties in coevolutionary
+  networks of plant-animal interactions.
+\newblock {\em Ecol. Lett.} 6(1):69--81.
+
+\bibitem{eklo11}
+Eklof A, Helmus MR, Moore M, Allesina S, Ekl{\"o}f A (2011) Relevance of
+  evolutionary history for food web structure.
+\newblock {\em Proc. R. Soc. B Biol. Sci.} 279(November 2011):1588--1596.
+
+\bibitem{stou12}
+Stouffer DB, Sales-Pardo M, Sirer MI, Bascompte J (2012) Evolutionary
+  conservation of species' roles in food webs.
+\newblock {\em Science} 335(6075):1489--1492.
+
+\bibitem{van73}
+Van~Valen L (1973) A new evolutionary law.
+\newblock {\em Evol. Theory} 1(1):1--30.
+
+\bibitem{gand08}
+Gandon S, Buckling A, Decaestecker E, Day T (2008) Host-parasite coevolution
+  and patterns of adaptation across time and space.
+\newblock {\em J. Evol. Biol.} 21(6):1861--1866.
+
+\bibitem{hemb14}
+Hembry DH, Yoder JB, Goodman KR (2014) Coevolution and the diversification of
+  life.
+\newblock {\em The American Naturalist} 184(4):425--438.
+
+\bibitem{thom05}
+Thompson JN (2005) {\em The Geographic Mosaic of Coevolution}.
+\newblock (University Of Chicago Press).
+
+\bibitem{lege02}
+Legendre P, Desdevises Y, Bazin E (2002) A statistical test for host-parasite
+  coevolution.
+\newblock {\em Syst. Biol.} 51(2):217--234.
+
+\bibitem{fahr13}
+Fahrenholz H (1913) Ectoparasiten und abstammungslehre.
+\newblock {\em Zool. Anz.} 41:371--374.
+
+\bibitem{reze07}
+Rezende EL, Lavabre JE, Guimar{\~a}es PR, Jordano P, Bascompte J (2007)
+  Non-random coextinctions in phylogenetically structured mutualistic networks.
+\newblock {\em Nature} 448(7156):925--8.
+
+\bibitem{page03}
+Page RDM (2003) {\em Tangled trees: Phylogeny, cospeciation, and coevolution}.
+\newblock (University of Chicago Press).
+
+\bibitem{pois15}
+Poisot T (2015) When is cophylogeny evidence of coevolution? in {\em
+  Evolutionary Ecology of Host-Parasite Systems}, eds.{} Morand S, Littlewood
+  DT, Poulin R.
+\newblock (Cambridge University Press).
+
+\bibitem{pois12c}
+Poisot T, Canard E, Mouillot D, Mouquet N, Gravel D (2012) The dissimilarity of
+  species interaction networks.
+\newblock {\em Ecol Lett} 15(12):1353--1361.
+
+\bibitem{pois15a}
+Poisot T, Stouffer DB, Gravel D (2015) Beyond species: why ecological
+  interaction networks vary through space and time.
+\newblock {\em Oikos} 124(3):243--251.
+
+\bibitem{kras12b}
+(2012) Data from: Phylogenetic signal in module composition and species
+  connectivity in compartmentalized host-parasite networks.
+
+\bibitem{vern09}
+Verneau O, Du~Preez L, Badets M (2009) Lessons from parasitic flatworms about
+  evolution and historical biogeography of their vertebrate hosts.
+\newblock {\em C. R. Biol.} 332(2):149--158.
+
+\bibitem{kras12a}
+Krasnov BR et~al. (2012) Phylogenetic signal in module composition and species
+  connectivity in compartmentalized host-parasite networks.
+\newblock {\em {The American Naturalist}} 179(4):501--511.
+
+\bibitem{comb01}
+Combes C (2001) {\em Parasitism - The Ecology and Evolution of Intimate
+  Interactions}.
+\newblock (University Of Chicago Press).
+
+\bibitem{thom99}
+Thompson JN (1999) The raw material for coevolution.
+\newblock {\em Oikos} 84(1):5--16.
+
+\bibitem{olit14}
+Olito C, Fox JW (2014) Species traits and abundances predict metrics of
+  plant{\textendash}pollinator network structure, but not pairwise
+  interactions.
+\newblock {\em Oikos} pp. n/a--n/a.
+
+\bibitem{mora10}
+Morand S, Krasnov B, eds. (2010) {\em Biogreography of host-parasite
+  interactions}.
+\newblock (Oxford University Press, Oxford).
+
+\bibitem{cave09}
+Cavender-Bares J, Kozak KH, Fine PVA, Kembel SW (2009) The merging of community
+  ecology and phylogenetic biology.
+\newblock {\em Ecol. Lett.} 12(7):693--715.
+
+\bibitem{balb13}
+Balbuena JA, M{\'\i}guez-Lozano R, Blasco-Costa I (2013) {PACo}: A novel
+  procrustes application to cophylogenetic analysis.
+\newblock {\em {PLoS} {ONE}} 8(4):e61048.
+
+\bibitem{ives10}
+Ives AR, Helmus MR (2010) Phylogenetic metrics of community similarity.
+\newblock {\em The American Naturalist} 176(5):E128--E142.
+
+\end{thebibliography}
+
+\end{article}
+
+\begin{figure}[p]
 \centering
-\includegraphics{../figures/figure1.pdf}
+\includegraphics[width=\textwidth]{figure1.pdf}
 \caption{Spatial distribution of coevolutionary signal across the 51
@@
 
-\begin{figure}[htbp]
+\begin{figure}[p]
 \centering
-\includegraphics{../figures/figure4.pdf}
+\includegraphics[width=\textwidth]{figure4.pdf}
 \caption{Distribution of coevolutionary signal at the network and
@@
 
-\begin{figure}[htbp]
+\begin{figure}[p]
 \centering
-\includegraphics{../figures/figure3.pdf}
+\includegraphics[width=\textwidth]{figure3.pdf}
 \caption{Spatial consistency of an interaction and its contribution to
@@
 
-\begin{figure}[htbp]
+\begin{figure}[p]
 \centering
-\includegraphics{../figures/figure2.pdf}
+\includegraphics[width=\textwidth]{figure2.pdf}
 \caption{The contribution to coevolutionary signal of the interaction
@@
 
-\clearpage
+\end{document}

### 2015-07-03 code/fig3.r
figures/

@@ -4,7 +4,7 @@ fig3dat$vary = cut(fig3dat$proba, breaks=seq(0.0, 1.0, 0.2))
 
 pdf(file="../figures/figure3.pdf", height=6)
 
-boxplot(stat~vary, fig3dat, ylim=c(0,3e4), lty=1, pch=19, xlab="Interaction spatial consistency", ylab="Interaction-level contribution to coevolutionary signal")
+boxplot(stat~vary, fig3dat, ylim=rev(c(0,3e4)), lty=1, pch=19, xlab="Interaction spatial consistency", ylab="Interaction-level contribution to coevolutionary signal")
 points(jitter(match(fig3dat$vary, levels(fig3dat$vary))), fig3dat$stat, pch=21, cex=fig3dat$weight/7, bg=rgb(0, 0, 0, alpha=0.2), col=NA)
 
 dev.off()

### 2015-07-03 code/fig4.r

@@ -41,7 +41,7 @@ mi = merge(mloc, mreg)
 colnames(mi) = c(".id", "mloc", "mreg")
 allm = merge(mi, fig1dat)
 
-plot(REG~mreg, allm, pch=NA, col=2, ylab = "Relative amount of coevolutionary signal", xlab="Average interaction-level contribution to coevolutionary signal", ylim=c(0, 0.3))
+plot(REG~mreg, allm, pch=NA, col=2, ylab = "Relative amount of coevolutionary signal", xlab="Average interaction-level contribution to coevolutionary signal", ylim=c(0, 0.3), xlim=rev(range(mreg)))
 segments(x0=allm$mreg, x1=allm$mloc, y0=REG, y1=LOC, col="lightgrey")
 lines(smooth.spline(x=allm$mreg, y=REG, df=3), lty=2, col=2)
 lines(smooth.spline(x=allm$mloc, y=LOC, df=3), lty=2, col=3)
@@ -56,7 +56,7 @@ plot(density(unique(fig2dat[,c("int","rvalue")])$rvalue, from=1e3, to=max(fig2da
    xlab = "Interaction-level contribution to coevoluationary signal",
    ylab = "Probability density",
    col = NA,
-   xlim = c(0, 3e4),
+   xlim = rev(c(0, 3e4)),
    ylim = c(0, 0.0002),
    main=""
 )
@@ -86,7 +86,3 @@ legend("topleft", pch=NA, legend=c("b"), bty="n", text.font=2, cex=1.2)
 
 
 dev.off()
-
-
-
-

### 2015-07-03 manuscript/extractbib.py

@@ -1,0 +1,38 @@
+#! /usr/bin/python2
+
+import sys
+import codecs
+import bibtexparser
+
+def di2bib(di):
+    b = "@"+di['type'].upper()+"{"+di['id']+","
+    for (k, v) in di.iteritems():
+        if k not in ['type', 'id', 'link', 'timestamp', 'urldate', 'abstract', 'doi', 'keywords', 'keyword', 'month', 'shorttitle', 'file']:
+            b += k+' = {'+v+'},\n'
+    b += '}\n'
+    return b
+
+if __name__ == "__main__":
+    ## Check the number of arguments
+    if len(sys.argv) != 4:
+        raise ValueError("Wrong number of arguments")
+    else :
+        key_list = sys.argv[1]
+        bib_file = sys.argv[2]
+        out_file = sys.argv[3]
+    ## The three arguments should be strings
+    if not isinstance(key_list, str):
+        raise TypeError("The path to the list of keys should be a string")
+    if not isinstance(bib_file, str):
+        raise TypeError("The path to the bibtex library should be a string")
+    if not isinstance(out_file, str):
+        raise TypeError("The path to the output bibtex file should be a string")
+    open(out_file, 'w').close()
+    keys = [kl.rstrip(":\n") for kl in open(key_list, 'r')]
+    with open(bib_file, 'r') as bfile:
+        refs = bibtexparser.load(bfile)
+    used_entries = dict()
+    with codecs.open(out_file, encoding='utf-8', mode='a') as ofile:
+        for e in refs.entries:
+            if e['id'] in keys:
+                ofile.write(di2bib(e))

### 2015-07-03 manuscript/figures.py

@@ -1,0 +1,45 @@
+#! /usr/bin/env python
+
+import sys
+import re
+import yaml
+
+FILE = sys.argv[1]
+YAML = sys.argv[2]
+TYPE = sys.argv[3]
+
+header = open(YAML, "r")
+text = open(FILE, "r")
+copy = open(FILE+"_NEW", "wt")
+
+docs = yaml.load_all(header)
+
+for doc in docs:
+    if not doc == None:
+        if 'figure' in doc.keys():
+            for line in text:
+                mfig = False
+                for f in doc['figure']:
+                    my_regex = r"^!\{" + re.escape(f['id']) + r"\}$"
+                    if re.search(my_regex, line, re.IGNORECASE):
+                        mfig = True
+                        print line
+                        if TYPE == 'preprint':
+                            ftype = "figure"
+                            fwidth = "\\columnwidth"
+                            if "wide" in f.keys():
+                                ftype = "figure*"
+                                fwidth = "\\textwidth"
+                            copy.write("\n\\begin{" + ftype + "}[bt]\n")
+                            copy.write("\t\\centering\n")
+                            copy.write("\t\\includegraphics[width=" + fwidth + "]{" + f['file'] + "}\n")
+                            copy.write("\t\\caption{" + f['caption'] + "}\n")
+                            copy.write("\t\\label{" + f['id'] + "}\n")
+                            copy.write("\\end{" + ftype + "}\n\n")
+                if not mfig:
+                    copy.write(line)
+
+
+header.close()
+text.close()
+copy.close()

### 2015-07-18 manuscript/coevo_ms.tex
OK!

\documentclass[12pt]{article}

\usepackage[hidelinks]{hyperref}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx}

% STIX for the text
\usepackage{stix}

% Inconsolata for the code
\usepackage{inconsolata}

\usepackage{amsmath}

% Helvetica for the titles
\usepackage[scaled]{helvet}

% Spacing
\usepackage{setspace}

% Track changes
\usepackage[inline]{trackchanges}
\usepackage{color}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}

\addeditor{author.id}
\addeditor{author.id}

\usepackage[letterpaper]{geometry}
\geometry{margin=2.5cm}

\usepackage{lineno}
\linenumbers

%%% Syntax Highlighting for code  %%%
%%% Adapted from knitr book %%%
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{enumerate}
\usepackage{ctable}
\usepackage{float}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\setlength{\parskip}{1em}
\setlength{\parindent}{0pt}

{\Large\bfseries\sffamily Coevolution leaves a stronger imprint on interactions than on community
structure}
\vskip 2em

\href{http://orcid.org/0000-0002-0735-5184}{Timothée Poisot}
$^{1, 2, 3 ,\ast}$, %\\
Daniel B. Stouffer
$^{1 }$\bigskip

\small
(1) School of Biological Sciences, University of Canterbury, Christchurch,
New Zealand\\
(2) Département des Sciences Biologiques, Université de Montréal, Montréal,
Canada\\
(3) Québec Centre for Biodiversity Sciences, Montréal, Canada\\
\bigskip
\normalsize

 $\ast$ e-mail: \texttt{tim@poisotlab.io}

\bigskip

{\small
\textbf{Abstract: }Coevolutionary dynamics act on both species and their interactions in
ways that shape ecological communities. It remains unclear, however, how
the structure of communities at larger spatial scales either influences
or is influenced by local coevolutionary processes, and how mechanisms
acting at these different scales feedback onto one another. Here we show
that, although species interactions vary substantially over a
continental gradient, the coevolutionary significance of individual
interactions is maintained across different scales. Notably, this occurs
despite the fact that observed community variation at the local scale
frequently tends to weaken or remove community-wide coevolutionary
signal. When considered in terms of the interplay between community
ecology and coevolutionary theory, our results demonstrate that
individual interactions are capable and likely to show a consistent
signature of past coevolution even when woven into communities that do
not.
}\\
{\small
\textbf{Keywords:}
  markdown \,\,\,\,\,\,\,\,\,\,
  pandoc \,\,\,\,\,\,\,\,\,\,
  LaTeX \,\,\,\,\,\,\,\,\,\,
}

{\small
\textbf{Date: }
Work in progress.
}\vskip 1em

\clearpage
\doublespacing

Ecological interactions often exert important selective pressures on the
species involved. For example, the phenologies of lodgepole pines and
red crossbills respond spatially to the presence of squirrels (Benkman
et al. 2003) and palm species undergo changes in seed morphology in
response to the extinction of bird dispersing their seeds (Galetti et
al. 2013). Given that interactions are distributed in similar ways
across communities, at both the large or small scale (Jordano,
Bascompte, and Olesen 2003), it can be argued that much ecological
structure is the end result of evolutionary or coevolutionary dynamics
between species ({\textbf{???}}; Stouffer et al. 2012). Unfortunately,
while the coevolutionary dynamic of pairs of interacting species has
been well described at macro (Van Valen 1973) and micro (Gandon et al.
2008) evolutionary timescales, most attempts to understand how they
cascade up to the levels of diversity of both species and interactions
found within empirical communities have been inconclusive (Hembry,
Yoder, and Goodman 2014). Moreover, because coevolutionary dynamics are
often presented as a key driving force behind ecological structure
across both time and space (Thompson 2005), it is crucial to determine
the scale at which they are both relevant and quantifiable.

Historically, the evidence for coevolution in taxonomically diverse
communities is quantified as the degree of matching between the
phylogenies of two sets of interacting organisms (Legendre, Desdevises,
and Bazin 2002). This notion builds on the century-old idea that extant
species interact in a way similar to the way their ancestors did
(Fahrenholz 1913), but it is considerably more restrictive than just
phylogenetic conservation of species' interactions (Rezende et al. 2007;
{\textbf{???}}) because of additional higher-order constraints. More
explicitly, communities that have assembled by successive divergence
events due to coevolution should display phylogenetic congruence, that
is (i) have similar phylogenetic trees and (ii) have species at matching
positions in the trees that tend to interact (Page 2003). On the other
hand, many ecological and evolutionary processes that occur locally are
expected to blur community-wide coevolutionary signal (Poisot 2015). One
possible explanation is that interactions can display substantial
turnover at ecologically relevant temporal and spatial scales
({\textbf{???}}): the same two species can interact in different ways
under the effect of local environmental contingencies, spatial mismatch
in species phenologies, variations in population abundances, and chance
events ({\textbf{???}}). It is unclear, however, whether these
mechanisms influence how the coevolutionary signal within individual
interactions should vary across spatial scales.

\section{Methods}\label{methods}

\subsection{Data source and
pre-treatment}\label{data-source-and-pre-treatment}

We use data on observations of interactions between 121 species of
rodents and 205 species of parasitic fleas in 51 locations across Europe
({\textbf{???}}) to build 51 species-species interaction networks.
Interactions were measured by combing rodents for fleas, a method that
gives high quality data as it has a high power of detection. To account
for differential sampling effort and across site variations in
abundance, we only study the networks' incidence matrices (presence and
absence of interactions). Previous analyses revealed that this dataset
shows significant coevolutionary signal at the continental level {[}B.
R. Krasnov et al. (2012); \(p \leq 10^{-4}\), see Methods{]}.
Importantly, it also provides spatial replication and variability
({\textbf{???}}) at a scale large enough to capture macro-ecological
processes. This dataset is uniquely suited for our analysis, as it
represents a paradigmatic system in which species-species interactions
are thought to be driven by macro-evolution and co-speciation events
(Verneau, Du Preez, and Badets 2009).

The original dataset gives quantitative interaction strengths (expressed
as an averaged number of parasites per species per host). Quantitative
interactions strength, in this system, were shown to be affected to a
very high degree by local variations in abundance across sampling
locations ({\textbf{???}}), and it therefore seems unlikely that they
reflect macro-ecological processes. For this reason, we transform all
quantitative matrices into bipartite incidence matrices, in which 1
represents the presence of an interaction, and 0 its absence.

\subsection{Spatial scales and interaction spatial
consistency}\label{spatial-scales-and-interaction-spatial-consistency}

We define threes scales for the network data and their subsequent
analysis---continental, regional, and local. The continental scale is
the aggregated ``metanetwork'' which includes all documented
interactions between species from the regional species pool
({\textbf{???}}). Note that although they are reported as 0, we actually
have no information about species pairs that have never co-occured.

Within each site, the regional scale is given by the subset of
metanetwork formed by the locally present species. Hence the regional
networks are always a perfect subset of the continental network, and do
not reflect whether species were actually observed to interact locally
or not. By contrast, the local scale includes only the interactions that
were actually observed in the field at a given site. Therefore, the
local and regional networks always include the same species, but the
local network has only a subset (or, at most, an exact match) of the
interactions in the regional network.

We define the spatial consistency of every interaction as the number of
sites in which the two species involved co-occur. Note that, because of
the co-occurence issue mentioned above, this measure is only defined for
species that have been observed to \emph{interact} at least once.

\subsection{Measure of coevolutionary
signal}\label{measure-of-coevolutionary-signal}

We quantify the strength of coevolutionary signal in terms of the degree
of matching between host and parasite phylogenies, given knowledge of
species interactions. We do so using the \emph{PACo} method (Balbuena,
M{í}guez-Lozano, and Blasco-Costa 2013), which is robust to variations
in number of species and interactions. \emph{PACo} provides measures of
both the network-level congruence (\emph{i.e.}, is the network
coevolved?) and the interaction-level signal (\emph{i.e.}, what is the
contribution of each interaction to the overall coevolutionary signal?).
Importantly, and by contrast to previous methods such as \emph{ParaFit}
(Legendre, Desdevises, and Bazin 2002), \emph{PACo} allows measuring the
contribution of every interaction to the network-level signal even
though the network shows no significant coevolutionary signal. As
required by \emph{PACo}, the phylogenetic trees for hosts and parasites
were rendered ultrametric (\emph{i.e.}, all species are at the same
distance from the root).

\section{Results}\label{results}

\subsection{Local and regional scale networks show no coevolutionary
signal}\label{local-and-regional-scale-networks-show-no-coevolutionary-signal}

As host-macroparasite interactions are hypothesized to be both
ecologically constrained and evolutionary conserved (Combes 2001), the
congruence observed at the continental level sets the baseline for what
would be expected in local communities. Of course, if ecological
mechanisms reduce coevolutionary signal, we should detect coevolution at
the continental scale but not locally. Noting that variation of
interactions can decrease congruence, we analyse the data at two
different levels to test these hypotheses: first, we use \emph{regional}
interaction data---which accounts for different species composition
across sites--and second, we use the \emph{local} interaction
data---which also accounts for variation in the interactions between
observed these species (Methods Summary). Out of 51 sites, 35 show no
signal of coevolution, 11 show significant coevolutionary signal when
using the regional interactions, and 12 show significant coevolutionary
signal using the local interactions (see \emph{Supp. Mat. 1} for
network-level significance values; \autoref{maps}).

\subsection{Coevolutionary signal is predicted by the contribution of
interactions}\label{coevolutionary-signal-is-predicted-by-the-contribution-of-interactions}

These results would appear to support the idea that macro-evolutionary
processes such as co-diversification can have consequences at the
macro-ecological level but may not in fact be detectable at finer
spatial scales. On the other hand, system-level differences say little
about the behaviour of individual interactions, despite the fact most
coevolutionary mechanisms act at the interaction level (Thompson 1999).
As might be expected, we observe here that networks with interactions
that are important for coevolution at the continental scale indeed have
more coevolutionary signal at the local and regional scales alike (Fig.
2A). Intriguingly, we also find that the distribution of individual
interactions' contributions to coevolution is strongly conserved,
regardless of the scale at which the interactions are quantified (Fig.
2B). Because interactions differ in their total contribution to
coevolution, this implies that their distribution across networks is
what actually drives differences in overall coevolutionary signal.
Network-level coevolutionary signal emerges directly from the properties
of interactions and is not a property of the network itself.

\subsection{Interactions contributing to coevolution are not more
spatially
consistent}\label{interactions-contributing-to-coevolution-are-not-more-spatially-consistent}

Beyond their contribution to coevolution, interactions also ultimately
differ in how frequently they vary when the species involved co-occur
(Olito and Fox 2014). Once more, the literature on host-parasite
interactions usually assumes that the reason why some interactions are
more frequent is because they reflect a significant past history of
coevolution (Morand and Krasnov 2010). If this were true, we should
observe a significant, positive correlation between the probability of
observing an interaction and the importance of that interaction for
coevolution at the continental scale (Methods Summary). Surprisingly, we
find that neither is true here since interactions that are important for
coevolution are not more conserved (Fig. 3).

\subsection{The contribution of interactions to coevolution is
consistent across
scales}\label{the-contribution-of-interactions-to-coevolution-is-consistent-across-scales}

Ultimately, coevolutionary signal varies across scale because of the
simultaneous variation of species' interactions \emph{and} communities'
phylogenetic tree structure. In a system characterised by substantial
turnover, we would expect the contribution of each separate interaction
to differ across scales as well. Instead, we observe here that
interactions that contribute strongly to coevolutionary signal at the
continental scale \emph{also} show a significant tendency to contribute
strongly at the local (\(p<0.05\) for positive correlations in 48 out of
51 networks) and regional (in 47 out of 51 networks), and this
observation is independent of network-wide coevolutionary signal (Fig.
4). Remarkably, this result implies that the remnants of coevolution are
still locally detectable in \emph{individual interactions} even though
coevolution regularly fails to leave its imprint on most local networks.

\section{Discussion}\label{discussion}

Overall, the results of our analyses demonstrate that there is a
sizeable gap between our current understanding of coevolution as the
basis of multi-species interactions and its applicability to ecological
questions. Local networks show little to no signal of coevolution and
the strength of coevolution between two species is a surprisingly poor
predictor of how frequently they interact. In contrast to the frequent
assumption that phylogenetic structure is a key driver of community
structure (Cavender-Bares et al. 2009), these data reveal that this
impact is actually minimal at ecologically relevant spatial scales.
Despite all the above, individual interactions are able to maintain
their coevolutionary signal even when the community they are woven into
does not. Thinking more broadly, these discrepancies provide a clear
roadmap for bridging the aforementioned gap between our appreciation of
the role of coevolution and its empirically measurable outcomes. Network
structure is the most parsimonious \emph{mechanism} by which coevolution
proceeds, not the imprint coevolution leaves on ecological communities.

\textbf{Acknowledgements.} We thank Juan Antonio Balbuena for
discussions about the \emph{PACo} method, and members of the Stouffer
and Tylianakis groups for comments on an early draft of this manuscript.
We are indebted to Matt Hutchinson and Fernando Cagua for contributions
to the code of the \texttt{paco} R package. Funding to TP and DBS was
provided by a Marsden Fund Fast-Start grant (UOC-1101) and to DBS by a
Rutherford Discovery Fellowship, both administered by the Royal Society
of New Zealand.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

Balbuena, Juan Antonio, Ra{ú}l M{í}guez-Lozano, and Isabel Blasco-Costa.
2013. ``PACo: A Novel Procrustes Application to Cophylogenetic
Analysis.'' \emph{PLoS ONE} 8 (4): e61048.

Benkman, Craig W., Thomas L. Parchman, Amanda Favis, and Adam M.
Siepielski. 2003. ``Reciprocal Selection Causes a Coevolutionary Arms
Race Between Crossbills and Lodgepole Pine.'' \emph{Am. Nat.} 162 (2):
182--94.

Cavender-Bares, Jeannine, Kenneth H. Kozak, Paul V. A. Fine, and Steven
W. Kembel. 2009. ``The Merging of Community Ecology and Phylogenetic
Biology.'' \emph{Ecol. Lett.} 12 (7): 693--715.

Combes, Claude. 2001. \emph{Parasitism - The Ecology and Evolution of
Intimate Interactions}. University Of Chicago Press.

Fahrenholz, H. 1913. ``Ectoparasiten Und Abstammungslehre.'' \emph{Zool.
Anz.} 41: 371--74.

Galetti, Mauro, Roger Guevara, Marina C. C{ô}rtes, Rodrigo Fadini,
Sandro Von Matter, Abra{ã}o B. Leite, F{á}bio Labecca, et al. 2013.
``Functional Extinction of Birds Drives Rapid Evolutionary Changes in
Seed Size.'' \emph{Science} 340 (6136): 1086--90.

Gandon, Sylvain, Angus Buckling, Ellen Decaestecker, and Troy Day. 2008.
``Host-Parasite Coevolution and Patterns of Adaptation Across Time and
Space.'' \emph{J. Evol. Biol.} 21 (6): 1861--66.

Hembry, David H., Jeremy B. Yoder, and Kari Roesch Goodman. 2014.
``Coevolution and the Diversification of Life.'' \emph{The American
Naturalist} 184 (4): 425--38.

Jordano, Pedro, Jordi Bascompte, and Jens M Olesen. 2003. ``Invariant
Properties in Coevolutionary Networks of Plant-Animal Interactions.''
\emph{Ecol. Lett.} 6 (1): 69--81.

Krasnov, Boris R., Miguel A. Fortuna, David Mouillot, Irina S.
Khokhlova, Georgy I. Shenbrot, and Robert Poulin. 2012. ``Phylogenetic
Signal in Module Composition and Species Connectivity in
Compartmentalized Host-Parasite Networks.'' \emph{The American
Naturalist} 179 (4): 501--11.

Legendre, Pierre, Yves Desdevises, and Eric Bazin. 2002. ``A Statistical
Test for Host-Parasite Coevolution.'' \emph{Syst. Biol.} 51 (2):
217--34.

Morand, Serge, and Boris Krasnov, eds. 2010. \emph{Biogreography of
Host-Parasite Interactions}. Oxford: Oxford University Press.

Olito, Colin, and Jeremy W. Fox. 2014. ``Species Traits and Abundances
Predict Metrics of Plantpollinator Network Structure, but Not Pairwise
Interactions.'' \emph{Oikos}, n/a--/a.

Page, Roderick D M. 2003. \emph{Tangled Trees: Phylogeny, Cospeciation,
and Coevolution}. University of Chicago Press.

Poisot, Timoth{é}e. 2015. ``When Is Cophylogeny Evidence of
Coevolution?'' In \emph{Evolutionary Ecology of Host-Parasite Systems},
edited by Serge Morand, D T Littlewood, and Robert Poulin. Cambridge
University Press.

Rezende, Enrico L, Jessica E Lavabre, Paulo R Guimar{ã}es, Pedro
Jordano, and Jordi Bascompte. 2007. ``Non-Random Coextinctions in
Phylogenetically Structured Mutualistic Networks.'' \emph{Nature} 448
(7156): 925--8.

Stouffer, Daniel B., Marta Sales-Pardo, M. Irmak Sirer, and Jordi
Bascompte. 2012. ``Evolutionary Conservation of Species' Roles in Food
Webs.'' \emph{Science} 335 (6075): 1489--92.

Thompson, John N. 1999. ``The Raw Material for Coevolution.''
\emph{Oikos} 84 (1): 5--16.

---------. 2005. \emph{The Geographic Mosaic of Coevolution}. University
Of Chicago Press.

Van Valen, Leigh. 1973. ``A New Evolutionary Law.'' \emph{Evol. Theory}
1 (1): 1--30.

Verneau, Olivier, Louis Du Preez, and Mathieu Badets. 2009. ``Lessons
from Parasitic Flatworms About Evolution and Historical Biogeography of
Their Vertebrate Hosts.'' \emph{C. R. Biol.} 332 (2): 149--58.

\singlespacing

\clearpage
\listoffigures
\clearpage
\begin{figure}[p!]
  \centering
  \includegraphics[width=\textwidth]{../figures/figure1.pdf}
	\caption[Spatial distribution.]{Spatial distribution of coevolutionary signal across the 51 sites. For
each location, we indicate whether or not the structure of regional and
local interaction networks is consistent with phylogenetic congruence.
The colour of the circle corresponds to regionally significant or
non-significant (black and grey, respectively) while the colour of the
symbol within corresponds to locally significant or non-significant
(black and grey, respectively).}
	\label{maps}
\end{figure}
\cleardoublepage
\begin{figure}[p!]
  \centering
  \includegraphics[width=\textwidth]{../figures/figure4.pdf}
	\caption[Example figure.]{Distribution of coevolutionary signal at the network and interaction
levels. \textbf{a}, Networks that have lower coevolutionary signal at
the local or regional level are composed of interactions that on average
contribute little to coevolution at the continental scale. Dashed lines
are the cubic smoothing spline; the two levels of the same networks are
linked by solid grey lines. \textbf{b}, Overall, interactions observed
at the local, regional, and continental scale have equal contributions
to coevolutionary signal. Probability density was smoothed using a
Gaussian kernel density estimator. Raw probability densities are shown
as semi-transparent bars.}
	\label{contributions}
\end{figure}
\cleardoublepage
\begin{figure}[p!]
  \centering
  \includegraphics[width=\textwidth]{../figures/figure3.pdf}
	\caption{Spatial consistency of an interaction and its contribution to
coevolutionary signal. Spatial consistency is defined as the probability
of observing an interaction between two species given that they were
observed to co-occur. Although statistically significant, there was no
biologically meaningful relationship between spatial consistency and an
interaction's importance for coevolution in the continental network
(\(R^2 \approx 0.01\), \(\rho = -0.1\), \(p \leq 10^{-5}\)).}
	\label{consistency}
\end{figure}
\cleardoublepage
\begin{figure}[p!]
  \centering
  \includegraphics[width=\textwidth]{../figures/figure2.pdf}
	\caption{The contribution to coevolutionary signal of the interaction between two
species is maintained across scales. For every site, we show the
Pearson's correlation between interaction-level coevolutionary signal in
the continental network and the same in the local network. The size of
each point is proportional to the size of the network, and all
correlations are significant at \(\alpha = 0.05\) except in the grey
shaded area.}
	\label{scales}
\end{figure}
\cleardoublepage

\end{document}

### 2015-07-18 manuscript/extractbib.py
Coevo MS

@@ -5,10 +5,12 @@ import codecs
 import bibtexparser
 
 def di2bib(di):
-    b = "@"+di['type'].upper()+"{"+di['id']+","
+    b = "@"+di['type'].upper()+"{"+di['id']+",\n"
     for (k, v) in di.iteritems():
-        if k not in ['type', 'id', 'link', 'timestamp', 'urldate', 'abstract', 'doi', 'keywords', 'keyword', 'month', 'shorttitle', 'file']:
-            b += k+' = {'+v+'},\n'
+        if k not in ['type', 'id', 'link', 'timestamp', 'urldate', 'abstract', 'doi', 'keywords', 'keyword', 'month', 'shorttitle', 'file', 'copyright', 'issn']:
+            if k == 'collaborator':
+                k = 'author'
+            b += '\t' + k + ' = {'+v+'},\n'
     b += '}\n'
     return b
 

### 2015-09-08 code/fig1.r
Revised version

@@ -13,10 +13,10 @@ pdf(file="../figures/figure1.pdf", height=5.5)
 map <- getMap(resolution="low")
 plot(map, xlim=range(pp$x), ylim=range(pp$y), col=rgb(0.88, 0.88, 0.82), border=rgb(0.87, 0.81, 0.81), asp=1)
 
-points(pp$x, pp$y, pch=1, col=c("grey", "black")[1+(fig1dat$reg <= 0.05)], cex=1.2)
-points(pp$x, pp$y, pch=24, bg=c("grey", "black")[1+(fig1dat$loc <= 0.05)], cex=0.6, col=NA)
-legend("topright", c("Significant", "Non significant"), pch=24, bty="n", pt.bg=c("black", "grey"), pt.cex=0.6, col=NA, title="Local network")
-legend("topleft", c("Significant", "Non significant"), pch=1, bty="n", col=c("black", "grey"), pt.cex=1.2, title="Regional network")
+points(pp$x, pp$y, pch=21, bg=c("darkgrey", "black")[1+(fig1dat$loc <= 0.05)], cex=0.7, col=NA)
+points(pp$x, pp$y, pch=1, col=c("darkgrey", "black")[1+(fig1dat$reg <= 0.05)], cex=0.7, lwd=1.5)
+legend("topright", c("Significant", "Non significant"), pch=21, bty="n", pt.bg=c("black", "darkgrey"), pt.cex=0.7, col=NA, title="Local network")
+legend("topleft", c("Significant", "Non significant"), pch=1, bty="n", col=c("black", "darkgrey"), pt.cex=0.7, title="Regional network")
 box()
 
 dev.off()

### 2016-03-10 manuscript/extractbib.py
Updates before serious revision

@@ -1,40 +1,0 @@
-#! /usr/bin/python2
-
-import sys
-import codecs
-import bibtexparser
-
-def di2bib(di):
-    b = "@"+di['type'].upper()+"{"+di['id']+",\n"
-    for (k, v) in di.iteritems():
-        if k not in ['type', 'id', 'link', 'timestamp', 'urldate', 'abstract', 'doi', 'keywords', 'keyword', 'month', 'shorttitle', 'file', 'copyright', 'issn']:
-            if k == 'collaborator':
-                k = 'author'
-            b += '\t' + k + ' = {'+v+'},\n'
-    b += '}\n'
-    return b
-
-if __name__ == "__main__":
-    ## Check the number of arguments
-    if len(sys.argv) != 4:
-        raise ValueError("Wrong number of arguments")
-    else :
-        key_list = sys.argv[1]
-        bib_file = sys.argv[2]
-        out_file = sys.argv[3]
-    ## The three arguments should be strings
-    if not isinstance(key_list, str):
-        raise TypeError("The path to the list of keys should be a string")
-    if not isinstance(bib_file, str):
-        raise TypeError("The path to the bibtex library should be a string")
-    if not isinstance(out_file, str):
-        raise TypeError("The path to the output bibtex file should be a string")
-    open(out_file, 'w').close()
-    keys = [kl.rstrip(":\n") for kl in open(key_list, 'r')]
-    with open(bib_file, 'r') as bfile:
-        refs = bibtexparser.load(bfile)
-    used_entries = dict()
-    with codecs.open(out_file, encoding='utf-8', mode='a') as ofile:
-        for e in refs.entries:
-            if e['id'] in keys:
-                ofile.write(di2bib(e))

### 2016-03-10 manuscript/plmt/critic.sh

@@ -3,20 +3,22 @@
 cat $1 > $2
 
 # Additions
+perl -pi -e 's/{\+\+@(\w+) /\\add[$1]{/gm' $2
+perl -pi -e 's/{\+\+/\\add{/gm' $2
+perl -pi -e 's/\+\+}/}/gm' $2
 perl -pi -e 's/{\+\+@(\w+) (.+)\+\+}/\\add[$1]{$2}/gm' $2
 perl -pi -e 's/{\+\+(.+)\+\+}/\\add{$1}/gm' $2
 
 # Deletions
+perl -pi -e 's/{\-\-@(\w+) /\\remove[$1]{/gm' $2
+perl -pi -e 's/{\-\-/\\remove{/gm' $2
+perl -pi -e 's/\-\-}/}/gm' $2
 perl -pi -e 's/{\-\-@(\w+) (.+)\-\-}/\\remove[$1]{$2}/gm' $2
 perl -pi -e 's/{\-\-(.+)\-\-}/\\remove{$1}/gm' $2
 
 # Replacements
-perl -pi -e 's/{~~@(\w+) (.+)~>(.+)~~}/\\change[$1]{$2}{$3}/gm' $2
-perl -pi -e 's/{~~(.+)~>(.+)~~}/\\change{$1}{$2}/gm' $2
-
-# Annotation
-perl -pi -e 's/{==(.+)==}{>>@(\w+) (.+)<<}/\\annote[$2]{$1}{$3}/gm' $2
-perl -pi -e 's/{==(.+)==}{>>(.+)<<}/\\annote{$1}{$2}/gm' $2
+perl -pi -e 's/{~~@(\w+) (.+)~>(.+)~~}/\\remove{$2}\\add[$1]{$3}/gm' $2
+perl -pi -e 's/{~~(.+)~>(.+)~~}/\\remove{$1}\\add{$2}/gm' $2
 
 # Highlights
 perl -pi -e 's/{==@(\w+) (.+)==}/\\hilight{\\small{\\color{red}$1} $2}/gm' $2

### 2016-03-10 manuscript/plmt/figures.py

@@ -23,7 +23,6 @@ for doc in docs:
                     my_regex = r"^!\{" + re.escape(f['id']) + r"\}$"
                     if re.search(my_regex, line, re.IGNORECASE):
                         mfig = True
-                        print(line)
                         if TYPE == 'preprint':
                             ftype = "figure"
                             fwidth = "\\columnwidth"
@@ -32,13 +31,22 @@ for doc in docs:
                                 fwidth = "\\textwidth"
                             copy.write("\n\\begin{" + ftype + "}[bt]\n")
                             copy.write("\t\\centering\n")
-                            copy.write("\t\\includegraphics[width=" + fwidth + "]{" + f['file'] + "}\n")
+                            # TODO Check if it's a tex file and do something else
+                            if f['file'][-4:] == ".tex":
+                                print(fwidth)
+                                copy.write("\t\\begin{adjustbox}{max width = " + fwidth + "}\n")
+                                copy.write("\t\t\\input{figures/" + f['file'] + "}\n")
+                                copy.write("\t\\end{adjustbox}\n")
+                            else:
+                                copy.write("\t\\includegraphics[width=" + fwidth + "]{figures/" + f['file'] + "}\n")
                             copy.write("\t\\caption{" + f['caption'] + "}\n")
                             copy.write("\t\\label{" + f['id'] + "}\n")
                             copy.write("\\end{" + ftype + "}\n\n")
                 if not mfig:
                     copy.write(line)
-
+        else:
+            for line in text:
+                copy.write(line)
 
 header.close()
 text.close()

### 2016-03-10 manuscript/plmt/generatebib.py

@@ -1,0 +1,23 @@
+#! /usr/bin/env python3
+
+with open('plmt/bib.keys', 'r') as infile:
+    data = infile.read()
+    my_keys = data.splitlines()
+
+import tammy
+l = tammy.library()
+l.export(keys=my_keys, path=".", output="citeproc-json")
+
+keys_to_pop = ["URL", "ISSN", "files", "keyword", "archive", "license", "link", "member", "score", "subtitle", "source"]
+
+import json
+with open("default.json") as jf:
+    refs = json.load(jf)
+    for r in refs:
+        for k in keys_to_pop:
+            r.pop(k, None)
+
+with open("default.json", "w") as jf:
+    json.dump(refs, jf, sort_keys=True, indent=3)
+
+

### 2016-03-10 code/fig3.r
Figure update

@@ -4,7 +4,7 @@ fig3dat$vary = cut(fig3dat$proba, breaks=seq(0.0, 1.0, 0.2))
 
 pdf(file="../figures/figure3.pdf", height=6)
 
-boxplot(stat~vary, fig3dat, ylim=rev(c(0,3e4)), lty=1, pch=19, xlab="Interaction spatial consistency", ylab="Interaction-level contribution to coevolutionary signal")
+boxplot(stat~vary, fig3dat, ylim=rev(c(0,3e4)), lty=1, pch=19, xlab="Interaction spatial consistency", ylab="Interaction-level contribution to cophylogenetic signal")
 points(jitter(match(fig3dat$vary, levels(fig3dat$vary))), fig3dat$stat, pch=21, cex=fig3dat$weight/7, bg=rgb(0, 0, 0, alpha=0.2), col=NA)
 
 dev.off()

### 2017-04-24 manuscript/.plmt/metadata.js
revised version with new ms structure

@@ -1,0 +1,55 @@
+var fs = require('fs');
+var path = require('path');
+var yaml = require('js-yaml');
+
+// Read the document
+var writeTo = path.normalize(".metadata.yaml");
+
+// Read the header
+var infos = yaml.safeLoad(fs.readFileSync('infos.yaml', 'utf8'));
+var autho = yaml.safeLoad(fs.readFileSync('authors.yaml', 'utf8'));
+
+// Deal with authors and affiliations
+var affiliations = {};
+var current = 1;
+for (var i = 0; i < autho.length; i++) {
+  if(autho[i].affiliations) {
+    for (var j = 0; j < autho[i].affiliations.length; j++) {
+      if (affiliations[autho[i].affiliations[j]] == undefined) {
+        affiliations[autho[i].affiliations[j]] = current
+        current = current + 1
+      }
+    }
+  }
+}
+
+// Update authors
+for (var i = 0; i < autho.length; i++) {
+  if (autho[i].affiliations) {
+    for (var j = 0; j < autho[i].affiliations.length; j++) {
+      autho[i].affiliations[j] = affiliations[autho[i].affiliations[j]];
+    }
+    autho[i].affiliations.sort()
+  }
+}
+
+// Update affiliations
+var print_affiliations = []
+for (var af in affiliations) {
+  var afobject = {}
+  afobject.id = affiliations[af]
+  afobject.text = af
+  print_affiliations.push(afobject)
+}
+
+// Abstract
+var abs = fs.readFileSync('ABSTRACT', 'utf8')
+infos.abstract = abs//.replace(/[^\n]/gmi, " ")
+
+// Update infos
+infos.author = autho
+infos.affiliation = print_affiliations
+
+// Write to file
+var json = yaml.safeDump(infos);
+fs.writeFileSync('.metadata.yaml', json, 'utf8');

### 2017-04-24 manuscript/final.sh

@@ -1,14 +1,0 @@
-#! /usr/bin/bash
-
-make SOURCE=submitted.md EXT=tex TITLE=submitted OUTPUT=subm.tex
-make SOURCE=manuscript.md EXT=tex TITLE=revised OUTPUT=revi.tex
-
-latexdiff subm.tex revi.tex > resub.tex
-pdflatex resub.tex
-pdflatex resub.tex
-
-pdftops resub.pdf resub.ps
-ps2pdf13 resub.ps resub.pdf
-rm resub.ps
-
-rm {subm,revi,resub}.tex

### 2017-04-24 manuscript/plmt/index.js

@@ -1,23 +1,0 @@
-var hylla = require('hylla');
-var fs = require('fs');
-var path = require('path');
-
-// Load the library
-var lib = new hylla.Library();
-
-// Read the document
-var doc = path.normalize(process.argv[2])
-
-fs.readFile(doc, 'utf-8', function (err, data) {
-  if (err) console.log(err);
-  var pandocKeyRE = /@([a-zA-Z0-9_:]*)/g;
-  var keys = data.match(pandocKeyRE)
-    .map(function (e) {
-      return e.replace('@', '')
-    });
-  keys = keys.filter(function (e, i, a) {
-    // if (lib.entry) lib.fix(e);
-    return lib.entry(e) ? true : false;
-  })
-  lib.write("./default.json", keys);
-});

### 2017-04-24 manuscript/plmt/tables.js

@@ -1,63 +1,0 @@
-var fs = require('fs');
-var path = require('path');
-var yaml = require('js-yaml');
-
-// Read the document
-var readTo = path.normalize(process.argv[2])
-var writeTo = path.normalize(process.argv[3])
-
-// Read the header
-var meta = yaml.safeLoad(fs.readFileSync('plmt.yaml', 'utf8'));
-
-function writeTableBlock(str, p1, p2, offset, s) {
-  var block = p1;
-  for (var i = 0; i < meta.table.length; i++) {
-    var tab = meta.table[i];
-    if (tab.id === p2) {
-      var content = fs.readFileSync('tables/' + tab.file, 'utf-8', function (
-        err) {
-        if (err) console.log(err);
-      });
-
-      var latexfile = 'tables/' + tab.file.replace('.md', '.tex');
-
-      var table = fs.readFileSync(latexfile,
-        'utf-8',
-        function (err) {
-          if (err) console.log(err);
-        });
-      table = table.replace(/longtable/g, 'tabular');
-      table = table.replace(/\{tabular\}\[c\]/g, '{tabular}');
-      table = table.replace(/@\{\}/g, '');
-      table = table.replace(/\\endhead/g, '');
-      table = table.replace(/\\tabularnewline/g, ' \\\\');
-      // End
-      var type = tab.wide ? 'table*' : 'table';
-      var short = tab.short;
-      var caption = tab.caption;
-      var _CAPT = '\t\\caption' + (short ? '[' + short + ']' : '') + '{' +
-        caption + '}\n\t\\label{' + tab.id + '}\n';
-      var _BLOCKBEGIN = '\\begin{' + type + '}[bt]\n\t\\centering\n';
-      _BLOCKBEGIN += _CAPT;
-      _BLOCKBEGIN += table;
-      _BLOCKBEGIN += '\\end{' + type + '}';
-      block = _BLOCKBEGIN;
-    }
-  }
-  return block;
-}
-
-
-var data = fs.readFile(readTo, 'utf-8', function (err, data) {
-
-  if (err) console.log(err);
-
-  if (meta.table) {
-    var table = /(\?\{([a-z0-9A-Z_-]+)\}){1}/g;
-    data = data.replace(table, writeTableBlock);
-  }
-  fs.writeFileSync(writeTo, data, 'utf-8', function (err) {
-    if (err) console.log(err);
-  });
-
-});

### 2017-04-27 manuscript/manuscript.Rmd
move to Rmd to make the figures

Ecological interactions often exert important selective pressures on the species
involved. For example, the phenologies of lodgepole pines and red crossbills
respond spatially to the presence of squirrels [@benk03rsc]. Likewise, palm
species undergo changes in seed morphology in response to the extinction of
birds dispersing their seeds [@gale13feb; @john17blc]. Interactions can be lost,
too, when phenologies of the species involved shift [@raff15psf]. Interactions
are, in fact, so important that the existence of a species has been inferred by
the fact that another species bore traits that matched no other known species:
@krit91dmh relates the discovery of the moth *Xanthopan morganii*, with a
proboscis famously over a foot long, which Darwin predicted would exist based
solely on the phenology of local plant *Angraecum sesquipedale*. In addition,
interactions and the emergent structures they define are distributed in similar
ways across communities at both large or small scales [@jord03ipc]. Together,
these observations suggest that much ecological structure could be the end
result of (co)evolutionary dynamics between species [@eklo12reh; @stou12ecs].
Unfortunately, although the evolutionary dynamics of pairs of interacting
species have been well described at macro-evolutionary [@van73nel] and
micro-evolutionary [@gand08hcp] timescales, most attempts to understand how they
cascade up to the levels of diversity of both species and interactions found
within empirical communities have been inconclusive [@hemb14cdl]. This suggests
that these well-describe mechanisms may not confer substantial predictive power
when examined at scales of organization larger than the pairwise interaction.

Historically, the evidence for shared evolutionary history in taxonomically
diverse communities relied on the quantification of the degree of matching
between the phylogenies of two sets of interacting organisms, accounting for the
distributions of interactions across the phylogeny [@lege02sth]. This notion
builds on the century-old idea that extant species interact in a way similar to
the way their ancestors did [@fahr13eua; @nuis13cam; @guim11ecm]. Note that
testing these assumptions is related to, but markedly more restrictive than,
testing for phylogenetic conservatism of species' interactions [@reze07ncp;
@eklo12reh]. This is because of additional, higher-order constraints related to
the shape of both trees at *all* depths [@cave09mce; @mouq12eap], because
ancestral evolutionary innovations have a high phylogenetic inertia, and they
carry forward to extant taxa [@vale10cpr; @desd03qps; @dini08mgc]. In a way, the
true measure of phylogenetic signal of interactions should depend not only on
how they are conserved within the tree of the species establishing them (*e.g.*
parasites or pollinators), but also how these interactions at matched to the
tree of the species receiving them (*e.g.* hosts or plants). This is true
whether or not the species complex are coevolving: in fact, neutral interactions
can yield perfectly matching co-phylogenies [@pois152wc]. Consequently, many of
the systems that have been described as exhibiting significant phylogenetic
structure of interactions ultimately deviate from this last constraint, and this
can occur for a variety of factors that stem from how other species evolved and
established, lost, or maintained interactions throughout their joint
evolutionary history. Nonetheless, detecting matching phylogenies for
interacting clades indicates that their shared evolutionary history is long
standing and is therefore suggestive that their extant ecological structure is
an outcome of ancestral constraints and/or co-adaptation [@nuis15pri].

It is important to note further that discovering matching phylogenies does not
mean that coevolutionary dynamics---*sensu* @thom99rmc---took place at any time.
In fact, coevolution is not expected to necessarily result in matching
phylogenies nor are matching phylogenies only produced through coevolution
[@pois152wc]. It follows that community-level measures of phylogenetic signal,
while they *do* quantify how closely interactions are a product of phylogeny, do
not allow us to draw conclusions on coevolution. Nevertheless, interaction-level
measures are useful, in that, when expressed as the contribution of interactions
to the overall signal, they allow us to *compare* the importance of interactions
across replicated communities. Communities from the same regional pool vary
because (i) the local species pool is at best a subset of the regional species
pool and (ii) the local interactions are at best a subset of the interactions in
the regional community [@pois15swe]. This implies that (i) the phylogenetic
signal in the regional pool will be different from the signal in the local
communities, and (ii) the phylogenetic signal across local communities will
differ. Species sampling and variability of interactions, however, does no
predict (i) how the phylogenetic signal of pairwise interactions is kept or lost
at the scale of the whole community nor (ii) whether or not this variability is
related to changes in the amount of phylogenetic signal that can be detected
locally.

In this manuscript, we analyze a large dataset of over 300 species of mammalian
hosts and their ectoparasites, sampled throughout Eurasia, for which
phylogenetic relationships are known. Using a Procrustean approach to quantify
the strength of co-phylogenetic matching of interactions between host and
parasite trees [@balb13pnp], we show that locally sampled communities rarely
show strong matching despite the fact that the overall system does at the
continental scale. We then provide evidence to support the conclusion that the
amount of phylogenetic matching within a local community is predictable based on
the importance of interactions in the regional network. We finally show that the
contribution of specific interactions to phylogenetic matching is invariant
across scales, and is unrelated to their tendency to vary across space. The lack
of co-phylogenetic structure in local communities suggests that, while
interactions are undeniably important for community assembly, they might be less
so than abiotic factors.

# Methods

## Data source and pre-treatment

We use data on observations of interactions between 121 species of rodents and
205 species of parasitic fleas in 51 locations across Europe [@kras12dfp] to
build 51 species-species interaction networks. Interactions were measured by
combing rodents for fleas, a method that gives high quality data as it has a
high power of detection. The dataset also includes phylogenies for the hosts and
the parasites. Previous analyses revealed that this dataset shows significant
co-phylogenetic matching at the continental level [@kras12psm]. Importantly, it
also provides spatial replication and variability [@cana14een] at a scale large
enough to capture macro-ecological processes. This dataset is thus uniquely
suited for our analysis as it represents a thorough spatial and taxonomic
sampling of a paradigmatic system in which interspecific interactions are
thought to be driven by macro-evolution and co-speciation events [@comb01pee;
@vern09lpf].

The original dataset gives quantitative interaction strengths (expressed as an
averaged number of parasites per species per host). In this system, quantitative
interaction strengths were previously shown to be affected to a very high degree
by local variations in abundance across sampling locations [@cana14een], and it
therefore seems unlikely that they reflect macro-ecological processes.
Therefore, to account for differential sampling effort---which cannot readily be
quantified---and across site variations in abundance---which do not pertain to
macro-evolutionary processes---we only study the networks' bipartite incidence
matrices (that is, presence and absence of infection of hosts by the parasites).

## Spatial scales and interaction spatial consistency

Noting that variation of interactions across locations---which can be caused by
local ecological mechanisms as opposed to reflecting evolutionary dynamics---can
decrease congruence, we analyze the data at three different levels which we will
refer to as continental, regional, and local. Notably, the continental level
summarizes the complete dataset whereas both the regional and local levels are
location-specific scales.

*Continental* interaction data consists of the aggregated "metanetwork" which
includes all documented interactions between species from the regional species
pool [@pois12dsi]. For every location, we further define two scales of
analysis.

First, *regional* interaction data accounts for different species composition
across sites: the species that have been observed locally interact as they would
do in the *continental* network, *i.e.* if interactions did not vary across
space. This allows testing whether sampling from the regional species pool
affects co-phylogenetic matching, regardless of the distribution of
interactions. Within each site, the regional scale is given by the subset of the
metanetwork formed by the locally present species (properly speaking, the
induced subgraph of the metanetwork induced from the nodes of the local
network). Hence the regional networks are always a perfect subset of the
continental network, and do not reflect whether species were actually observed
to interact locally or not, but whether they *can* interact at all. This
*regional* network is thus a baseline estimate derived from interactions within
the species pool and measures the effect of species sampling on co-phylogenetic
matching.

Second, *local* interaction data are the actual observations at this location:
the identity of the present species, and the way they interact. In addition to
capturing the dissimilarity of species composition across sites, this allows
measuring the effect of interaction turnover across space. The local and
regional networks always include the same species, but the local network has
only a subset (or, at most, an exact match) of the interactions in the regional
network.

We finally define the spatial consistency of every interaction as the proportion
of sites in which the two co-occurring species interact with each other, or
simply

$$ S_{ij} = \frac{L_{ij}}{C_{ij}}\,. $$ {#eq:linktunover}

The spatial consistency of an interaction $S_{ij}$ between species $i$ and $j$
is therefore the ratio between the the number of locations in which they were
observed to interact ($L_{ij}$) and the number of locations in which both were
observed to be present ($C_{ij}$). Because $L_{ij} \in [0,C_{ij}]$, this measure
takes values in $[0,1]$. Larger values reflect high spatial consistency. Note
that although they are reported as 0 (*i.e.* having no interactions), we
actually have no information about species pairs that have never co-occurred;
this is a common, but hard-to-correct-for, feature of spatially replicated
datasets in which species occurrence varies [@mora15ibi]. Therefore, the only
values of $S_{ij}$ can be properly estimated are those for species pairs that
have been observed to *co-occur* at least once.

## Quantifying co-phylogenetic matching

We quantify the strength of co-phylogenetic matching in terms of the degree of
matching between host and parasite phylogenies given knowledge of extant species
interactions. We do so using the *PACo* method [@balb13pnp], which is robust to
variations in both number of species and interactions. *PACo* provides measures
of both the network-level congruence (*i.e.*, is there phylogenetic signal in
the species interactions across the entire network?) and the interaction-level
signal (*i.e.*, what is the contribution of each interaction to the overall
signal?). Because interaction-level measures provided by *PACo* operate like
residuals, larger values of this metric reflect *low* contributions to
co-phylogenetic matching. Likewise, interactions that contribute strongly to
phylogenetic congruence have smaller *PACo* values. Importantly, and in contrast
to previous methods such as *ParaFit* [@lege02sth], *PACo* also can be used to
meaningfully quantify the contribution of every interaction to the network-level
signal even in cases where the entire network shows no significant phylogenetic
signal.

All values returned by *PACo* are tested for deviation from a random expectation
[@hutc17pip], and we generated those random expectations by applying
permutations to the species interaction networks. Specifically, we applied
permutations that maintained the number of parasites for each host and the
number of hosts for each parasite. This has the effect of measuring whether
re-distributing interactions between tree tips would give rise to the same
value. We always compared the observed value to the randomized distribution
using a two-tailed statistic; thus, a significant value indicates that the
observed value is unlikely to have been observed by chance, without
pre-specifying whether or not it is larger or smaller than expected.

In PACo, the effective sample size is the number of interactions in the network,
and our interpretation of PACo's output must account for this. This is not an
issue for permutation tests, since they evaluate the significance of the
cophylogenetic signal by permutations of each network, the power of each test
varies but the test statistics can be compared. To ensure that values of the
interaction contribution to cophylogenetic signal are comparable, we normalized
them network-wise by dividing them by the maximal value of the sum of square in
PACo. While the raw values returned by PACo are not meaningfully comparable
between networks, the corrected values presented here are.

As required by *PACo*, the phylogenetic trees for hosts and parasites were
rendered ultrametric (*i.e.*, all species are at the same distance from the
root). This has the consequence of losing the temporal component of the tree
(which was not available for the parasites in the original dataset), but
standardizes phylogenetic distances in a way that satisfies *PACo*'s
requirements. Moreover, this introduces the hypothesis that the common ancestor
to the parasites was able to infect the common ancestor of the host. Note that
the same procedure was applied in the original publication based on these
phylogenetic data [@kras12psm].

```{r maps, fig.show='hide', dev='pdf', fig.height=4.1, echo=F, results='hide', warning=F, message=F, error=F}
library(rworldmap)
library(igraph)
load("data/metrics.Rdata")
load("data/paco_fig1.Rdata")
sites <- read.table("data/coordinates.csv", h=T, sep="\t")
pp <- list(x=sites$Long, y=sites$Lat)
map <- getMap(resolution="low")
par(mar=c(0,0,0,0))
plot(map, xlim=range(pp$x), ylim=range(pp$y), col="#f4f2ef", border=rgb(0.87, 0.81, 0.81))

pchs <- c(21,25)[1+(fig1dat$loc < 0.05)]
bgs <- c("white", "black")[1+(fig1dat$reg < 0.05)]

points(pp$x, pp$y, pch=pchs, bg=bgs, cex=0.9)

legend("topright", c("Significant", "Non significant"), pch=c(25,21), bty="n", pt.cex=1.2, title="Local network", col="black", pt.bg=c("white", "white"))
legend("topleft", c("Significant", "Non significant"), fill=c("black", "white"), bty="n", pt.cex=0.9, title="Regional network")
box()
```

![Spatial distribution of co-phylogenetic matching across the 51 sites. For each location, we indicate whether or not the structure of regional and local interaction networks is consistent with phylogenetic congruence. Locations where the local network shows a significant co-phylogenetic structure are marked with triangles. Locaitions where the regional network shows a significant co-phylogenetic structure are in black. See also {@tbl:contingency}.](figure/maps-1.pdf){#fig:maps width=100%}

# Results and discussion

Splitting the datasets at the continental, regional, and local levels delineates
clear quantitative predictions. At the regional scale, one can expect community
assembly to promote the co-occurrence of evolutionarily linked species pairs --
*i.e.*, a host and a parasite from lineages that interact will tend to co-occur
more often because the parasites are filtered to be present in sites where they
can find hosts. Under this situation, we expect that regional networks will have
a high degree of phylogenetic matching (because they account for the information
on potential species interactions); we do in addition expect that their
phylogenetic signal will be larger than what is found in the continental
network, since the latter represents a somewhat artefactual agglomeration of
species pairs that do not co-occur. The opposite situation (a relatively lower
phylogenetic matching) would therefore be suggestive of a weaker selection for
the co-occurrence of evolutionarily tied species pairs.

At the local scale, if interactions between species at matching phylogenetic
positions are conserved, we would expect both a similar or higher level of
phylogenetic matching between the local and the regional scale, and a positive
relationship between the frequency of interaction and its overall importance for
phylogenetic matching (interactions with a strong phylogenetic signal happen
more often). On the contrary, if local assembly proceeds largely independently
from the co-evolutionary history, the relative level of phylogenetic matching in
local networks should be the same as in the regional networks (through a
sampling effect from the distribution of interaction-level contribution to
cophylogenetic matching), but the frequency of interactions should bear no
relationship to their importance in overall matching.

## Local and regional scale networks show no co-phylogenetic matching

As host-macroparasite interactions are hypothesized to be ecologically
constrained, as a result of their being evolutionary conserved [@comb01pee], the
congruence observed at the continental level sets the baseline for what would be
expected in local communities. Of course, if ecological mechanisms (such as
filtering) reduce co-phylogenetic matching, we should detect this signal at the
continental scale but not locally. Out of 51 sites, our *PACo* analysis
indicates that 35 show no signal of co-phylogenetic matching at all, 11 show
significant co-phylogenetic matching when using the regional interactions, and
12 show significant co-phylogenetic matching using the local interactions (see
*Supp. Mat. 1* for network-level significance values; @tbl:contingency;
@fig:maps). These results support the idea that macro-evolutionary processes,
such as co-diversification, can have consequences at the macro-ecological level
but may not in fact be detectable at finer spatial scales.

```{r congruence, results='markup', echo=F}

# Local structure or no?
local <- fig1dat$loc < 0.05
isloc <- local
isloc[local] <- "Local significant"
isloc[!local] <- "Local non-significant"

# Regional structure or no?
regal <- fig1dat$reg < 0.05
isreg <- regal
isreg[regal] <- "Regional significant"
isreg[!regal] <- "Regional non-significant"

kable(table(isloc, isreg))
```
Table: Contingency table showing the number of networks with (non-)significant local and regional co-phylogenetic signal. {#tbl:contingency}

## Local and regional scale networks have the same relative co-phylogenetic matching

```{r localregional, fig.show='hide', dev='pdf', echo=F, results='hide', warning=F, message=F, error=F}

z = function(x){return((x-mean(x))/sd(x))}
plot(z(loc_ss)~z(reg_ss), fig1dat, pch=19,
  xlab="Relative cophylogenetic signal (regional)", ylab="Relative cophylogenetic signal (local)", asp=1)
abline(h=0, lty=2, col="grey")
abline(v=0, lty=2, col="grey")
abline(a=0, b=1, col="darkgrey")
```

![The regional and local networks show the same relative amount of co-phylogenetic matching. The values presented are the z-scores of the PACo statistic for the entire network, with the 1:1 relationship indicated by the solid line.](figure/localregional-1.pdf){#fig:relative width=80%}

When we compared the relative degree of co-phylogenetic matching in the local
and regional communities ({@fig:relative}), we see that the relationship between
the two is approximately linear (95% confidence interval for the correlation
coefficient $0.914$--$0.971$). This fits with the hypothesis of local networks
being assembled by a random sampling from regional networks: if interactions
between species at matching positions in both trees are maintained by the same
set of drivers, then this should be reflected in the local networks by a higher
degree of cophylogenetic matching.

## Co-phylogenetic matching is predicted by the contribution of interactions

```{r contributions, fig.show='hide', dev='pdf', echo=F, results='hide', warning=F, message=F, error=F, fig.width=10, fig.height=6}
library(RColorBrewer)
library(plyr)
palette(brewer.pal(8, "Set1"))

load("data/paco_fig2.Rdata")
load("data/paco_fig1.Rdata")
load("data/D.Rdata")

par(mfcol=c(1,2), xaxs="i", yaxs="i")

LOC <- fig1dat$loc_ss / max(D$gof$ss)
REG <- fig1dat$reg_ss / max(D$gof$ss)
imean = ddply(fig2dat[,c("site", "type", "rvalue")], .(site, type), summarize, m = mean(rvalue))
mloc = subset(imean, type=="loc")[,c("site", "m")]
colnames(mloc) = c("site", "mloc")
mreg = subset(imean, type!="loc")[,c("site", "m")]
colnames(mreg) = c("site", "mreg")
mi = merge(mloc, mreg)
colnames(mi) = c(".id", "mloc", "mreg")
allm = merge(mi, fig1dat)

plot(REG~mreg, allm, pch=NA, col=2, ylab = "Relative amount of coevolutionary signal", xlab="Average interaction-level contribution to coevolutionary signal", ylim=c(0, 0.3), xlim=rev(range(mreg)))
segments(x0=allm$mreg, x1=allm$mloc, y0=REG, y1=LOC, col="lightgrey")
lines(smooth.spline(x=allm$mreg, y=REG, df=3), lty=2, col=2)
lines(smooth.spline(x=allm$mloc, y=LOC, df=3), lty=2, col=3)
points(REG~mreg, allm, pch=19, col=2)
points(LOC~mloc, allm, pch=19, col=3)
legend("topright", fill=c(2,3), legend=c("Regional", "Local"), bty="n")
legend("topleft", pch=NA, legend=c("a"), bty="n", text.font=2, cex=1.2)
co = col2rgb(palette())/255
plot(density(unique(fig2dat[,c("int","rvalue")])$rvalue, from=1e3, to=max(fig2dat$rvalue)),
   xlab = "Interaction-level contribution to coevoluationary signal",
   ylab = "Probability density",
   col = NA,
   xlim = rev(c(0, 3e4)),
   ylim = c(0, 0.0002),
   main=""
)
hist(fig2dat$rvalue, col=rgb(co[1,1], co[2,1], co[3,1], alpha=0.3), add=T, freq=F, border=NA)
hist(subset(fig2dat, type=="reg")$score, col=rgb(co[1,2], co[2,2], co[3,2], alpha=0.3), add=T, freq=F, border=NA)
hist(subset(fig2dat, type=="loc")$score, col=rgb(co[1,3], co[2,3], co[3,3], alpha=0.3), add=T, freq=F, border=NA)
lines(density(unique(fig2dat[,c("int","rvalue")])$rvalue, from=0, to=max(fig2dat$rvalue)), lwd=2, col=1)
lines(density(subset(fig2dat, type=="reg")$score, from=0, to=max(fig2dat$rvalue)),col=2, lwd=2)
lines(density(subset(fig2dat, type=="loc")$score, from=0, to=max(fig2dat$rvalue)),col=3, lwd=2)
box()
legend("topright", fill=c(1,2,3), legend=c("Continental", "Regional", "Local"), bty="n")
legend("topleft", pch=NA, legend=c("b"), bty="n", text.font=2, cex=1.2)
```

![Distribution of co-phylogenetic matching at the network and interaction levels. **a**, Networks that have lower co-phylogenetic matching at the local or regional level are composed of interactions that on average contribute little to co-phylogenetic matching at the continental scale. co-phylogenetic matching is presented relatively to the continental level co-phylogenetic matching. Dashed lines are a cubic smoothing spline, and the two levels of the same networks are linked by solid grey lines. **b**, Overall, interactions observed at the local, regional, and continental scale have roughly equivalent contributions to co-phylogenetic matching. Probability density was smoothed using a Gaussian kernel density estimator. Raw probability densities are shown as semi-transparent bars.](figure/contributions-1.pdf){#fig:contributions width=100%}

On the other hand, system-level differences say little about the behavior of
individual interactions. Despite the fact most coevolutionary mechanisms act at
the interaction level [@thom99rmc], most *measures* of it are expressed at the
community level. We observe here that networks with interactions that are
important for co-phylogenetic matching at the continental scale are also
important for co-phylogenetic matching at the local and regional scales as well
($\rho = 0.95$; {@fig:contributions}A). Intriguingly, we also find that the
distribution of individual interactions' contributions to co-phylogenetic
matching is strongly conserved, regardless of the scale at which the
interactions are quantified ({@fig:contributions}B). Because interactions
differ between each other in terms of their total contribution to
co-phylogenetic matching, this implies that their distribution across networks
(*i.e.* whether the local network contains a sample of strongly contributing, or
weakly contributing, interactions) is what actually drives differences in
overall co-phylogenetic matching. As such, network-level co-phylogenetic
matching emerges directly from the properties of interactions and is not a
property of the network itself.

## Interactions contributing to co-phylogenetic matching are marginally more spatially consistent

```{r consistency, fig.show='hide', dev='pdf', echo=F, results='hide', warning=F, message=F, error=F, fig.width=9}
load("data/paco_fig3.Rdata")

fig3dat$vary = cut(fig3dat$proba, breaks=seq(0.0, 1.0, 0.2))

boxplot(stat~vary, fig3dat, ylim=rev(c(0,3e4)), lty=1, pch=19, xlab="Interaction spatial consistency", ylab="Interaction-level contribution to cophylogenetic signal")
points(jitter(match(fig3dat$vary, levels(fig3dat$vary))), fig3dat$stat, pch=21, cex=fig3dat$weight/7, bg=rgb(0, 0, 0, alpha=0.2), col=NA)
```

![Spatial consistency of an interaction and its contribution to co-phylogenetic matching. Note that because *PACo* gives low scores to interactions with a strong contribution to co-phylogenetic matching, the y axis is reversed. Spatial consistency is defined as the probability of observing an interaction between two species given that they were observed to co-occur (the size of the point is proportional to the number of times an interaction was observed). Although statistically significant, there was no biologically meaningful relationship between spatial consistency and an interaction's importance for co-phylogenetic matching in the continental network ($R^2 \approx 0.01$, $\rho = -0.1$, $p \leq 10^{-5}$).](figure/consistency-1.pdf){#fig:consistency width=80%}

Beyond their contribution to co-phylogenetic matching, interactions also
ultimately differ in how frequently they vary when the species involved co-occur
[@olit15staa; @troj15gvm; @cars14bdp]. This can happen, for example, when one of
the partners is able to forage for optimal resources [@bett15prk]. Once more,
the literature on host-parasite interactions assumes that the reason why some
interactions are more frequent is because they reflect a significant past
history of coevolution [@guim07iia; @mora10bhi]; that is, the ecological
constraints emerge from evolutionary conservatism. Using a weighted Pearson's
correlation between the interaction frequency, interaction contribution to
co-phylogenetic matching, and the number of observations of each interaction as
the weight, we observe that this is marginally true ($\rho \approx -0.11$. $t
\approx -5.09$ with weights; $\rho \approx -0.10$, $t \approx -4.6$ without;
both significant at $\alpha = 0.05$; {@fig:consistency}). Recall that the
*negative* correlation here arises from the fact that high interaction-level
values in PACo means *low* contribution to co-phylogenetic signal. Nevertheless,
the significance of this result ought to be tempered by the fact that the $R^2$
of both regressions is close to $0.01$. Consequently, the association between
spatial consistency and contribution to co-phylogenetic signal, while
statistically significant, explains so little variance of either quantities that
it is likely of negligible biological importance. This implies that the spatial
consistency of an interaction does not necessarily reflect its evolutionary
past, but rather (possibly) extant ecological processes.

## The contribution of interactions to co-phylogenetic matching is consistent across scales

```{r scales, fig.show='hide', dev='pdf', echo=F, results='hide', warning=F, message=F, error=F, fig.width=9}
library(RColorBrewer)
library(plyr)

load("data/paco_fig1.Rdata")
load("data/paco_fig2.Rdata")

colnames(fig1dat)[1] = "site"
fig1dat$loc = fig1dat$loc < 0.05
fig1dat$reg = fig1dat$reg < 0.05
fig2dat = merge(fig1dat, fig2dat)
fig2dat$int <- as.vector(fig2dat$int)
fig2dat <- subset(fig2dat, type=="loc")
corpval = function(x, y) cor.test(x, y)$p.value
f2d <- ddply(fig2dat, .(site, loc, reg), summarize, cor = cor(score, rvalue), l = length(int), p = corpval(score, rvalue))
f2d$type = factor(paste(f2d$reg, f2d$loc))
levels(f2d$type) = c("None", "Local only", "Regional only", "Both")
par(xaxs="i", yaxs="i")

palette(brewer.pal(8, "Set2"))

plot(rank(f2d$p, ties.method="random"), f2d$cor, cex=log(f2d$l, 10), col="darkgrey", bg=as.numeric(f2d$type), xlim=c(0, 52), ylim=c(-1, 1), pch=NA, axes=T, ylab="Correlation between local and continental contribution to coevolutionary signal", xlab=NA)
rect(49.5, -1, 52, 1, col=rgb(0.88, 0.88, 0.82), border=NA)
rug(f2d$cor, side=2, col="grey")
rug(f2d$cor, side=4, col="grey")
abline(h=0, col="lightgrey", lwd=2, lty=2)
points(rank(f2d$p, ties.method="random"), f2d$cor, cex=log(f2d$l, 10), col="darkgrey", bg=as.numeric(f2d$type), xlim=c(0, 52), ylim=c(-1, 1), pch=21)

legend(x=-1, y=-0.5, legend=levels(f2d$type), fill=c(1,2,3,4), bty='n', title="Network coevolutionary signal", title.adj=7, xjust=0)
legend(x=-1.25, y=-0.1, legend=c(10, 30, 100), pch=19, bty='n', title="Number of interactions", title.adj=8, pt.cex=log(c(10, 30, 100),10))

box()
```

![The contribution to co-phylogenetic matching of the interaction between two species is maintained across scales. For every site (ranked on the x axis), we show the Pearson's correlation between interaction-level values of co-phylogenetic matching in the continental network and the same in the local network. The size of each point is proportional to the size of the network, and correlations for all sites are significant at $\alpha = 0.05$ except for those falling in the grey shaded area.](figure/scales-1.pdf){#fig:scales width=100%}

Ultimately, co-phylogenetic matching varies across scale because of the
simultaneous variation of species' interactions *and* communities' phylogenetic
tree structure. In a system characterised by substantial turnover, we would
expect the contribution of each separate interaction to differ across scales as
well. Instead, we observe here that interactions that contribute strongly to
co-phylogenetic matching at the continental scale *also* show a significant
tendency to contribute strongly at the local ($p < 0.05$ for positive
correlations in 48 out of 51 networks) and regional (in 47 out of 51 networks),
and this observation is independent of network-wide co-phylogenetic matching
({@fig:scales}). Remarkably, this result implies that the remnants of
co-phylogenetic inertia are still locally detectable in *individual
interactions* even though shared evolutionary history regularly fails to leave
its imprint on most local networks.

# Conclusions

Overall, the results of our study demonstrate that there is a sizeable gap
between our current understanding of host-parasite co-evolution as the basis of
multi-species interactions, its phylogenetic consequences, and their
applicability to ecological questions. Our results suggest that, while the
continental-scale system might show a strong signal of past coevolution through
significantly matching phylogenies (which was also reported, through different
analyses, by other studies of this system), the quasi-entirety of this signal is
lost when species and their interactions are filtered to assemble local
communities. That there is no further loss of signal from the regional to the
local scale strongly suggests that the loss of signal from the continental to
regional scale is due to species sampling in a manner that proceeds
independently of the evolutionary history of species pairs. Because regional and
local networks have the same species, the difference between them stems from the
loss of some species interactions locally. It would therefore seem that local
species pools in this system are also driven by the interaction between abiotic
conditions and species tolerance, in addition to potential species interactions.
Taking a step back, this result suggests that while a shared phylogenetic
history is a strong structuring force at the scale of the species pool, its
influence is overridden by other factors during species filtering and community
assembly. This does beg for future investigation of whether the importance of
phylogenetic history decays at smaller spatial scale in host-parasite
assemblages.

Recently, @coel17nbp studied the factors that shape phylogenetic signal in
bipartite interactions betweeen plants and mutualists. In contrast to our study,
they used a Mantel test to compare the two trees; this is known to be lacking
robustness [@harm10psp; @guil13dmt], which is what originally prompted the
development of PACo [@balb13pnp] or ParaFit [@lege02sth]. Leaving aside the
relative merits of the various methods, they show that phylogenetic signal is
expected to decrease when (1) dispersal probability increases (*i.e.* all
locations share the same species) and (2) the probability of interactions is
high (*i.e.* there is no loss of signal due to local interaction filtering). We
argue that the probability of interaction should not be viewed as a system-wide
measure, but rather be defined for each interaction ({@eq:linktunover}). When
this is the case, we report no relationship between the probability of
interaction, and its contribution to phylogenetic signal ({@fig:consistency}).

Local networks show little to no signal of co-phylogenetic matching, and the
strength of co-phylogenetic matching that can be ascribed to the interactions
between two species is a surprisingly poor predictor of how frequently they
interact. In contrast to the frequent assumption that phylogenetic structure is
a key driver of community structure [@cave09mce], these data reveal that this
impact is actually minimal at ecologically relevant spatial scales. And yet,
despite all the above, individual interactions are somehow able to maintain
their co-phylogenetic matching even when the community they are woven into does
not. Thinking more broadly, these discrepancies provide a clear roadmap for
bridging the gap between our appreciation of the role of shared evolutionary
history and its empirically measurable outcomes: network structure is the most
parsimonious *mechanism* by which coevolution proceeds, not the imprint
potential coevolution leaves on ecological communities.

**Acknowledgements.** We thank Juan Antonio Balbuena for discussions about the
*PACo* method, and members of the Stouffer and Tylianakis groups for comments
on an early draft of this manuscript. We thank Scott Nuismer for feedback. We
are indebted to Matt Hutchinson and Fernando Cagua for contributions to the
code of the `paco` R package. Funding to TP and DBS was provided by a Marsden
Fund Fast-Start grant (UOC-1101) and to DBS by a Rutherford Discovery
Fellowship, both administered by the Royal Society of New Zealand.

# References

### 2017-04-27 manuscript/output/manuscript.tex
move to Rmd to make the figures

\documentclass[12pt]{article}

\usepackage[table]{xcolor}

\usepackage[hidelinks]{hyperref}
\usepackage{etoolbox}
\usepackage{graphicx}
\usepackage{adjustbox}

\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

% fonts
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textgreek}
\usepackage[greek,english]{babel}
\usepackage{amsmath}

% Code highlight and colors
\usepackage{listings}
\lstset{
  numbers=left,
  tabsize=1,
  basicstyle=\small\ttfamily,
  breaklines=true
}

\usepackage{booktabs, tabularx, longtable}
\usepackage{csquotes}
\usepackage{authblk}

% Geometry block
\usepackage[letterpaper]{geometry}
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\title{Interactions retain the co-phylogenetic matching that communities lost}

\author[1,2,3]{Timothée~Poisot}
\author[1]{Daniel B.~Stouffer}
\affil[1]{Centre for Integrative Ecology, School of Biological Sciences,
University of Canterbury, Christchurch, New Zealand}
\affil[2]{Université de Montréal, Département de Sciences Biologiques, Montréal,
Canada}
\affil[3]{Québec Centre for Biodiversity Sciences, Montréal, Canada}

\begin{document}

\maketitle

\begin{abstract}
  Both species and their interactions are affected by changes that occur
  at evolutionary time-scales, and these changes shape both ecological
  communities and their phylogenetic structure. That said, extant
  ecological community structure is contingent upon random chance,
  environmental filters, and local effects. It is therefore unclear how
  much ecological signal local communities should retain. Here we show
  that, in a host--parasite system where species interactions vary
  substantially over a continental gradient, the ecological significance
  of individual interactions is maintained across different scales.
  Notably, this occurs despite the fact that observed community variation
  at the local scale frequently tends to weaken or remove community-wide
  phylogenetic signal. When considered in terms of the interplay between
  community ecology and coevolutionary theory, our results demonstrate
  that individual interactions are capable and indeed likely to show a
  consistent signature of past evolutionary history even when woven into
  communities that do not.
\end{abstract}

% pandoc-xnos: macro to create a caption without a prefix
\makeatletter
\long\def\@makenoprefixcaption#1#2{
  \vskip\abovecaptionskip
  \sbox\@tempboxa{#2}
  \ifdim \wd\@tempboxa >\hsize
    #2\par
  \else
    \global \@minipagefalse
    \hb@xt@\hsize{\hfil\box\@tempboxa\hfil}
  \fi
  \vskip\belowcaptionskip}
\makeatother

% pandoc-fignos: save original macros
\makeatletter
\let\@oldmakecaption=\@makecaption
\let\oldthefigure=\thefigure
\let\oldtheHfigure=\theHfigure
\makeatother

% pandoc-fignos: environment disables figure caption prefixes
\makeatletter
\newcounter{figno}
\newenvironment{no-prefix-figure-caption}{
  \let\@makecaption=\@makenoprefixcaption
  \renewcommand\thefigure{x.\thefigno}
  \renewcommand\theHfigure{x.\thefigno}
  \stepcounter{figno}
}{
  \let\thefigure=\oldthefigure
  \let\theHfigure=\oldtheHfigure
  \let\@makecaption=\@oldmakecaption
  \addtocounter{figure}{-1}
}
\makeatother

% pandoc-xnos: cleveref fakery
\newcommand{\plusnamesingular}{}
\newcommand{\starnamesingular}{}
\newcommand{\xrefname}[1]{\protect\renewcommand{\plusnamesingular}{#1}}
\newcommand{\Xrefname}[1]{\protect\renewcommand{\starnamesingular}{#1}}
\providecommand{\cref}{\plusnamesingular~\ref}
\providecommand{\Cref}{\starnamesingular~\ref}
\providecommand{\crefformat}[2]{}
\providecommand{\Crefformat}[2]{}

% pandoc-xnos: cleveref formatting
\crefformat{figure}{fig.~#2#1#3}
\Crefformat{figure}{Figure~#2#1#3}
\crefformat{table}{table~#2#1#3}
\Crefformat{table}{Table~#2#1#3}
\crefformat{equation}{eq.~#2#1#3}
\Crefformat{equation}{Equation~#2#1#3}

Ecological interactions often exert important selective pressures on the
species involved. For example, the phenologies of lodgepole pines and
red crossbills respond spatially to the presence of squirrels (Benkman
et al. 2003). Likewise, palm species undergo changes in seed morphology
in response to the extinction of birds dispersing their seeds (Galetti
et al. 2013; Johnson et al. 2017). Interactions can be lost, too, when
phenologies of the species involved shift (Rafferty et al. 2015).
Interactions are, in fact, so important that the existence of a species
has been inferred by the fact that another species bore traits that
matched no other known species: Kritsky (1991) relates the discovery of
the moth \emph{Xanthopan morganii}, with a proboscis famously over a
foot long, which Darwin predicted would exist based solely on the
phenology of local plant \emph{Angraecum sesquipedale}. In addition,
interactions and the emergent structures they define are distributed in
similar ways across communities at both large or small scales (Jordano
et al. 2003). Together, these observations suggest that much ecological
structure could be the end result of (co)evolutionary dynamics between
species (Eklöf et al. 2012; Stouffer et al. 2012). Unfortunately,
although the evolutionary dynamics of pairs of interacting species have
been well described at macro-evolutionary (Van Valen 1973) and
micro-evolutionary (Gandon et al. 2008) timescales, most attempts to
understand how they cascade up to the levels of diversity of both
species and interactions found within empirical communities have been
inconclusive (Hembry et al. 2014). This suggests that these
well-describe mechanisms may not confer substantial predictive power
when examined at scales of organization larger than the pairwise
interaction.

Historically, the evidence for shared evolutionary history in
taxonomically diverse communities relied on the quantification of the
degree of matching between the phylogenies of two sets of interacting
organisms, accounting for the distributions of interactions across the
phylogeny (Legendre et al. 2002). This notion builds on the century-old
idea that extant species interact in a way similar to the way their
ancestors did (Fahrenholz 1913; Guimarães Jr et al. 2011; Nuismer et al.
2013). Note that testing these assumptions is related to, but markedly
more restrictive than, testing for phylogenetic conservatism of species'
interactions (Rezende et al. 2007; Eklöf et al. 2012). This is because
of additional, higher-order constraints related to the shape of both
trees at \emph{all} depths (Cavender-Bares et al. 2009; Mouquet et al.
2012), because ancestral evolutionary innovations have a high
phylogenetic inertia, and they carry forward to extant taxa (Desdevises
et al. 2003; Diniz-Filho \& Bini 2008; Vale \& Little 2010). In a way,
the true measure of phylogenetic signal of interactions should depend
not only on how they are conserved within the tree of the species
establishing them (\emph{e.g.} parasites or pollinators), but also how
these interactions at matched to the tree of the species receiving them
(\emph{e.g.} hosts or plants). This is true whether or not the species
complex are coevolving: in fact, neutral interactions can yield
perfectly matching co-phylogenies (Poisot 2015). Consequently, many of
the systems that have been described as exhibiting significant
phylogenetic structure of interactions ultimately deviate from this last
constraint, and this can occur for a variety of factors that stem from
how other species evolved and established, lost, or maintained
interactions throughout their joint evolutionary history. Nonetheless,
detecting matching phylogenies for interacting clades indicates that
their shared evolutionary history is long standing and is therefore
suggestive that their extant ecological structure is an outcome of
ancestral constraints and/or co-adaptation (Nuismer \& Harmon 2015).

It is important to note further that discovering matching phylogenies
does not mean that coevolutionary dynamics---\emph{sensu} Thompson
(1999)---took place at any time. In fact, coevolution is not expected to
necessarily result in matching phylogenies nor are matching phylogenies
only produced through coevolution (Poisot 2015). It follows that
community-level measures of phylogenetic signal, while they \emph{do}
quantify how closely interactions are a product of phylogeny, do not
allow us to draw conclusions on coevolution. Nevertheless,
interaction-level measures are useful, in that, when expressed as the
contribution of interactions to the overall signal, they allow us to
\emph{compare} the importance of interactions across replicated
communities. Communities from the same regional pool vary because (i)
the local species pool is at best a subset of the regional species pool
and (ii) the local interactions are at best a subset of the interactions
in the regional community (Poisot et al. 2015). This implies that (i)
the phylogenetic signal in the regional pool will be different from the
signal in the local communities, and (ii) the phylogenetic signal across
local communities will differ. Species sampling and variability of
interactions, however, does no predict (i) how the phylogenetic signal
of pairwise interactions is kept or lost at the scale of the whole
community nor (ii) whether or not this variability is related to changes
in the amount of phylogenetic signal that can be detected locally.

In this manuscript, we analyze a large dataset of over 300 species of
mammalian hosts and their ectoparasites, sampled throughout Eurasia, for
which phylogenetic relationships are known. Using a Procrustean approach
to quantify the strength of co-phylogenetic matching of interactions
between host and parasite trees (Balbuena et al. 2013), we show that
locally sampled communities rarely show strong matching despite the fact
that the overall system does at the continental scale. We then provide
evidence to support the conclusion that the amount of phylogenetic
matching within a local community is predictable based on the importance
of interactions in the regional network. We finally show that the
contribution of specific interactions to phylogenetic matching is
invariant across scales, and is unrelated to their tendency to vary
across space. The lack of co-phylogenetic structure in local communities
suggests that, while interactions are undeniably important for community
assembly, they might be less so than abiotic factors.

\section{Methods}\label{methods}

\subsection{Data source and
pre-treatment}\label{data-source-and-pre-treatment}

We use data on observations of interactions between 121 species of
rodents and 205 species of parasitic fleas in 51 locations across Europe
(Krasnov et al. 2012b) to build 51 species-species interaction networks.
Interactions were measured by combing rodents for fleas, a method that
gives high quality data as it has a high power of detection. The dataset
also includes phylogenies for the hosts and the parasites. Previous
analyses revealed that this dataset shows significant co-phylogenetic
matching at the continental level (Krasnov et al. 2012a). Importantly,
it also provides spatial replication and variability (Canard et al.
2014) at a scale large enough to capture macro-ecological processes.
This dataset is thus uniquely suited for our analysis as it represents a
thorough spatial and taxonomic sampling of a paradigmatic system in
which interspecific interactions are thought to be driven by
macro-evolution and co-speciation events (Combes 2001; Verneau et al.
2009).

The original dataset gives quantitative interaction strengths (expressed
as an averaged number of parasites per species per host). In this
system, quantitative interaction strengths were previously shown to be
affected to a very high degree by local variations in abundance across
sampling locations (Canard et al. 2014), and it therefore seems unlikely
that they reflect macro-ecological processes. Therefore, to account for
differential sampling effort---which cannot readily be quantified---and
across site variations in abundance---which do not pertain to
macro-evolutionary processes---we only study the networks' bipartite
incidence matrices (that is, presence and absence of infection of hosts
by the parasites).

\subsection{Spatial scales and interaction spatial
consistency}\label{spatial-scales-and-interaction-spatial-consistency}

Noting that variation of interactions across locations---which can be
caused by local ecological mechanisms as opposed to reflecting
evolutionary dynamics---can decrease congruence, we analyze the data at
three different levels which we will refer to as continental, regional,
and local. Notably, the continental level summarizes the complete
dataset whereas both the regional and local levels are location-specific
scales.

\emph{Continental} interaction data consists of the aggregated
\enquote{metanetwork} which includes all documented interactions between
species from the regional species pool (Poisot et al. 2012). For every
location, we further define two scales of analysis.

First, \emph{regional} interaction data accounts for different species
composition across sites: the species that have been observed locally
interact as they would do in the \emph{continental} network, \emph{i.e.}
if interactions did not vary across space. This allows testing whether
sampling from the regional species pool affects co-phylogenetic
matching, regardless of the distribution of interactions. Within each
site, the regional scale is given by the subset of the metanetwork
formed by the locally present species (properly speaking, the induced
subgraph of the metanetwork induced from the nodes of the local
network). Hence the regional networks are always a perfect subset of the
continental network, and do not reflect whether species were actually
observed to interact locally or not, but whether they \emph{can}
interact at all. This \emph{regional} network is thus a baseline
estimate derived from interactions within the species pool and measures
the effect of species sampling on co-phylogenetic matching.

Second, \emph{local} interaction data are the actual observations at
this location: the identity of the present species, and the way they
interact. In addition to capturing the dissimilarity of species
composition across sites, this allows measuring the effect of
interaction turnover across space. The local and regional networks
always include the same species, but the local network has only a subset
(or, at most, an exact match) of the interactions in the regional
network.

We finally define the spatial consistency of every interaction as the
proportion of sites in which the two co-occurring species interact with
each other, or simply

\begin{equation} S_{ij} = \frac{L_{ij}}{C_{ij}}\,. \label{eq:linktunover}\end{equation}

The spatial consistency of an interaction \(S_{ij}\) between species
\(i\) and \(j\) is therefore the ratio between the the number of
locations in which they were observed to interact (\(L_{ij}\)) and the
number of locations in which both were observed to be present
(\(C_{ij}\)). Because \(L_{ij} \in [0,C_{ij}]\), this measure takes
values in \([0,1]\). Larger values reflect high spatial consistency.
Note that although they are reported as 0 (\emph{i.e.} having no
interactions), we actually have no information about species pairs that
have never co-occurred; this is a common, but hard-to-correct-for,
feature of spatially replicated datasets in which species occurrence
varies (Morales-Castilla et al. 2015). Therefore, the only values of
\(S_{ij}\) can be properly estimated are those for species pairs that
have been observed to \emph{co-occur} at least once.

\subsection{Quantifying co-phylogenetic
matching}\label{quantifying-co-phylogenetic-matching}

We quantify the strength of co-phylogenetic matching in terms of the
degree of matching between host and parasite phylogenies given knowledge
of extant species interactions. We do so using the \emph{PACo} method
(Balbuena et al. 2013), which is robust to variations in both number of
species and interactions. \emph{PACo} provides measures of both the
network-level congruence (\emph{i.e.}, is there phylogenetic signal in
the species interactions across the entire network?) and the
interaction-level signal (\emph{i.e.}, what is the contribution of each
interaction to the overall signal?). Because interaction-level measures
provided by \emph{PACo} operate like residuals, larger values of this
metric reflect \emph{low} contributions to co-phylogenetic matching.
Likewise, interactions that contribute strongly to phylogenetic
congruence have smaller \emph{PACo} values. Importantly, and in contrast
to previous methods such as \emph{ParaFit} (Legendre et al. 2002),
\emph{PACo} also can be used to meaningfully quantify the contribution
of every interaction to the network-level signal even in cases where the
entire network shows no significant phylogenetic signal.

All values returned by \emph{PACo} are tested for deviation from a
random expectation (Hutchinson et al. 2017), and we generated those
random expectations by applying permutations to the species interaction
networks. Specifically, we applied permutations that maintained the
number of parasites for each host and the number of hosts for each
parasite. This has the effect of measuring whether re-distributing
interactions between tree tips would give rise to the same value. We
always compared the observed value to the randomized distribution using
a two-tailed statistic; thus, a significant value indicates that the
observed value is unlikely to have been observed by chance, without
pre-specifying whether or not it is larger or smaller than expected.

In PACo, the effective sample size is the number of interactions in the
network, and our interpretation of PACo's output must account for this.
This is not an issue for permutation tests, since they evaluate the
significance of the cophylogenetic signal by permutations of each
network, the power of each test varies but the test statistics can be
compared. To ensure that values of the interaction contribution to
cophylogenetic signal are comparable, we normalized them network-wise by
dividing them by the maximal value of the sum of square in PACo. While
the raw values returned by PACo are not meaningfully comparable between
networks, the corrected values presented here are.

As required by \emph{PACo}, the phylogenetic trees for hosts and
parasites were rendered ultrametric (\emph{i.e.}, all species are at the
same distance from the root). This has the consequence of losing the
temporal component of the tree (which was not available for the
parasites in the original dataset), but standardizes phylogenetic
distances in a way that satisfies \emph{PACo}'s requirements. Moreover,
this introduces the hypothesis that the common ancestor to the parasites
was able to infect the common ancestor of the host. Note that the same
procedure was applied in the original publication based on these
phylogenetic data (Krasnov et al. 2012a).

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{figures/figure1.pdf}
\caption{Spatial distribution of co-phylogenetic matching across the 51
sites. For each location, we indicate whether or not the structure of
regional and local interaction networks is consistent with phylogenetic
congruence. The colour of the circle corresponds to regionally
significant or non-significant (black and grey, respectively) while the
colour of the symbol within corresponds to locally significant or
non-significant (black and grey, respectively).\label{fig:maps}}
\end{figure}

\section{Results and discussion}\label{results-and-discussion}

Splitting the datasets at the continental, regional, and local levels
delineates clear quantitative predictions. At the regional scale, one
can expect community assembly to promote the co-occurrence of
evolutionarily linked species pairs -- \emph{i.e.}, a host and a
parasite from lineages that interact will tend to co-occur more often
because the parasites are filtered to be present in sites where they can
find hosts. Under this situation, we expect that regional networks will
have a high degree of phylogenetic matching (because they account for
the information on potential species interactions); we do in addition
expect that their phylogenetic signal will be larger than what is found
in the continental network, since the latter represents a somewhat
artefactual agglomeration of species pairs that do not co-occur. The
opposite situation (a relatively lower phylogenetic matching) would
therefore be suggestive of a weaker selection for the co-occurrence of
evolutionarily tied species pairs.

At the local scale, if interactions between species at matching
phylogenetic positions are conserved, we would expect both a similar or
higher level of phylogenetic matching between the local and the regional
scale, and a positive relationship between the frequency of interaction
and its overall importance for phylogenetic matching (interactions with
a strong phylogenetic signal happen more often). On the contrary, if
local assembly proceeds largely independently from the co-evolutionary
history, the relative level of phylogenetic matching in local networks
should be the same as in the regional networks (through a sampling
effect from the distribution of interaction-level contribution to
cophylogenetic matching), but the frequency of interactions should bear
no relationship to their importance in overall matching.

\subsection{Local and regional scale networks show no co-phylogenetic
matching}\label{local-and-regional-scale-networks-show-no-co-phylogenetic-matching}

As host-macroparasite interactions are hypothesized to be ecologically
constrained, as a result of their being evolutionary conserved (Combes
2001), the congruence observed at the continental level sets the
baseline for what would be expected in local communities. Of course, if
ecological mechanisms (such as filtering) reduce co-phylogenetic
matching, we should detect this signal at the continental scale but not
locally. Out of 51 sites, our \emph{PACo} analysis indicates that 35
show no signal of co-phylogenetic matching at all, 11 show significant
co-phylogenetic matching when using the regional interactions, and 12
show significant co-phylogenetic matching using the local interactions
(see \emph{Supp. Mat. 1} for network-level significance values;
\autoref{maps}). These results support the idea that macro-evolutionary
processes, such as co-diversification, can have consequences at the
macro-ecological level but may not in fact be detectable at finer
spatial scales.

\subsection{Local and regional scale networks have the same relative
co-phylogenetic
matching}\label{local-and-regional-scale-networks-have-the-same-relative-co-phylogenetic-matching}

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{figures/figureLocReg.pdf}
\caption{The regional and local networks show the same relative amount
of co-phylogenetic matching. The values presented are the z-scores of
the PACo statistic for the entire network, with the 1:1 relationship
indicated by the solid line.\label{fig:relative}}
\end{figure}

When we compared the relative degree of co-phylogenetic matching in the
local and regional communities (\autoref{relative}), we see that the
relationship between the two is approximately linear (95\% confidence
interval for the correlation coefficient \(0.914\)--\(0.971\)). This
fits with the hypothesis of local networks being assembled by a random
sampling from regional networks: if interactions between species at
matching positions in both trees are maintained by the same set of
drivers, then this should be reflected in the local networks by a higher
degree of cophylogenetic matching.

\subsection{Co-phylogenetic matching is predicted by the contribution of
interactions}\label{co-phylogenetic-matching-is-predicted-by-the-contribution-of-interactions}

\begin{no-prefix-figure-caption}

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{figures/figure4.pdf}
\caption{Distribution of co-phylogenetic matching at the network and
interaction levels. \textbf{a}, Networks that have lower co-phylogenetic
matching at the local or regional level are composed of interactions
that on average contribute little to co-phylogenetic matching at the
continental scale. co-phylogenetic matching is presented relatively to
the continental level co-phylogenetic matching. Dashed lines are a cubic
smoothing spline, and the two levels of the same networks are linked by
solid grey lines. \textbf{b}, Overall, interactions observed at the
local, regional, and continental scale have roughly equivalent
contributions to co-phylogenetic matching. Probability density was
smoothed using a Gaussian kernel density estimator. Raw probability
densities are shown as semi-transparent bars.}\label{fg:contributions}
\end{figure}

\end{no-prefix-figure-caption}

On the other hand, system-level differences say little about the
behavior of individual interactions. Despite the fact most
coevolutionary mechanisms act at the interaction level (Thompson 1999),
most \emph{measures} of it are expressed at the community level. We
observe here that networks with interactions that are important for
co-phylogenetic matching at the continental scale are also important for
co-phylogenetic matching at the local and regional scales as well
(\(\rho = 0.95\); \autoref{contributions}A). Intriguingly, we also find
that the distribution of individual interactions' contributions to
co-phylogenetic matching is strongly conserved, regardless of the scale
at which the interactions are quantified (\autoref{contributions}B).
Because interactions differ between each other in terms of their total
contribution to co-phylogenetic matching, this implies that their
distribution across networks (\emph{i.e.} whether the local network
contains a sample of strongly contributing, or weakly contributing,
interactions) is what actually drives differences in overall
co-phylogenetic matching. As such, network-level co-phylogenetic
matching emerges directly from the properties of interactions and is not
a property of the network itself.

\subsection{Interactions contributing to co-phylogenetic matching are
marginally more spatially
consistent}\label{interactions-contributing-to-co-phylogenetic-matching-are-marginally-more-spatially-consistent}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.80000\textwidth]{figures/figure3.pdf}
\caption{Spatial consistency of an interaction and its contribution to
co-phylogenetic matching. Note that because \emph{PACo} gives low scores
to interactions with a strong contribution to co-phylogenetic matching,
the y axis is reversed. Spatial consistency is defined as the
probability of observing an interaction between two species given that
they were observed to co-occur. Although statistically significant,
there was no biologically meaningful relationship between spatial
consistency and an interaction's importance for co-phylogenetic matching
in the continental network (\(R^2 \approx 0.01\), \(\rho = -0.1\),
\(p \leq 10^{-5}\)).\label{fig:consistency}}
\end{figure}

Beyond their contribution to co-phylogenetic matching, interactions also
ultimately differ in how frequently they vary when the species involved
co-occur (Carstensen et al. 2014; Olito \& Fox 2015; Trøjelsgaard et al.
2015). This can happen, for example, when one of the partners is able to
forage for optimal resources (Betts et al. 2015). Once more, the
literature on host-parasite interactions assumes that the reason why
some interactions are more frequent is because they reflect a
significant past history of coevolution (Guimaraes et al. 2007; 2010);
that is, the ecological constraints emerge from evolutionary
conservatism. Using a weighted Pearson's correlation between the
interaction frequency, interaction contribution to co-phylogenetic
matching, and the number of observations of each interaction as the
weight, we observe that this is marginally true (\(\rho \approx -0.11\).
\(t \approx -5.09\) with weights; \(\rho \approx -0.10\),
\(t \approx -4.6\) without; both significant at \(\alpha = 0.05\);
\autoref{consistency}). Recall that the \emph{negative} correlation here
arises from the fact that high interaction-level values in PACo means
\emph{low} contribution to co-phylogenetic signal. Nevertheless, the
significance of this result ought to be tempered by the fact that the
\(R^2\) of both regressions is close to \(0.01\). Consequently, the
association between spatial consistency and contribution to
co-phylogenetic signal, while statistically significant, explains so
little variance of either quantities that it is likely of negligible
biological importance. This implies that the spatial consistency of an
interaction does not necessarily reflect its evolutionary past, but
rather (possibly) extant ecological processes.

\subsection{The contribution of interactions to co-phylogenetic matching
is consistent across
scales}\label{the-contribution-of-interactions-to-co-phylogenetic-matching-is-consistent-across-scales}

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{figures/figure2.pdf}
\caption{The contribution to co-phylogenetic matching of the interaction
between two species is maintained across scales. For every site (ranked
on the x axis), we show the Pearson's correlation between
interaction-level values of co-phylogenetic matching in the continental
network and the same in the local network. The size of each point is
proportional to the size of the network, and correlations for all sites
are significant at \(\alpha = 0.05\) except for those falling in the
grey shaded area.\label{fig:scales}}
\end{figure}

Ultimately, co-phylogenetic matching varies across scale because of the
simultaneous variation of species' interactions \emph{and} communities'
phylogenetic tree structure. In a system characterised by substantial
turnover, we would expect the contribution of each separate interaction
to differ across scales as well. Instead, we observe here that
interactions that contribute strongly to co-phylogenetic matching at the
continental scale \emph{also} show a significant tendency to contribute
strongly at the local (\(p < 0.05\) for positive correlations in 48 out
of 51 networks) and regional (in 47 out of 51 networks), and this
observation is independent of network-wide co-phylogenetic matching
(\autoref{scales}). Remarkably, this result implies that the remnants of
co-phylogenetic inertia are still locally detectable in \emph{individual
interactions} even though shared evolutionary history regularly fails to
leave its imprint on most local networks.

\section{Conclusions}\label{conclusions}

Overall, the results of our study demonstrate that there is a sizeable
gap between our current understanding of host-parasite co-evolution as
the basis of multi-species interactions, its phylogenetic consequences,
and their applicability to ecological questions. Our results suggest
that, while the continental-scale system might show a strong signal of
past coevolution through significantly matching phylogenies (which was
also reported, through different analyses, by other studies of this
system), the quasi-entirety of this signal is lost when species and
their interactions are filtered to assemble local communities. That
there is no further loss of signal from the regional to the local scale
strongly suggests that the loss of signal from the continental to
regional scale is due to species sampling in a manner that proceeds
independently of the evolutionary history of species pairs. Because
regional and local networks have the same species, the difference
between them stems from the loss of some species interactions locally.
It would therefore seem that local species pools in this system are also
driven by the interaction between abiotic conditions and species
tolerance, in addition to potential species interactions. Taking a step
back, this result suggests that while a shared phylogenetic history is a
strong structuring force at the scale of the species pool, its influence
is overridden by other factors during species filtering and community
assembly. This does beg for future investigation of whether the
importance of phylogenetic history decays at smaller spatial scale in
host-parasite assemblages.

Recently, Coelho et al. (2017) studied the factors that shape
phylogenetic signal in bipartite interactions betweeen plants and
mutualists. In contrast to our study, they used a Mantel test to compare
the two trees; this is known to be lacking robustness (Harmon \& Glor
2010; Guillot \& Rousset 2013), which is what originally prompted the
development of PACo (Balbuena et al. 2013) or ParaFit (Legendre et al.
2002). Leaving aside the relative merits of the various methods, they
show that phylogenetic signal is expected to decrease when (1) dispersal
probability increases (\emph{i.e.} all locations share the same species)
and (2) the probability of interactions is high (\emph{i.e.} there is no
loss of signal due to local interaction filtering). We argue that the
probability of interaction should not be viewed as a system-wide
measure, but rather be defined for each interaction
(\xrefname{eq.}\cref{eq:linktunover}). When this is the case, we report
no relationship between the probability of interaction, and its
contribution to phylogenetic signal
(\xrefname{fig.}\cref{fig:consistency}).

Local networks show little to no signal of co-phylogenetic matching, and
the strength of co-phylogenetic matching that can be ascribed to the
interactions between two species is a surprisingly poor predictor of how
frequently they interact. In contrast to the frequent assumption that
phylogenetic structure is a key driver of community structure
(Cavender-Bares et al. 2009), these data reveal that this impact is
actually minimal at ecologically relevant spatial scales. And yet,
despite all the above, individual interactions are somehow able to
maintain their co-phylogenetic matching even when the community they are
woven into does not. Thinking more broadly, these discrepancies provide
a clear roadmap for bridging the gap between our appreciation of the
role of shared evolutionary history and its empirically measurable
outcomes: network structure is the most parsimonious \emph{mechanism} by
which coevolution proceeds, not the imprint potential coevolution leaves
on ecological communities.

\textbf{Acknowledgements.} We thank Juan Antonio Balbuena for
discussions about the \emph{PACo} method, and members of the Stouffer
and Tylianakis groups for comments on an early draft of this manuscript.
We thank Scott Nuismer for feedback. We are indebted to Matt Hutchinson
and Fernando Cagua for contributions to the code of the \lstinline!paco!
R package. Funding to TP and DBS was provided by a Marsden Fund
Fast-Start grant (UOC-1101) and to DBS by a Rutherford Discovery
Fellowship, both administered by the Royal Society of New Zealand.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-balb13pnp}{}
\textbf{Balbuena et al.} (2013). PACo: A Novel Procrustes Application to
Cophylogenetic Analysis. \emph{PLoS ONE.} 8:e61048.

\hypertarget{ref-benk03rsc}{}
\textbf{Benkman et al.} (2003). Reciprocal selection causes a
coevolutionary arms race between crossbills and lodgepole pine. \emph{Am
Nat.} 162:182--94.

\hypertarget{ref-bett15prk}{}
\textbf{Betts et al.} (2015). Pollinator recognition by a keystone
tropical plant. \emph{Proceedings of the National Academy of Sciences of
the United States of America.} 112:3433--8.

\hypertarget{ref-cana14een}{}
\textbf{Canard et al.} (2014). Empirical evaluation of neutral
interactions in host-parasite networks. \emph{The American Naturalist.}
183:468--79.

\hypertarget{ref-cars14bdp}{}
\textbf{Carstensen et al.} (2014). Beta Diversity of Plant-Pollinator
Networks and the Spatial Turnover of Pairwise Interactions. \emph{PLoS
ONE.} 9:e112903.

\hypertarget{ref-cave09mce}{}
\textbf{Cavender-Bares et al.} (2009). The merging of community ecology
and phylogenetic biology. \emph{Ecol Lett.} 12:693--715.

\hypertarget{ref-coel17nbp}{}
\textbf{Coelho et al.} (2017). Neutral biogeography of phylogenetically
structured interaction networks. \emph{Ecography.}

\hypertarget{ref-comb01pee}{}
\textbf{Combes}. (2001). Parasitism - The Ecology and Evolution of
Intimate Interactions. University Of Chicago Press;

\hypertarget{ref-desd03qps}{}
\textbf{Desdevises et al.} (2003). Quantifying phylogenetically
structured environmental variation. \emph{Evolution.} 57:2647--52.

\hypertarget{ref-dini08mgc}{}
\textbf{Diniz-Filho \& Bini}. (2008). Macroecology, global change and
the shadow of forgotten ancestors. \emph{Glob Ecol Biogeogr.} 17:11--7.

\hypertarget{ref-eklo12reh}{}
\textbf{Eklöf et al.} (2012). Relevance of evolutionary history for food
web structure. \emph{Proceedings of the Royal Society of London B:
Biological Sciences.} 279:1588--96.

\hypertarget{ref-fahr13eua}{}
\textbf{Fahrenholz}. (1913). Ectoparasiten und abstammungslehre.
\emph{Zool Anz.} 41:371--4.

\hypertarget{ref-gale13feb}{}
\textbf{Galetti et al.} (2013). Functional Extinction of Birds Drives
Rapid Evolutionary Changes in Seed Size. \emph{Science.} 340:1086--90.

\hypertarget{ref-gand08hcp}{}
\textbf{Gandon et al.} (2008). Host-parasite coevolution and patterns of
adaptation across time and space. \emph{J Evol Biol.} 21:1861--6.

\hypertarget{ref-guil13dmt}{}
\textbf{Guillot \& Rousset}. (2013). Dismantling the Mantel tests.
Harmon, ed. \emph{Methods in Ecology and Evolution.} 4:336--44.

\hypertarget{ref-guim07iia}{}
\textbf{Guimaraes et al.} (2007). Interaction intimacy affects structure
and coevolutionary dynamics in mutualistic networks. \emph{Curr Biol.}
17:1797--803.

\hypertarget{ref-guim11ecm}{}
\textbf{Guimarães Jr et al.} (2011). Evolution and coevolution in
mutualistic networks. \emph{Ecol Lett.} 14:877--85.

\hypertarget{ref-harm10psp}{}
\textbf{Harmon \& Glor}. (2010). POOR STATISTICAL PERFORMANCE OF THE
MANTEL TEST IN PHYLOGENETIC COMPARATIVE ANALYSES. \emph{Evolution.}

\hypertarget{ref-hemb14cdl}{}
\textbf{Hembry et al.} (2014). Coevolution and the Diversification of
Life. \emph{The American Naturalist.} 184:425--38.

\hypertarget{ref-hutc17pip}{}
\textbf{Hutchinson et al.} (2017). paco: implementing Procrustean
Approach to Cophylogeny in R. \emph{Methods in Ecology and Evolution.}

\hypertarget{ref-john17blc}{}
\textbf{Johnson et al.} (2017). Biodiversity losses and conservation
responses in the Anthropocene. \emph{Science.} 356:270--5.

\hypertarget{ref-jord03ipc}{}
\textbf{Jordano et al.} (2003). Invariant properties in coevolutionary
networks of plant--animal interactions. \emph{Ecology Letters.}
6:69--81.

\hypertarget{ref-kras12psm}{}
\textbf{Krasnov et al.} (2012a). Phylogenetic Signal in Module
Composition and Species Connectivity in Compartmentalized Host-Parasite
Networks. \emph{The American Naturalist.} 179:501--11.

\hypertarget{ref-kras12dfp}{}
\textbf{Krasnov et al.} (2012b). Data from: Phylogenetic signal in
module composition and species connectivity in compartmentalized
host-parasite networks.

\hypertarget{ref-krit91dmh}{}
\textbf{Kritsky}. (1991). Darwin's Madagascan Hawk Moth Prediction.
\emph{American Entomologist.} 37:206--10.

\hypertarget{ref-lege02sth}{}
\textbf{Legendre et al.} (2002). A statistical test for host-parasite
coevolution. \emph{Syst Biol.} 51:217--34.

\hypertarget{ref-mora15ibi}{}
\textbf{Morales-Castilla et al.} (2015). Inferring biotic interactions
from proxies. \emph{Trends in Ecology \& Evolution.}

\hypertarget{ref-mouq12eap}{}
\textbf{Mouquet et al.} (2012). Ecophylogenetics: advances and
perspectives. \emph{Biol Rev.} 87:769--85.

\hypertarget{ref-nuis15pri}{}
\textbf{Nuismer \& Harmon}. (2015). Predicting rates of interspecific
interaction from phylogenetic trees. \emph{Ecol Lett.} 18:17--27.

\hypertarget{ref-nuis13cam}{}
\textbf{Nuismer et al.} (2013). Coevolution and the Architecture of
Mutualistic Networks. \emph{Evolution.} 67:338--54.

\hypertarget{ref-olit15staa}{}
\textbf{Olito \& Fox}. (2015). Species traits and abundances predict
metrics of plant--pollinator network structure, but not pairwise
interactions. \emph{Oikos.} 124:428--36.

\hypertarget{ref-pois152wc}{}
\textbf{Poisot}. (2015). 23 When is co-phylogeny evidence of
coevolution? \emph{Parasite Diversity and Diversification: Evolutionary
Ecology Meets Phylogenetics.}:420.

\hypertarget{ref-pois12dsi}{}
\textbf{Poisot et al.} (2012). The dissimilarity of species interaction
networks. \emph{Ecol Lett.} 15:1353--61.

\hypertarget{ref-pois15swe}{}
\textbf{Poisot et al.} (2015). Beyond species: why ecological
interaction networks vary through space and time. \emph{Oikos.}
124:243--51.

\hypertarget{ref-raff15psf}{}
\textbf{Rafferty et al.} (2015). Phenological shifts and the fate of
mutualisms. \emph{Oikos.} 124:14--21.

\hypertarget{ref-reze07ncp}{}
\textbf{Rezende et al.} (2007). Non-random coextinctions in
phylogenetically structured mutualistic networks. \emph{Nature.}
448:925--8.

\hypertarget{ref-stou12ecs}{}
\textbf{Stouffer et al.} (2012). Evolutionary Conservation of Species'
Roles in Food Webs. \emph{Science.} 335:1489--92.

\hypertarget{ref-thom99rmc}{}
\textbf{Thompson}. (1999). The raw material for coevolution.
\emph{Oikos.} 84:5--16.

\hypertarget{ref-troj15gvm}{}
\textbf{Trøjelsgaard et al.} (2015). Geographical variation in
mutualistic networks: similarity, turnover and partner fidelity.
\emph{Proceedings of the Royal Society B: Biological Sciences.}
282:20142925--5.

\hypertarget{ref-vale10cpr}{}
\textbf{Vale \& Little}. (2010). CRISPR-mediated phage resistance and
the ghost of coevolution past. \emph{Proc R Soc B Biol Sci.}

\hypertarget{ref-van73nel}{}
\textbf{Van Valen}. (1973). A new evolutionary law. \emph{Evol Theory.}
1:1--30.

\hypertarget{ref-vern09lpf}{}
\textbf{Verneau et al.} (2009). Lessons from parasitic flatworms about
evolution and historical biogeography of their vertebrate hosts. \emph{C
R Biol.} 332:149--58.

\hypertarget{ref-mora10bhi}{}
(2010). Biogreography of host-parasite interactions. Morand, Krasnov,
eds. Oxford: Oxford University Press;

\end{document}

### 2017-04-27 manuscript/.plmt/metadata.js

@@ -49,6 +49,7 @@ infos.abstract = abs//.replace(/[^\n]/gmi, " ")
 // Update infos
 infos.author = autho
 infos.affiliation = print_affiliations
+infos.cleveref = true
 
 // Write to file
 var json = yaml.safeDump(infos);

### 2017-05-06 manuscript/manuscript.Rmd
replies list of todos
update the MS + replies

@@
 whether or not the species complex are coevolving: in fact, neutral interactions
-can yield perfectly matching co-phylogenies [@pois152wc]. Consequently, many of
+can yield perfectly matching co-phylogenies [@pois15wce]. Consequently, many of
 the systems that have been described as exhibiting significant phylogenetic
@@
 established, lost, or maintained interactions throughout their joint
-evolutionary history. Nonetheless, detecting matching phylogenies for
-interacting clades indicates that their shared evolutionary history is long
-standing and is therefore suggestive that their extant ecological structure is
-an outcome of ancestral constraints and/or co-adaptation [@nuis15pri].
+evolutionary history (in addition to the fact that species may have different
+impacts on one another, *i.e.* the effect of any interaction on the
+community-level cophylogenetic signal is not expected to be equal). Nonetheless,
+detecting matching phylogenies for interacting clades indicates that their
+shared evolutionary history is long standing and is therefore suggestive that
+their extant ecological structure is an outcome of ancestral constraints and/or
+co-adaptation [@nuis15pri].
 
@@
 phylogenies nor are matching phylogenies only produced through coevolution
-[@pois152wc]. It follows that community-level measures of phylogenetic signal,
+[@pois15wce]. It follows that community-level measures of phylogenetic signal,
 while they *do* quantify how closely interactions are a product of phylogeny, do
@@
 **a**, Networks that have lower co-phylogenetic matching at the local or regional level are composed of interactions that on average contribute little to co-phylogenetic matching at the continental scale.
-co-phylogenetic matching is presented relatively to the continental level co-phylogenetic matching.
+Co-phylogenetic matching is presented relatively to the continental level co-phylogenetic matching.
 Dashed lines are a cubic smoothing spline, and the two levels of the same networks are linked by solid grey lines.
@@
 Probability density was smoothed using a Gaussian kernel density estimator.
-Raw probability densities are shown as semi-transparent bars.](figure/contributions-1.pdf){#fig:contributions width=100%}
+Raw probability densities are shown as semi-transparent bars.
+Interaction-level contributions are unitless, and lower values represent stronger signal.](figure/contributions-1.pdf){#fig:contributions width=100%}
 
@@
 matching is strongly conserved, regardless of the scale at which the
-interactions are quantified ({@fig:contributions}B). Because interactions
-differ between each other in terms of their total contribution to
-co-phylogenetic matching, this implies that their distribution across networks
-(*i.e.* whether the local network contains a sample of strongly contributing, or
-weakly contributing, interactions) is what actually drives differences in
-overall co-phylogenetic matching. As such, network-level co-phylogenetic
-matching emerges directly from the properties of interactions and is not a
-property of the network itself.
+interactions are quantified ({@fig:contributions}B). Because interactions differ
+between each other in terms of their total contribution to co-phylogenetic
+matching, this implies that their distribution across networks (*i.e.* whether
+the local network contains a sample of strongly contributing, or weakly
+contributing, interactions) is what actually drives differences in overall
+co-phylogenetic matching. As such, network-level co-phylogenetic matching
+emerges directly from the properties of interactions and is not a property of
+the network itself.
 
@@
 
+The lack of a relationship between interaction probability (which represents
+their ecological stability) and their contribution to the cophylogenetic process
+(which can be a proxy of their evolutionary stability) draws into the question
+of the long-term stability of interactions. Specifically, the existence of
+interactions with strong cophylogenetic contribution, but low probability, is
+puzzling. It is tempting to hypothesize that these interactions were once strong
+enough to drive (co-)speciation, but are now decaying due either to the fact
+that the host/parasite pair has been disrupted, or under the action of
+ecological processes. @janz11err show that parasites can frequently acquire
+hosts that are not closely related to their initial host. This phenomenon,
+dubbed the "parasite paradox", can be responsible for a large number of
+diversification events, as parasites will be introduced to a novel environment
+when exposed to a novel host. The acquisition of novel hosts proceeds primarily
+from ecological contacts between distantly related species. This emphasizes the
+need to account for the spatial structure of species interactions in these
+studies -- because all species do not co-occur at all places, the potential for
+ecological contact with novel hosts varies across space. Ideally, reconstruction
+of the ancestral range of the species can shed some light on whether acquisiton
+of distantly related species happened, and where.
+
 Local networks show little to no signal of co-phylogenetic matching, and the
@@
 a key driver of community structure [@cave09mce], these data reveal that this
-impact is actually minimal at ecologically relevant spatial scales. And yet,
-despite all the above, individual interactions are somehow able to maintain
-their co-phylogenetic matching even when the community they are woven into does
-not. Thinking more broadly, these discrepancies provide a clear roadmap for
-bridging the gap between our appreciation of the role of shared evolutionary
-history and its empirically measurable outcomes: network structure is the most
-parsimonious *mechanism* by which coevolution proceeds, not the imprint
-potential coevolution leaves on ecological communities.
+impact is actually minimal at ecologically relevant spatial scales, even in
+system where phylogenetic structure would be expected to have a profoundly
+strong role. And yet, despite all the above, individual interactions are somehow
+able to maintain their co-phylogenetic matching even when the community they are
+woven into does not. Thinking more broadly, these discrepancies provide a clear
+roadmap for bridging the gap between our appreciation of the role of shared
+evolutionary history and its empirically measurable outcomes: network structure
+is the most parsimonious *mechanism* by which coevolution proceeds, not the
+imprint potential coevolution leaves on ecological communities.
+
+Finally, we would like to acknowledge some limitations in the data.
+Host-parasite evolutions usually follows a number of canonical coevolutionary
+scenarios [@page03ttp]: true cospeciation, wherein the two speciation events are
+simultaneous; pseudo- or delayed-cospeciations, wherein one of the speciations
+happens after the other; host-shift, wherein the parasite acquires a new host
+(and can subsequently lose the previous one, undergo speciation, or maintain its
+ability to use it); finally, host range expansion, in which the parasite
+acquires a novel host. When the likelihood of both host and parasite extinctions
+events are added to these model, the variety of outcomes is considerable.
+@dev07wch shows that host-switch like events can result in matching trees, and
+so one could argue that the continental-level signal of tree matching can emerge
+from numerous host-shift events [although the results of @kras12psm do not
+support this scenario]. Because separating true cospeciation events from all
+other situations is difficult without time-calibrated trees, @dev13cvh suggest
+that the number of cospeciation event is inflated by cophenetic methods like
+*PACo* or *ParaFit* [although @lope01mpf reported an increased number of
+cospeciations when accounting for time of speciation events]. This re-inforces
+the need for high-quality phylogeny data calibrated for communities in which the
+interactions are known. Not only will this help make more robust inference about
+the evolution of networks [@eklo16pcf], it will also help use informations on
+species interactions embedded within networks to help understand coevoluationary
+dynamics.
 

### 2017-05-23 manuscript/manuscript.Rmd

--- 2017-04-27 manuscript/manuscript.Rmd
@@
 within empirical communities have been inconclusive [@hemb14cdl]. This suggests
-that these well-describe mechanisms may not confer substantial predictive power
+that these well-described mechanisms may not confer substantial predictive power
 when examined at scales of organization larger than the pairwise interaction.
@@
 established, lost, or maintained interactions throughout their joint
-evolutionary history. Nonetheless, detecting matching phylogenies for
-interacting clades indicates that their shared evolutionary history is long
-standing and is therefore suggestive that their extant ecological structure is
-an outcome of ancestral constraints and/or co-adaptation [@nuis15pri].
+evolutionary history (in addition to the fact that species may have different
+impacts on one another, *i.e.* the effect of any interaction on the
+community-level co-phylogenetic signal is not expected to be equal). Nonetheless,
+detecting matching phylogenies for interacting clades indicates that their
+shared evolutionary history is long standing and is therefore suggestive that
+their extant ecological structure is an outcome of ancestral constraints and/or
+co-adaptation [@nuis15pri].
 
@@
 phylogenies nor are matching phylogenies only produced through coevolution
-[@pois152wc]. It follows that community-level measures of phylogenetic signal,
+[@pois15wce]. It follows that community-level measures of phylogenetic signal,
 while they *do* quantify how closely interactions are a product of phylogeny, do
 not allow us to draw conclusions on coevolution. Nevertheless, interaction-level
-measures are useful, in that, when expressed as the contribution of interactions
+measures are useful in that, when expressed as the contribution of interactions
 to the overall signal, they allow us to *compare* the importance of interactions
@@
 communities, and (ii) the phylogenetic signal across local communities will
-differ. Species sampling and variability of interactions, however, does no
+differ. Species sampling and variability of interactions, however, do no
 predict (i) how the phylogenetic signal of pairwise interactions is kept or lost
@@
 Second, *local* interaction data are the actual observations at this location:
-the identity of the present species, and the way they interact. In addition to
+the identity of the species present, and the way they interact. In addition to
 capturing the dissimilarity of species composition across sites, this allows
@@
 observed to be present ($C_{ij}$). Because $L_{ij} \in [0,C_{ij}]$, this measure
-takes values in $[0,1]$. Larger values reflect high spatial consistency. Note
+takes values in $[0,1]$ where larger values reflect high spatial consistency. Note
 that although they are reported as 0 (*i.e.* having no interactions), we
@@
 issue for permutation tests, since they evaluate the significance of the
-cophylogenetic signal by permutations of each network, the power of each test
+co-phylogenetic signal by permutations of each network, the power of each test
 varies but the test statistics can be compared. To ensure that values of the
-interaction contribution to cophylogenetic signal are comparable, we normalized
-them network-wise by dividing them by the maximal value of the sum of square in
+interaction contribution to co-phylogenetic signal are comparable, we normalized
+them network-wise by dividing them by the maximal value of the sum of squares in
 PACo. While the raw values returned by PACo are not meaningfully comparable
@@
 phylogenetic signal will be larger than what is found in the continental
-network, since the latter represents a somewhat artefactual agglomeration of
+network, since the latter represents a somewhat artifactual agglomeration of
 species pairs that do not co-occur. The opposite situation (a relatively lower
@@
 more often). On the contrary, if local assembly proceeds largely independently
-from the co-evolutionary history, the relative level of phylogenetic matching in
+from the coevolutionary history, the relative level of phylogenetic matching in
 local networks should be the same as in the regional networks (through a
 sampling effect from the distribution of interaction-level contribution to
-cophylogenetic matching), but the frequency of interactions should bear no
+co-phylogenetic matching), but the frequency of interactions should bear no
 relationship to their importance in overall matching.
@@
 As host-macroparasite interactions are hypothesized to be ecologically
-constrained, as a result of their being evolutionary conserved [@comb01pee], the
+constrained due to their being evolutionary conserved [@comb01pee], the
 congruence observed at the continental level sets the baseline for what would be
@@
 plot(z(loc_ss)~z(reg_ss), fig1dat, pch=19,
-  xlab="Relative cophylogenetic signal (regional)", ylab="Relative cophylogenetic signal (local)", asp=1)
+  xlab="Relative co-phylogenetic signal (regional)", ylab="Relative co-phylogenetic signal (local)", asp=1)
 abline(h=0, lty=2, col="grey")
@@
 set of drivers, then this should be reflected in the local networks by a higher
-degree of cophylogenetic matching.
+degree of co-phylogenetic matching.
 
@@
 
-plot(REG~mreg, allm, pch=NA, col=2, ylab = "Relative amount of coevolutionary signal", xlab="Average interaction-level contribution to coevolutionary signal", ylim=c(0, 0.3), xlim=rev(range(mreg)))
+plot(REG~mreg, allm, pch=NA, col=2, ylab = "Relative amount of co-phylogenetic signal", xlab="Average interaction-level contribution to co-phylogenetic signal", ylim=c(0, 0.3), xlim=rev(range(mreg)))
 segments(x0=allm$mreg, x1=allm$mloc, y0=REG, y1=LOC, col="lightgrey")
@@
 plot(density(unique(fig2dat[,c("int","rvalue")])$rvalue, from=1e3, to=max(fig2dat$rvalue)),
-   xlab = "Interaction-level contribution to coevoluationary signal",
+   xlab = "Interaction-level contribution to co-phylogenetic signal",
    ylab = "Probability density",
@@
 
-boxplot(stat~vary, fig3dat, ylim=rev(c(0,3e4)), lty=1, pch=19, xlab="Interaction spatial consistency", ylab="Interaction-level contribution to cophylogenetic signal")
+boxplot(stat~vary, fig3dat, ylim=rev(c(0,3e4)), lty=1, pch=19, xlab="Interaction spatial consistency", ylab="Interaction-level contribution to co-phylogenetic signal")
 points(jitter(match(fig3dat$vary, levels(fig3dat$vary))), fig3dat$stat, pch=21, cex=fig3dat$weight/7, bg=rgb(0, 0, 0, alpha=0.2), col=NA)
@@
 ![Spatial consistency of an interaction and its contribution to co-phylogenetic matching.
-Note that because *PACo* gives low scores to interactions with a strong contribution to co-phylogenetic matching, the y axis is reversed.
+Note that because *PACo* gives low scores to interactions with a strong contribution to co-phylogenetic matching, the y-axis is reversed.
 Spatial consistency is defined as the probability of observing an interaction between two species given that they were observed to co-occur (the size of the point is proportional to the number of times an interaction was observed).
@@
 ![The contribution to co-phylogenetic matching of the interaction between two species is maintained across scales.
-For every site (ranked on the x axis), we show the Pearson's correlation between interaction-level values of co-phylogenetic matching in the continental network and the same in the local network.
+For every site (ranked on the x-axis), we show the Pearson's correlation between interaction-level values of co-phylogenetic matching in the continental network and the same in the local network.
 The size of each point is proportional to the size of the network, and correlations for all sites are significant at $\alpha = 0.05$ except for those falling in the grey shaded area.](figure/scales-1.pdf){#fig:scales width=100%}
@@
 simultaneous variation of species' interactions *and* communities' phylogenetic
-tree structure. In a system characterised by substantial turnover, we would
+tree structure. In a system characterized by substantial turnover, we would
 expect the contribution of each separate interaction to differ across scales as
@@
 Overall, the results of our study demonstrate that there is a sizeable gap
-between our current understanding of host-parasite co-evolution as the basis of
+between our current understanding of host-parasite coevolution as the basis of
 multi-species interactions, its phylogenetic consequences, and their
@@
 local scale strongly suggests that the loss of signal from the continental to
-regional scale is due to species sampling in a manner that proceeds
+regional scale is due to species sampling in a manner that acts
 independently of the evolutionary history of species pairs. Because regional and
 local networks have the same species, the difference between them stems from the
-loss of some species interactions locally. It would therefore seem that local
+loss of some interactions locally. It would therefore seem that local
 species pools in this system are also driven by the interaction between abiotic
 conditions and species tolerance, in addition to potential species interactions.
-Taking a step back, this result suggests that while a shared phylogenetic
+Taking a step back, this result suggests that, while a shared phylogenetic
 history is a strong structuring force at the scale of the species pool, its
 influence is overridden by other factors during species filtering and community
-assembly. This does beg for future investigation of whether the importance of
-phylogenetic history decays at smaller spatial scale in host-parasite
-assemblages.
+assembly. It further highlights the need for future investigation of whether the importance of
+phylogenetic history in host-parasite
+assemblages decays at smaller spatial scales.
 
 Recently, @coel17nbp studied the factors that shape phylogenetic signal in
-bipartite interactions betweeen plants and mutualists. In contrast to our study,
-they used a Mantel test to compare the two trees; this is known to be lacking
-robustness [@harm10psp; @guil13dmt], which is what originally prompted the
-development of PACo [@balb13pnp] or ParaFit [@lege02sth]. Leaving aside the
-relative merits of the various methods, they show that phylogenetic signal is
+bipartite interactions between plants and mutualists. In contrast to our study,
+they used a Mantel test to compare the two trees, a method whose lack of
+robustness [@harm10psp; @guil13dmt] is what originally prompted the
+development of PACo [@balb13pnp] or ParaFit [@lege02sth]. Setting aside the
+relative merits of the various methods, they showed that phylogenetic signal is
 expected to decrease when (1) dispersal probability increases (*i.e.* all
@@
 high (*i.e.* there is no loss of signal due to local interaction filtering). We
-argue that the probability of interaction should not be viewed as a system-wide
-measure, but rather be defined for each interaction ({@eq:linktunover}). When
+argue here that the probability of interaction should not be viewed as a system-wide
+measure, but is better defined for each interaction separately ({@eq:linktunover}). When
 this is the case, we report no relationship between the probability of
-interaction, and its contribution to phylogenetic signal ({@fig:consistency}).
+interaction and its contribution to co-phylogenetic signal ({@fig:consistency}).
+
+The lack of a relationship between an interaction's probability of occurring (which represents
+their ecological stability) and its contribution to the co-phylogenetic process
+(which can be a proxy of their evolutionary stability) draws into question
+the basic long-term stability of interactions. Specifically, the existence of
+interactions with strong co-phylogenetic contribution, but low probability, is
+puzzling. It is tempting to hypothesize that these interactions may have once been strong
+enough to drive (co-)speciation, but are now decaying, due either to the fact
+that the host-parasite pair has been disrupted or as a consequence of
+ecological processes. DBS Can you spell this transition out for me better? I don't quite see the link. DBS @janz11err show that parasites can frequently acquire
+hosts that are not closely related to their initial host. This phenomenon,
+dubbed the "parasite paradox", can be responsible for a large number of
+diversification events, as parasites will be introduced to a novel environment
+when exposed to a novel host. The acquisition of novel hosts proceeds primarily
+from ecological contact between distantly related species. This emphasizes the
+need to account for the spatial structure of species interactions in these
+studies -- because all species do not co-occur at all places, the potential for
+ecological contact with novel hosts varies across space. Ideally, reconstruction
+of the ancestral range of the species can shed some light on whether acquisition
+of distantly related species happened, and where.
 
@@
 a key driver of community structure [@cave09mce], these data reveal that this
-impact is actually minimal at ecologically relevant spatial scales. And yet,
-despite all the above, individual interactions are somehow able to maintain
-their co-phylogenetic matching even when the community they are woven into does
-not. Thinking more broadly, these discrepancies provide a clear roadmap for
-bridging the gap between our appreciation of the role of shared evolutionary
-history and its empirically measurable outcomes: network structure is the most
-parsimonious *mechanism* by which coevolution proceeds, not the imprint
-potential coevolution leaves on ecological communities.
+impact is actually minimal at ecologically relevant spatial scales, even in
+a system where phylogenetic structure would be expected to have a profoundly
+strong role. And yet, despite all the above, individual interactions are somehow
+able to maintain their co-phylogenetic matching even when the community they are
+woven into does not. Thinking more broadly, these discrepancies provide a 
+roadmap for bridging the gap between our appreciation of the role of shared
+evolutionary history and its empirically measurable outcomes: network structure
+is the most parsimonious *mechanism* by which coevolution proceeds, not the
+imprint potential coevolution leaves on ecological communities.
+
+Finally, we would like to acknowledge some limitations in the data.
+Host-parasite evolution usually follows a number of canonical coevolutionary
+scenarios [@page03ttp]: true cospeciation, where the two speciation events are
+simultaneous; pseudo- or delayed-cospeciations, where one speciation event
+happens after the other; host shift, where the parasite acquires a new host
+(and can subsequently lose the previous host, undergo speciation, or maintain its
+ability to use the previous host); and host-range expansion, in which the parasite
+acquires a novel host.
+DBS Are we sure the differences between host shift and host-range expansion clear enough in the above? DBS
+When the likelihood of both host and parasite extinction
+events are added to these models, the variety of outcomes is considerable.
+@dev07wch shows that host-switch-like events can result in matching trees, and
+so one could argue that the continental-level signal of tree matching can emerge
+from numerous host-shift events [although the results of @kras12psm do not
+support this scenario]. Because separating true cospeciation events from all
+other situations is difficult without time-calibrated trees, @dev13cvh suggest
+that the number of cospeciation events is inflated by cophenetic methods like
+*PACo* or *ParaFit* [although @lope01mpf reported an increased number of
+cospeciations when accounting for time of speciation events]. This reinforces
+the need for high-quality phylogeny data calibrated for communities in which the
+interactions are known. Not only will this help us make more robust inference about
+the evolution of networks [@eklo16pcf], it will also help us leverage information about
+species interactions embedded within networks to better understand coevolutionary
+dynamics.
 

### 2017-05-23 manuscript/manuscript.Rmd
update the text with DBS comments

@@
 Locaitions where the regional network shows a significant co-phylogenetic structure are in black.
-See also {@tbl:contingency}.](figure/maps-1.pdf){#fig:maps width=100%}
+See also {@tbl:contingency}.
+](figure/maps-1.pdf){#fig:maps width=100%}
 
@@
 
-The lack of a relationship between an interaction's probability of occurring (which represents
-their ecological stability) and its contribution to the co-phylogenetic process
-(which can be a proxy of their evolutionary stability) draws into question
-the basic long-term stability of interactions. Specifically, the existence of
-interactions with strong co-phylogenetic contribution, but low probability, is
-puzzling. It is tempting to hypothesize that these interactions may have once been strong
-enough to drive (co-)speciation, but are now decaying, due either to the fact
-that the host-parasite pair has been disrupted or as a consequence of
-ecological processes. DBS Can you spell this transition out for me better? I don't quite see the link. DBS @janz11err show that parasites can frequently acquire
-hosts that are not closely related to their initial host. This phenomenon,
-dubbed the "parasite paradox", can be responsible for a large number of
-diversification events, as parasites will be introduced to a novel environment
-when exposed to a novel host. The acquisition of novel hosts proceeds primarily
-from ecological contact between distantly related species. This emphasizes the
-need to account for the spatial structure of species interactions in these
-studies -- because all species do not co-occur at all places, the potential for
-ecological contact with novel hosts varies across space. Ideally, reconstruction
-of the ancestral range of the species can shed some light on whether acquisition
-of distantly related species happened, and where.
+The lack of a relationship between an interaction's probability of occurring
+(which represents their ecological stability) and its contribution to the
+co-phylogenetic process (which can be a proxy of their evolutionary stability)
+draws into question the basic long-term stability of interactions. Specifically,
+the existence of interactions with strong co-phylogenetic contribution, but low
+probability, is puzzling. It is tempting to hypothesize that these interactions
+may have once been strong enough to drive (co-)speciation, but are now decaying,
+due either to the fact that the host-parasite pair has been disrupted (by
+additional speciation and extinction events in the hosts or parasites) or as a
+consequence of ecological processes (for example, changes in the environment
+modifying the strength of some interactions). @janz11err show that parasites can
+frequently acquire hosts that are not closely related to their initial host.
+This phenomenon, dubbed the "parasite paradox", can be responsible for a large
+number of diversification events, as parasites will be introduced to a novel
+environment when exposed to a novel host. The acquisition of novel hosts
+proceeds primarily from ecological contact between distantly related species.
+This emphasizes the need to account for the spatial structure of species
+interactions in these studies -- because all species do not co-occur at all
+places, the potential for ecological contact with novel hosts varies across
+space. Ideally, reconstruction of the ancestral range of the species can shed
+some light on whether acquisition of distantly related species happened, and
+where.
 
@@
 simultaneous; pseudo- or delayed-cospeciations, where one speciation event
-happens after the other; host shift, where the parasite acquires a new host
-(and can subsequently lose the previous host, undergo speciation, or maintain its
-ability to use the previous host); and host-range expansion, in which the parasite
-acquires a novel host.
-DBS Are we sure the differences between host shift and host-range expansion clear enough in the above? DBS
-When the likelihood of both host and parasite extinction
-events are added to these models, the variety of outcomes is considerable.
-@dev07wch shows that host-switch-like events can result in matching trees, and
-so one could argue that the continental-level signal of tree matching can emerge
-from numerous host-shift events [although the results of @kras12psm do not
-support this scenario]. Because separating true cospeciation events from all
-other situations is difficult without time-calibrated trees, @dev13cvh suggest
-that the number of cospeciation events is inflated by cophenetic methods like
-*PACo* or *ParaFit* [although @lope01mpf reported an increased number of
-cospeciations when accounting for time of speciation events]. This reinforces
-the need for high-quality phylogeny data calibrated for communities in which the
-interactions are known. Not only will this help us make more robust inference about
-the evolution of networks [@eklo16pcf], it will also help us leverage information about
-species interactions embedded within networks to better understand coevolutionary
-dynamics.
+happens after the other; host shift, where the parasite acquires a new host (and
+can subsequently lose the previous host, or undergo speciation); and host-range
+expansion, in which the parasite acquires a novel host and retains the ability
+to infect the previous host. When the likelihood of both host and parasite
+extinction events are added to these models, the variety of outcomes is
+considerable. @dev07wch shows that host-switch-like events can result in
+matching trees, and so one could argue that the continental-level signal of tree
+matching can emerge from numerous host-shift events [although the results of
+@kras12psm do not support this scenario]. Because separating true cospeciation
+events from all other situations is difficult without time-calibrated trees,
+@dev13cvh suggest that the number of cospeciation events is inflated by
+cophenetic methods like *PACo* or *ParaFit* [although @lope01mpf reported an
+increased number of cospeciations when accounting for time of speciation
+events]. This reinforces the need for high-quality phylogeny data calibrated for
+communities in which the interactions are known. Not only will this help us make
+more robust inference about the evolution of networks [@eklo16pcf], it will also
+help us leverage information about species interactions embedded within networks
+to better understand coevolutionary dynamics.
 

### 2017-06-06 manuscript/manuscript.Rmd
revision 2

@@
 Locations where the local network shows a significant co-phylogenetic structure are marked with triangles.
-Locaitions where the regional network shows a significant co-phylogenetic structure are in black.
-See also {@tbl:contingency}.
-](figure/maps-1.pdf){#fig:maps width=100%}
+Locaitions where the regional network shows a significant co-phylogenetic structure are in black.](figure/maps-1.pdf){#fig:maps width=100%}
 
@@
 interactions are more frequent is because they reflect a significant past
-history of coevolution [@guim07iia; @mora10bhi]; that is, the ecological
+history of coevolution [@guim07iia; @nieb10ucp]; that is, the ecological
 constraints emerge from evolutionary conservatism. Using a weighted Pearson's
@@
 a key driver of community structure [@cave09mce], these data reveal that this
-impact is actually minimal at ecologically relevant spatial scales, even in
-a system where phylogenetic structure would be expected to have a profoundly
+impact is actually minimal at ecologically relevant spatial scales, even in a
+system where phylogenetic structure would be expected to have a profoundly
 strong role. And yet, despite all the above, individual interactions are somehow
@@
 is the most parsimonious *mechanism* by which coevolution proceeds, not the
-imprint potential coevolution leaves on ecological communities.
+imprint potential coevolution leaves on ecological communities [@poni17clw].
 

### 2017-06-06 manuscript/new.tex
revision 2

--- 2017-04-27 manuscript/output/manuscript.tex
@@
-\documentclass[12pt]{article}
+\documentclass[11pt,serif]{article}
 
-\usepackage[table]{xcolor}
+\input{.plmt/plmt.tex}
 
-\usepackage[hidelinks]{hyperref}
-\usepackage{etoolbox}
-\usepackage{graphicx}
-\usepackage{adjustbox}
+\geometry{margin=2.5cm}
 
-\makeatletter
-\def\ScaleIfNeeded{%
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-% fonts
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage{textgreek}
-\usepackage[greek,english]{babel}
-\usepackage{amsmath}
-
-% Code highlight and colors
-\usepackage{listings}
-\lstset{
-  numbers=left,
-  tabsize=1,
-  basicstyle=\small\ttfamily,
-  breaklines=true
-}
-
-\usepackage{booktabs, tabularx, longtable}
-\usepackage{csquotes}
-\usepackage{authblk}
-
-% Geometry block
-\usepackage[letterpaper]{geometry}
-\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-\title{Interactions retain the co-phylogenetic matching that communities lost}
-
-\author[1,2,3]{Timothée~Poisot}
-\author[1]{Daniel B.~Stouffer}
-\affil[1]{Centre for Integrative Ecology, School of Biological Sciences,
-University of Canterbury, Christchurch, New Zealand}
-\affil[2]{Université de Montréal, Département de Sciences Biologiques, Montréal,
-Canada}
-\affil[3]{Québec Centre for Biodiversity Sciences, Montréal, Canada}
+\usepackage[right]{lineno}
+\linenumbers
+\usepackage{endfloat}
 
@@
 
-\maketitle
+\thispagestyle{empty}
 
-\begin{abstract}
+{\bfseries\huge Interactions retain the co-phylogenetic matching that communities lost}
+
+\vskip 5em
+
+\begin{flushleft}
+\href{http://orcid.org/0000-0002-0735-5184}{Timothée Poisot}
+~\emph{1,2,3}
+\quad
+\mbox{Daniel B. Stouffer}
+~\emph{1}
+\end{flushleft}
+\bigskip
+
+\small
+\textbf{1}:~Centre for Integrative Ecology, School of Biological Sciences,
+University of Canterbury, Christchurch, New Zealand;\quad\textbf{2}:~Université de Montréal, Département de Sciences Biologiques, Montréal,
+Canada;\quad\textbf{3}:~Québec Centre for Biodiversity Sciences, Montréal, Canada\normalsize
+\vfill
+
 Both species and their interactions are affected by changes that occur
@@
 communities that do not.
-\end{abstract}
+\vskip 1em
+{\small{\bfseries Keywords:}
+species interactions  - host-parasites  - phylogenetic congruence  - network cophylogeny  - community phylogenetics \vskip 4em
+}
 
-% pandoc-xnos: macro to create a caption without a prefix
-\makeatletter
-\long\def\@makenoprefixcaption#1#2{
-  \vskip\abovecaptionskip
-  \sbox\@tempboxa{#2}
-  \ifdim \wd\@tempboxa >\hsize
-    #2\par
-  \else
-    \global \@minipagefalse
-    \hb@xt@\hsize{\hfil\box\@tempboxa\hfil}
-  \fi
-  \vskip\belowcaptionskip}
-\makeatother
+\vfill
 
-% pandoc-fignos: save original macros
-\makeatletter
-\let\@oldmakecaption=\@makecaption
-\let\oldthefigure=\thefigure
-\let\oldtheHfigure=\theHfigure
-\makeatother
+{\small%
+{\ccby}\\
+{\emph{This work is licensed under a %
+Creative Commons Attribution 4.0 Unported License.}}%
+\\
+Correspondence to Timothée Poisot -- \texttt{timothee.poisot@umontreal.ca}\newline
+\texttt{2017-03-02T00:00:00.000Z}
+}%
 
-% pandoc-fignos: environment disables figure caption prefixes
-\makeatletter
-\newcounter{figno}
-\newenvironment{no-prefix-figure-caption}{
-  \let\@makecaption=\@makenoprefixcaption
-  \renewcommand\thefigure{x.\thefigno}
-  \renewcommand\theHfigure{x.\thefigno}
-  \stepcounter{figno}
-}{
-  \let\thefigure=\oldthefigure
-  \let\theHfigure=\oldtheHfigure
-  \let\@makecaption=\@oldmakecaption
-  \addtocounter{figure}{-1}
-}
-\makeatother
+\cleardoublepage
+
+\doublespacing
 
@@
 inconclusive (Hembry et al. 2014). This suggests that these
-well-describe mechanisms may not confer substantial predictive power
+well-described mechanisms may not confer substantial predictive power
 when examined at scales of organization larger than the pairwise
@@
 how other species evolved and established, lost, or maintained
-interactions throughout their joint evolutionary history. Nonetheless,
+interactions throughout their joint evolutionary history (in addition to
+the fact that species may have different impacts on one another,
+\emph{i.e.} the effect of any interaction on the community-level
+co-phylogenetic signal is not expected to be equal). Nonetheless,
 detecting matching phylogenies for interacting clades indicates that
@@
 allow us to draw conclusions on coevolution. Nevertheless,
-interaction-level measures are useful, in that, when expressed as the
+interaction-level measures are useful in that, when expressed as the
 contribution of interactions to the overall signal, they allow us to
@@
 local communities will differ. Species sampling and variability of
-interactions, however, does no predict (i) how the phylogenetic signal
-of pairwise interactions is kept or lost at the scale of the whole
+interactions, however, do no predict (i) how the phylogenetic signal of
+pairwise interactions is kept or lost at the scale of the whole
 community nor (ii) whether or not this variability is related to changes
@@
 \emph{Continental} interaction data consists of the aggregated
-\enquote{metanetwork} which includes all documented interactions between
+``metanetwork'' which includes all documented interactions between
 species from the regional species pool (Poisot et al. 2012). For every
@@
 Second, \emph{local} interaction data are the actual observations at
-this location: the identity of the present species, and the way they
+this location: the identity of the species present, and the way they
 interact. In addition to capturing the dissimilarity of species
@@
 (\(C_{ij}\)). Because \(L_{ij} \in [0,C_{ij}]\), this measure takes
-values in \([0,1]\). Larger values reflect high spatial consistency.
-Note that although they are reported as 0 (\emph{i.e.} having no
-interactions), we actually have no information about species pairs that
-have never co-occurred; this is a common, but hard-to-correct-for,
-feature of spatially replicated datasets in which species occurrence
-varies (Morales-Castilla et al. 2015). Therefore, the only values of
-\(S_{ij}\) can be properly estimated are those for species pairs that
-have been observed to \emph{co-occur} at least once.
+values in \([0,1]\) where larger values reflect high spatial
+consistency. Note that although they are reported as 0 (\emph{i.e.}
+having no interactions), we actually have no information about species
+pairs that have never co-occurred; this is a common, but
+hard-to-correct-for, feature of spatially replicated datasets in which
+species occurrence varies (Morales-Castilla et al. 2015). Therefore, the
+only values of \(S_{ij}\) can be properly estimated are those for
+species pairs that have been observed to \emph{co-occur} at least once.
 
@@
 This is not an issue for permutation tests, since they evaluate the
-significance of the cophylogenetic signal by permutations of each
+significance of the co-phylogenetic signal by permutations of each
 network, the power of each test varies but the test statistics can be
 compared. To ensure that values of the interaction contribution to
-cophylogenetic signal are comparable, we normalized them network-wise by
-dividing them by the maximal value of the sum of square in PACo. While
-the raw values returned by PACo are not meaningfully comparable between
-networks, the corrected values presented here are.
+co-phylogenetic signal are comparable, we normalized them network-wise
+by dividing them by the maximal value of the sum of squares in PACo.
+While the raw values returned by PACo are not meaningfully comparable
+between networks, the corrected values presented here are.
 
@@
 \centering
-\includegraphics[width=1.00000\textwidth]{figures/figure1.pdf}
+\includegraphics[width=1.00000\textwidth]{figure/maps-1.pdf}
 \caption{Spatial distribution of co-phylogenetic matching across the 51
@@
 regional and local interaction networks is consistent with phylogenetic
-congruence. The colour of the circle corresponds to regionally
-significant or non-significant (black and grey, respectively) while the
-colour of the symbol within corresponds to locally significant or
-non-significant (black and grey, respectively).\label{fig:maps}}
+congruence. Locations where the local network shows a significant
+co-phylogenetic structure are marked with triangles. Locaitions where
+the regional network shows a significant co-phylogenetic structure are
+in black.\label{fig:maps}}
 \end{figure}
@@
 in the continental network, since the latter represents a somewhat
-artefactual agglomeration of species pairs that do not co-occur. The
+artifactual agglomeration of species pairs that do not co-occur. The
 opposite situation (a relatively lower phylogenetic matching) would
@@
 a strong phylogenetic signal happen more often). On the contrary, if
-local assembly proceeds largely independently from the co-evolutionary
+local assembly proceeds largely independently from the coevolutionary
 history, the relative level of phylogenetic matching in local networks
@@
 effect from the distribution of interaction-level contribution to
-cophylogenetic matching), but the frequency of interactions should bear
+co-phylogenetic matching), but the frequency of interactions should bear
 no relationship to their importance in overall matching.
@@
 As host-macroparasite interactions are hypothesized to be ecologically
-constrained, as a result of their being evolutionary conserved (Combes
-2001), the congruence observed at the continental level sets the
-baseline for what would be expected in local communities. Of course, if
-ecological mechanisms (such as filtering) reduce co-phylogenetic
-matching, we should detect this signal at the continental scale but not
-locally. Out of 51 sites, our \emph{PACo} analysis indicates that 35
-show no signal of co-phylogenetic matching at all, 11 show significant
-co-phylogenetic matching when using the regional interactions, and 12
-show significant co-phylogenetic matching using the local interactions
-(see \emph{Supp. Mat. 1} for network-level significance values;
-\autoref{maps}). These results support the idea that macro-evolutionary
-processes, such as co-diversification, can have consequences at the
-macro-ecological level but may not in fact be detectable at finer
-spatial scales.
+constrained due to their being evolutionary conserved (Combes 2001), the
+congruence observed at the continental level sets the baseline for what
+would be expected in local communities. Of course, if ecological
+mechanisms (such as filtering) reduce co-phylogenetic matching, we
+should detect this signal at the continental scale but not locally. Out
+of 51 sites, our \emph{PACo} analysis indicates that 35 show no signal
+of co-phylogenetic matching at all, 11 show significant co-phylogenetic
+matching when using the regional interactions, and 12 show significant
+co-phylogenetic matching using the local interactions (see \emph{Supp.
+Mat. 1} for network-level significance values;
+\xrefname{table}\cref{tbl:contingency}; \xrefname{fig.}\cref{fig:maps}).
+These results support the idea that macro-evolutionary processes, such
+as co-diversification, can have consequences at the macro-ecological
+level but may not in fact be detectable at finer spatial scales.
+
+\begin{longtable}[]{@{}lrr@{}}
+\caption{Contingency table showing the number of networks with
+(non-)significant local and regional co-phylogenetic signal.
+\label{tbl:contingency}}\tabularnewline
+\toprule
+& Regional non-significant & Regional significant\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& Regional non-significant & Regional significant\tabularnewline
+\midrule
+\endhead
+Local non-significant & 35 & 4\tabularnewline
+Local significant & 5 & 7\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 \centering
-\includegraphics[width=1.00000\textwidth]{figures/figureLocReg.pdf}
+\includegraphics[width=0.80000\textwidth]{figure/localregional-1.pdf}
 \caption{The regional and local networks show the same relative amount
@@
 When we compared the relative degree of co-phylogenetic matching in the
-local and regional communities (\autoref{relative}), we see that the
-relationship between the two is approximately linear (95\% confidence
-interval for the correlation coefficient \(0.914\)--\(0.971\)). This
-fits with the hypothesis of local networks being assembled by a random
-sampling from regional networks: if interactions between species at
-matching positions in both trees are maintained by the same set of
-drivers, then this should be reflected in the local networks by a higher
-degree of cophylogenetic matching.
+local and regional communities (\xrefname{fig.}\cref{fig:relative}), we
+see that the relationship between the two is approximately linear (95\%
+confidence interval for the correlation coefficient
+\(0.914\)--\(0.971\)). This fits with the hypothesis of local networks
+being assembled by a random sampling from regional networks: if
+interactions between species at matching positions in both trees are
+maintained by the same set of drivers, then this should be reflected in
+the local networks by a higher degree of co-phylogenetic matching.
 
@@
 
-\begin{no-prefix-figure-caption}
-
 \begin{figure}[htbp]
 \centering
-\includegraphics[width=1.00000\textwidth]{figures/figure4.pdf}
+\includegraphics[width=1.00000\textwidth]{figure/contributions-1.pdf}
 \caption{Distribution of co-phylogenetic matching at the network and
@@
 that on average contribute little to co-phylogenetic matching at the
-continental scale. co-phylogenetic matching is presented relatively to
+continental scale. Co-phylogenetic matching is presented relatively to
 the continental level co-phylogenetic matching. Dashed lines are a cubic
@@
 smoothed using a Gaussian kernel density estimator. Raw probability
-densities are shown as semi-transparent bars.}\label{fg:contributions}
+densities are shown as semi-transparent bars. Interaction-level
+contributions are unitless, and lower values represent stronger
+signal.\label{fig:contributions}}
 \end{figure}
-
-\end{no-prefix-figure-caption}
 
@@
 co-phylogenetic matching at the local and regional scales as well
-(\(\rho = 0.95\); \autoref{contributions}A). Intriguingly, we also find
-that the distribution of individual interactions' contributions to
-co-phylogenetic matching is strongly conserved, regardless of the scale
-at which the interactions are quantified (\autoref{contributions}B).
-Because interactions differ between each other in terms of their total
+(\(\rho = 0.95\); \xrefname{fig.}\cref{fig:contributions}A).
+Intriguingly, we also find that the distribution of individual
+interactions' contributions to co-phylogenetic matching is strongly
+conserved, regardless of the scale at which the interactions are
+quantified (\xrefname{fig.}\cref{fig:contributions}B). Because
+interactions differ between each other in terms of their total
 contribution to co-phylogenetic matching, this implies that their
@@
 \centering
-\includegraphics[width=0.80000\textwidth]{figures/figure3.pdf}
+\includegraphics[width=0.80000\textwidth]{figure/consistency-1.pdf}
 \caption{Spatial consistency of an interaction and its contribution to
@@
 to interactions with a strong contribution to co-phylogenetic matching,
-the y axis is reversed. Spatial consistency is defined as the
+the y-axis is reversed. Spatial consistency is defined as the
 probability of observing an interaction between two species given that
-they were observed to co-occur. Although statistically significant,
-there was no biologically meaningful relationship between spatial
-consistency and an interaction's importance for co-phylogenetic matching
-in the continental network (\(R^2 \approx 0.01\), \(\rho = -0.1\),
-\(p \leq 10^{-5}\)).\label{fig:consistency}}
+they were observed to co-occur (the size of the point is proportional to
+the number of times an interaction was observed). Although statistically
+significant, there was no biologically meaningful relationship between
+spatial consistency and an interaction's importance for co-phylogenetic
+matching in the continental network (\(R^2 \approx 0.01\),
+\(\rho = -0.1\), \(p \leq 10^{-5}\)).\label{fig:consistency}}
 \end{figure}
@@
 some interactions are more frequent is because they reflect a
-significant past history of coevolution (Guimaraes et al. 2007; 2010);
-that is, the ecological constraints emerge from evolutionary
-conservatism. Using a weighted Pearson's correlation between the
-interaction frequency, interaction contribution to co-phylogenetic
-matching, and the number of observations of each interaction as the
-weight, we observe that this is marginally true (\(\rho \approx -0.11\).
-\(t \approx -5.09\) with weights; \(\rho \approx -0.10\),
-\(t \approx -4.6\) without; both significant at \(\alpha = 0.05\);
-\autoref{consistency}). Recall that the \emph{negative} correlation here
-arises from the fact that high interaction-level values in PACo means
-\emph{low} contribution to co-phylogenetic signal. Nevertheless, the
-significance of this result ought to be tempered by the fact that the
-\(R^2\) of both regressions is close to \(0.01\). Consequently, the
-association between spatial consistency and contribution to
-co-phylogenetic signal, while statistically significant, explains so
-little variance of either quantities that it is likely of negligible
-biological importance. This implies that the spatial consistency of an
-interaction does not necessarily reflect its evolutionary past, but
-rather (possibly) extant ecological processes.
+significant past history of coevolution (Guimaraes et al. 2007;
+Nieberding et al. 2010); that is, the ecological constraints emerge from
+evolutionary conservatism. Using a weighted Pearson's correlation
+between the interaction frequency, interaction contribution to
+co-phylogenetic matching, and the number of observations of each
+interaction as the weight, we observe that this is marginally true
+(\(\rho \approx -0.11\). \(t \approx -5.09\) with weights;
+\(\rho \approx -0.10\), \(t \approx -4.6\) without; both significant at
+\(\alpha = 0.05\); \xrefname{fig.}\cref{fig:consistency}). Recall that
+the \emph{negative} correlation here arises from the fact that high
+interaction-level values in PACo means \emph{low} contribution to
+co-phylogenetic signal. Nevertheless, the significance of this result
+ought to be tempered by the fact that the \(R^2\) of both regressions is
+close to \(0.01\). Consequently, the association between spatial
+consistency and contribution to co-phylogenetic signal, while
+statistically significant, explains so little variance of either
+quantities that it is likely of negligible biological importance. This
+implies that the spatial consistency of an interaction does not
+necessarily reflect its evolutionary past, but rather (possibly) extant
+ecological processes.
 
@@
 \centering
-\includegraphics[width=1.00000\textwidth]{figures/figure2.pdf}
+\includegraphics[width=1.00000\textwidth]{figure/scales-1.pdf}
 \caption{The contribution to co-phylogenetic matching of the interaction
 between two species is maintained across scales. For every site (ranked
-on the x axis), we show the Pearson's correlation between
+on the x-axis), we show the Pearson's correlation between
 interaction-level values of co-phylogenetic matching in the continental
@@
 simultaneous variation of species' interactions \emph{and} communities'
-phylogenetic tree structure. In a system characterised by substantial
+phylogenetic tree structure. In a system characterized by substantial
 turnover, we would expect the contribution of each separate interaction
@@
 observation is independent of network-wide co-phylogenetic matching
-(\autoref{scales}). Remarkably, this result implies that the remnants of
-co-phylogenetic inertia are still locally detectable in \emph{individual
-interactions} even though shared evolutionary history regularly fails to
-leave its imprint on most local networks.
+(\xrefname{fig.}\cref{fig:scales}). Remarkably, this result implies that
+the remnants of co-phylogenetic inertia are still locally detectable in
+\emph{individual interactions} even though shared evolutionary history
+regularly fails to leave its imprint on most local networks.
 
@@
 Overall, the results of our study demonstrate that there is a sizeable
-gap between our current understanding of host-parasite co-evolution as
+gap between our current understanding of host-parasite coevolution as
 the basis of multi-species interactions, its phylogenetic consequences,
@@
 strongly suggests that the loss of signal from the continental to
-regional scale is due to species sampling in a manner that proceeds
+regional scale is due to species sampling in a manner that acts
 independently of the evolutionary history of species pairs. Because
 regional and local networks have the same species, the difference
-between them stems from the loss of some species interactions locally.
-It would therefore seem that local species pools in this system are also
-driven by the interaction between abiotic conditions and species
-tolerance, in addition to potential species interactions. Taking a step
-back, this result suggests that while a shared phylogenetic history is a
-strong structuring force at the scale of the species pool, its influence
-is overridden by other factors during species filtering and community
-assembly. This does beg for future investigation of whether the
-importance of phylogenetic history decays at smaller spatial scale in
-host-parasite assemblages.
+between them stems from the loss of some interactions locally. It would
+therefore seem that local species pools in this system are also driven
+by the interaction between abiotic conditions and species tolerance, in
+addition to potential species interactions. Taking a step back, this
+result suggests that, while a shared phylogenetic history is a strong
+structuring force at the scale of the species pool, its influence is
+overridden by other factors during species filtering and community
+assembly. It further highlights the need for future investigation of
+whether the importance of phylogenetic history in host-parasite
+assemblages decays at smaller spatial scales.
 
 Recently, Coelho et al. (2017) studied the factors that shape
-phylogenetic signal in bipartite interactions betweeen plants and
+phylogenetic signal in bipartite interactions between plants and
 mutualists. In contrast to our study, they used a Mantel test to compare
-the two trees; this is known to be lacking robustness (Harmon \& Glor
-2010; Guillot \& Rousset 2013), which is what originally prompted the
-development of PACo (Balbuena et al. 2013) or ParaFit (Legendre et al.
-2002). Leaving aside the relative merits of the various methods, they
-show that phylogenetic signal is expected to decrease when (1) dispersal
+the two trees, a method whose lack of robustness (Harmon \& Glor 2010;
+Guillot \& Rousset 2013) is what originally prompted the development of
+PACo (Balbuena et al. 2013) or ParaFit (Legendre et al. 2002). Setting
+aside the relative merits of the various methods, they showed that
+phylogenetic signal is expected to decrease when (1) dispersal
 probability increases (\emph{i.e.} all locations share the same species)
 and (2) the probability of interactions is high (\emph{i.e.} there is no
-loss of signal due to local interaction filtering). We argue that the
-probability of interaction should not be viewed as a system-wide
-measure, but rather be defined for each interaction
+loss of signal due to local interaction filtering). We argue here that
+the probability of interaction should not be viewed as a system-wide
+measure, but is better defined for each interaction separately
 (\xrefname{eq.}\cref{eq:linktunover}). When this is the case, we report
-no relationship between the probability of interaction, and its
-contribution to phylogenetic signal
+no relationship between the probability of interaction and its
+contribution to co-phylogenetic signal
 (\xrefname{fig.}\cref{fig:consistency}).
+
+The lack of a relationship between an interaction's probability of
+occurring (which represents their ecological stability) and its
+contribution to the co-phylogenetic process (which can be a proxy of
+their evolutionary stability) draws into question the basic long-term
+stability of interactions. Specifically, the existence of interactions
+with strong co-phylogenetic contribution, but low probability, is
+puzzling. It is tempting to hypothesize that these interactions may have
+once been strong enough to drive (co-)speciation, but are now decaying,
+due either to the fact that the host-parasite pair has been disrupted
+(by additional speciation and extinction events in the hosts or
+parasites) or as a consequence of ecological processes (for example,
+changes in the environment modifying the strength of some interactions).
+Janz (2011) show that parasites can frequently acquire hosts that are
+not closely related to their initial host. This phenomenon, dubbed the
+``parasite paradox'', can be responsible for a large number of
+diversification events, as parasites will be introduced to a novel
+environment when exposed to a novel host. The acquisition of novel hosts
+proceeds primarily from ecological contact between distantly related
+species. This emphasizes the need to account for the spatial structure
+of species interactions in these studies -- because all species do not
+co-occur at all places, the potential for ecological contact with novel
+hosts varies across space. Ideally, reconstruction of the ancestral
+range of the species can shed some light on whether acquisition of
+distantly related species happened, and where.
 
@@
 (Cavender-Bares et al. 2009), these data reveal that this impact is
-actually minimal at ecologically relevant spatial scales. And yet,
-despite all the above, individual interactions are somehow able to
-maintain their co-phylogenetic matching even when the community they are
-woven into does not. Thinking more broadly, these discrepancies provide
-a clear roadmap for bridging the gap between our appreciation of the
-role of shared evolutionary history and its empirically measurable
-outcomes: network structure is the most parsimonious \emph{mechanism} by
-which coevolution proceeds, not the imprint potential coevolution leaves
-on ecological communities.
+actually minimal at ecologically relevant spatial scales, even in a
+system where phylogenetic structure would be expected to have a
+profoundly strong role. And yet, despite all the above, individual
+interactions are somehow able to maintain their co-phylogenetic matching
+even when the community they are woven into does not. Thinking more
+broadly, these discrepancies provide a roadmap for bridging the gap
+between our appreciation of the role of shared evolutionary history and
+its empirically measurable outcomes: network structure is the most
+parsimonious \emph{mechanism} by which coevolution proceeds, not the
+imprint potential coevolution leaves on ecological communities (Ponisio
+\& M'Gonigle 2017).
+
+Finally, we would like to acknowledge some limitations in the data.
+Host-parasite evolution usually follows a number of canonical
+coevolutionary scenarios (Page 2003): true cospeciation, where the two
+speciation events are simultaneous; pseudo- or delayed-cospeciations,
+where one speciation event happens after the other; host shift, where
+the parasite acquires a new host (and can subsequently lose the previous
+host, or undergo speciation); and host-range expansion, in which the
+parasite acquires a novel host and retains the ability to infect the
+previous host. When the likelihood of both host and parasite extinction
+events are added to these models, the variety of outcomes is
+considerable. De Vienne et al. (2007) shows that host-switch-like events
+can result in matching trees, and so one could argue that the
+continental-level signal of tree matching can emerge from numerous
+host-shift events (although the results of Krasnov et al. 2012a do not
+support this scenario). Because separating true cospeciation events from
+all other situations is difficult without time-calibrated trees, de
+Vienne et al. (2013) suggest that the number of cospeciation events is
+inflated by cophenetic methods like \emph{PACo} or \emph{ParaFit}
+(although Lopez-Vaamonde et al. 2001 reported an increased number of
+cospeciations when accounting for time of speciation events). This
+reinforces the need for high-quality phylogeny data calibrated for
+communities in which the interactions are known. Not only will this help
+us make more robust inference about the evolution of networks (Eklöf \&
+Stouffer 2016), it will also help us leverage information about species
+interactions embedded within networks to better understand
+coevolutionary dynamics.
 
@@
 \textbf{Coelho et al.} (2017). Neutral biogeography of phylogenetically
-structured interaction networks. \emph{Ecography.}
+structured interaction networks. \emph{Ecography.}:n/a--a.
 
@@
 Intimate Interactions. University Of Chicago Press;
+
+\hypertarget{ref-dev07wch}{}
+\textbf{De Vienne et al.} (2007). When can host shifts produce congruent
+host and parasite phylogenies? A simulation approach. \emph{Journal of
+Evolutionary Biology.} 20:1428--38.
+
+\hypertarget{ref-dev13cvh}{}
+\textbf{de Vienne et al.} (2013). Cospeciation vs host-shift speciation:
+methods for testing, evidence from natural associations and relation to
+coevolution. \emph{New Phytol.} 198:347--85.
 
@@
 the shadow of forgotten ancestors. \emph{Glob Ecol Biogeogr.} 17:11--7.
+
+\hypertarget{ref-eklo16pcf}{}
+\textbf{Eklöf \& Stouffer}. (2016). The phylogenetic component of food
+web structure and intervality. \emph{Theor Ecol.} 9:107--15.
 
@@
 \hypertarget{ref-harm10psp}{}
-\textbf{Harmon \& Glor}. (2010). POOR STATISTICAL PERFORMANCE OF THE
-MANTEL TEST IN PHYLOGENETIC COMPARATIVE ANALYSES. \emph{Evolution.}
+\textbf{Harmon \& Glor}. (2010). Poor Statistical Performance of the
+Mantel Test in Phylogenetic Comparative Analyses. \emph{Evolution.}
 
@@
 Approach to Cophylogeny in R. \emph{Methods in Ecology and Evolution.}
+
+\hypertarget{ref-janz11err}{}
+\textbf{Janz}. (2011). Ehrlich and Raven Revisited: Mechanisms
+Underlying Codiversification of Plants and Enemies. \emph{Annual Review
+of Ecology, Evolution, and Systematics.} 42:71--89.
 
@@
 
+\hypertarget{ref-lope01mpf}{}
+\textbf{Lopez-Vaamonde et al.} (2001). Molecular Phylogenies of Fig
+Wasps: Partial Cocladogenesis of Pollinators and Parasites.
+\emph{Molecular Phylogenetics and Evolution.} 21:55--71.
+
 \hypertarget{ref-mora15ibi}{}
@@
 perspectives. \emph{Biol Rev.} 87:769--85.
+
+\hypertarget{ref-nieb10ucp}{}
+\textbf{Nieberding et al.} (2010). The use of co-phylogeographic
+patterns to predict the nature of host--parasite interactions, and vice
+versa. \emph{The Biogeography of Host-Parasite Interactions.} Oxford:
+Oxford University Press; pp. 631--41.
 
@@
 
-\hypertarget{ref-pois152wc}{}
-\textbf{Poisot}. (2015). 23 When is co-phylogeny evidence of
-coevolution? \emph{Parasite Diversity and Diversification: Evolutionary
-Ecology Meets Phylogenetics.}:420.
+\hypertarget{ref-page03ttp}{}
+\textbf{Page}. (2003). Tangled trees: Phylogeny, cospeciation, and
+coevolution. University of Chicago Press;
+
+\hypertarget{ref-pois15wce}{}
+\textbf{Poisot}. (2015). When is co-phylogeny evidence of coevolution?
+\emph{Parasite Diversity and Diversification: Evolutionary Ecology Meets
+Phylogenetics.} p. 420.
 
@@
 124:243--51.
+
+\hypertarget{ref-poni17clw}{}
+\textbf{Ponisio \& M'Gonigle}. (2017). Coevolution leaves a weak signal
+on ecological networks. \emph{Ecosphere.} 8:n/a--a.
 
@@
 
-\hypertarget{ref-mora10bhi}{}
-(2010). Biogreography of host-parasite interactions. Morand, Krasnov,
-eds. Oxford: Oxford University Press;
-
 \end{document}
